### 2023-05-28 LaTeX_paper/paper.tex
add LaTeX folder

\documentclass{article}
\usepackage{graphicx} % Required for inserting images

\title{Use Of Jigsaw Puzzle Solving Algorithms In The Real World}
\author{Luca Sartore}
\date{May 2023}

\begin{document}

\maketitle

\newpage

\tableofcontents

\newpage

\section{Abstract}
The jigsaw puzzle problem has been in the eye of computer scientists for a while,
and some clever solutions have already been found. These algorithms are made to
work with a “digital” jigsaw puzzle (insert reference here), there aren't papers
(at least not popular enough to be searchable) that try to apply the solution
to a “real world” (insert reference here) jigsaw puzzle.\newline
The problem has been tackled by some small projects. But, as said earlier,
the process and eventual challenges has never been documented by a paper,
this wants to be the first.\newline
As a Bonus the paper will also cover the creation of a user friendly app
that will be open source and free to use.

\section{Introduction}
\subsection{Classification}
This paper will focus on type 2 puzzles. A type 2 puzzle is a puzzle where the position, and the orientation of each piece is unknown. 
\subsection{Digital vs Real-World Jigsaw Puzzles}

There is  another important distinction between different types of puzzles. They can be divided into “digital” and “real world” jigsaw puzzles.

\end{document}

### 2023-05-28 LaTeX_paper/paper.tex
backup commit with changes latex doc

@@
 and some clever solutions have already been found. These algorithms are made to
-work with a “digital” jigsaw puzzle (insert reference here), there aren't papers
+work with a “digital” jigsaw puzzle [Figure \ref{fig:figure_digital_puzzle}], there aren't papers
 (at least not popular enough to be searchable) that try to apply the solution
@@
 
+\bigskip
+
+%\begin{center}
+
+    \begin{figure}[h]
+        \caption{An example of a “digital” puzzle}
+        \label{fig:figure_digital_puzzle}
+        \centering
+        \includegraphics[width=0.5\textwidth]{pictures/digital_puzzle.png}
+    \end{figure}
+
+    \includegraphics[height=0.3\columnwidth]{pictures/real_puzzle.jpg}
+    \newline
+    %\bigskip
+    \includegraphics[height=0.3\columnwidth]{pictures/digital_puzzle.png}
+%\end{center}
+
 \end{document}

### 2023-05-28 LaTeX_paper/paper.tex
finish up to section 3 in lpaper

--- 2023-05-28 LaTeX_paper/paper.tex
@@
 \documentclass{article}
-\usepackage{graphicx} % Required for inserting images
+
+% Required for inserting images
+\usepackage{graphicx}
+
+% to have more colors avelable
+\usepackage{xcolor}
+
+% to insert hiperlinks
+\usepackage[colorlinks=true,linkcolor=cyan]{hyperref}
+
+% to have better references
+\usepackage[noabbrev]{cleveref}
+
+% to use prefix for references
+\usepackage{etoolbox}
+
+% rule for reference to fugures
+\pretocmd{\thefigure}{F}{}{}
 
@@
 
+% make the table of content without the hiperlink color
+{
+  \hypersetup{linkcolor=black}
   \tableofcontents
+}
 
@@
 and some clever solutions have already been found. These algorithms are made to
-work with a “digital” jigsaw puzzle (insert reference here), there aren't papers
-(at least not popular enough to be searchable) that try to apply the solution
-to a “real world” (insert reference here) jigsaw puzzle.\newline
+work with a “digital” jigsaw puzzle [\ref{fig:figure_digital_puzzle}],
+there aren't papers (at least not popular enough to be searchable)
+that try to apply the solution
+to a “real world” jigsaw puzzle [\ref{fig:figure_real_puzzle}].\newline
 The problem has been tackled by some small projects. But, as said earlier,
@@
 
+% figure of digital jigsaw puzzle    
+\begin{figure}[h]
+    \caption{An example of a “digital” jigsaw  puzzle}\label{fig:figure_digital_puzzle}
+    \centering
+    \includegraphics[height=0.25\textwidth]{pictures/digital_puzzle.png}
+\end{figure}
+
+% figure of real jigsaw puzzle    
+\begin{figure}[h]
+    \caption{An example of a “real world” jigsaw  puzzle}\label{fig:figure_real_puzzle}
+    \includegraphics[height=0.25\textwidth]{pictures/real_puzzle.jpg}
+    \centering
+
+\end{figure}
+
+The reason this distinction is important is because,
+despite the generic concept of the puzzle not changing,
+obtaining accurate matches of a piece's characteristics
+is far easier with a digital puzzle,
+since there are far less things that can go wrong.
+
+% figure of a mesurement error
+\begin{figure}[h]
+    \caption{An example of what can go wrong when dealing with the real world}\label{fig:figure_measurement_error}
+    \includegraphics[height=0.25\textwidth]{pictures/example_bad_piece.jpg}
+    \centering
+
+\end{figure}
+
+\section{Previous Literature}
+This section will analyze 3 different algorithms that have been proposed
+as a solution of type 2 puzzles. The objective is to understand the
+strengths and the weaknesses of each one, to build up some knowledge
+that will be useful for the next section.
+
+\subsection{General Structure Of The Algorithms}
+
+All the algorithms that will be analyzed are composed of 3 sub algorithms.
+
 \end{document}

### 2023-05-28 LaTeX_paper/paper.tex
fix margins

@@
 \usepackage{etoolbox}
+
+\usepackage[a4paper, total={6.5in, 9in}]{geometry}
 
@@
 work with a “digital” jigsaw puzzle [\ref{fig:figure_digital_puzzle}],
-there aren't papers (at least not popular enough to be searchable)
+but there aren't papers (at least not popular enough to be searchable)
 that try to apply the solution
@@
 this wants to be the first.\newline
-As a Bonus the paper will also cover the creation of a user friendly app
+As a bonus the paper will also cover the creation of a user friendly app
 that will be open source and free to use.

### 2023-05-28 c#_desktop_app/JigsawGenius/WinFormsApp1/Program.cs

@@ -12,8 +12,8 @@ namespace JigsawGenius
         static void Main()
         {
 
-            //Comunicator c = new comunicator("c:\\users\\lucas\\clionprojects\\puzzle_solver\\cpp_lib\\work_path\\status.txt");
-            //return;
+            Comunicator c = new Comunicator("c:\\users\\lucas\\clionprojects\\puzzle_solver\\cpp_lib\\work_path\\");
+            return;
             // To customize application configuration such as set high DPI settings or default font,
             // see https://aka.ms/applicationconfiguration.
             ApplicationConfiguration.Initialize();

### 2023-05-29 LaTeX_paper/paper.tex
LaTeX: finish general structure of algorithms

@@
 
+% to set the margin of the page
 \usepackage[a4paper, total={6.5in, 9in}]{geometry}
+
+% to make indentations
+\usepackage{changepage}
 
@@
 \pretocmd{\thefigure}{F}{}{}
+
+% settings for how to indend the page when neaded
+\newenvironment{indented_section}
+  {\adjustwidth{3em}{0pt}}
+  {\endadjustwidth}
 
@@
 and some clever solutions have already been found. These algorithms are made to
-work with a “digital” jigsaw puzzle [\ref{fig:figure_digital_puzzle}],
+work with a “digital” jigsaw puzzle \ref{fig:figure_digital_puzzle},
 but there aren't papers (at least not popular enough to be searchable)
 that try to apply the solution
-to a “real world” jigsaw puzzle [\ref{fig:figure_real_puzzle}].\newline
+to a “real world” jigsaw puzzle \ref{fig:figure_real_puzzle}.\newline
 The problem has been tackled by some small projects. But, as said earlier,
-the process and eventual challenges has never been documented by a paper,
+the process and eventual challenges has never been documented by a full paper,
 this wants to be the first.\newline
@@
 
-All the algorithms that will be analyzed are composed of 3 sub algorithms.
+All the algorithms that will be analyzed are composed of 3 sub algorithms:
+
+\begin{indented_section}
+
+    \subsubsection{The Splitter:} This component takes as input one or more images
+    containing all the pieces. It then split all the pieces from each other,
+    9and split each piece into his four sides.\label{document:splitter}
+
+    \subsubsection{The Comparator:} This component compares each side with all the
+    others, in order to understand whether they match or not.\newline
+    There are two distinct kinds of “Comparator” algorithms:
+    The “Binary Comparison” and the “Non Binary Comparison”.
+    As the name suggests when comparing two sides with a “Binary Comparison”
+    the result can either be 0 (they do not match) or 1 (they match).
+    In contrast a “Non Binary Comparison” can give any value between 0 and 1.
+    This allows states of uncertainty to be represented.\label{document:comparator}
+
+    \subsubsection{The Solver:} This component  uses the information provided by the
+    Comparator \ref{document:comparator}, and tries to find a solution
+    (i.e.\ a position and an orientation for each piece)
+    that is the most likely to be correct.\label{document:solver}
+
+\end{indented_section}
+
+\subsection{Solving Jigsaw Puzzles By The Graph Connection Laplacian}
 

### 2023-06-02 LaTeX_paper/paper.tex
add reference template

@@
 and some clever solutions have already been found. These algorithms are made to
-work with a “digital” jigsaw puzzle \ref{fig:figure_digital_puzzle},
+work with a “digital” jigsaw puzzle~\ref{fig:figure_digital_puzzle},
 but there aren't papers (at least not popular enough to be searchable)
 that try to apply the solution
-to a “real world” jigsaw puzzle \ref{fig:figure_real_puzzle}.\newline
+to a “real world” jigsaw puzzle~\ref{fig:figure_real_puzzle}.\newline
 The problem has been tackled by some small projects. But, as said earlier,
@@
     \subsubsection{The Solver:} This component  uses the information provided by the
-    Comparator \ref{document:comparator}, and tries to find a solution
+    Comparator~\ref{document:comparator}, and tries to find a solution
     (i.e.\ a position and an orientation for each piece)
@@
 
-\end{document}
+\cite{lamport94}
+
+\begin{thebibliography}{9}
+
+  \bibitem{lamport94}
+    Leslie Lamport,
+    \textit{\LaTeX: a document preparation system},
+    Addison Wesley, Massachusetts,
+    2nd edition,
+    1994.
+
+  \end{thebibliography}\end{document}

### 2023-06-02 c#_desktop_app/JigsawGenius/WinFormsApp1/Program.cs

@@ -12,8 +12,8 @@ namespace JigsawGenius
         static void Main()
         {
 
-            Comunicator c = new Comunicator("c:\\users\\lucas\\clionprojects\\puzzle_solver\\cpp_lib\\work_path\\");
-            return;
+            //Comunicator c = new Comunicator("c:\\users\\lucas\\clionprojects\\puzzle_solver\\cpp_lib\\work_path\\");
+            //return;
             // To customize application configuration such as set high DPI settings or default font,
             // see https://aka.ms/applicationconfiguration.
             ApplicationConfiguration.Initialize();

### 2023-06-02 LaTeX_paper/paper.tex
add reference to GCL
backup commit

@@
 
-\subsection{Solving Jigsaw Puzzles By The Graph Connection Laplacian}
+\subsection{Solving Jigsaw Puzzles By The Graph Connection Laplacian~\cite{GCL}}
+This algorithm falls in the “binary comparison” category~\ref{document:comparator}.
+And can be used to understand the strength and weaknesses
+of this approach.\newline
+The main benefit of this approach is speed,  having a binary comparison allows
+some specific optimization, in particular the use of some graph theory techniques.\newline
+The  algorithm has a time complexity of ruffly \(O(N^2)\). Which is in line with the theoretical
+minimum for jigsaw puzzle solving, according to the study:
+\footnotesize{“No easy puzzles: Hardness results for jigsaw puzzles~\cite{ON2Claim}”}.
 
-\cite{lamport94}
+\subsection{A Genetic Algorithm-Based Solver for Very Large Jigsaw Puzzles~\cite{GA}}
 
+% referneces page
+\newpage
 \begin{thebibliography}{9}
 
-  \bibitem{lamport94}
-    Leslie Lamport,
-    \textit{\LaTeX: a document preparation system},
-    Addison Wesley, Massachusetts,
-    2nd edition,
-    1994.
+  %Graph Connection Laplacian
+  \bibitem{GCL}
+    Vahan Huroyan, Gilad   Lerman and Hau-Tieng Wu,
+    Solving Jigsaw Puzzles By The Graph Connection Laplacian,
+    2020.
+    \url{https://arxiv.org/pdf/1811.03188.pdf}.
 
-  \end{thebibliography}\end{document}
+  % Genetic algorighm
+  \bibitem{GA}
+    Dror Sholomon, Omid David and Nathan S. Netanyahu,
+    A Genetic Algorithm-Based Solver for Very Large Jigsaw Puzzles,
+    2013.
+    \url{https://openaccess.thecvf.com/content_cvpr_2013/papers/Sholomon_A_Genetic_Algorithm-Based_2013_CVPR_paper.pdf}.
+
+    % Claim of best solution O(N^2)
+    \bibitem{ON2Claim}
+    Michael Brand,
+    No easy puzzles: Hardness results for jigsaw puzzles,
+    2015.
+    \url{https://www.sciencedirect.com/science/article/pii/S0304397515001607}.
+
+\end{thebibliography}
+
+\end{document}

### 2023-06-05 LaTeX_paper/paper.tex
finish latex section 3.2 (GCL)

@@
 minimum for jigsaw puzzle solving, according to the study:
-\footnotesize{“No easy puzzles: Hardness results for jigsaw puzzles~\cite{ON2Claim}”}.
+“No easy puzzles: Hardness results for jigsaw puzzles~\cite{ON2Claim}”.\newline
+The negative aspect might be the accuracy, since by using only two states
+(match or not match) some informations are lost, compared to a non binary comparison.
+To quantify accuracy the paper used the “neighbors comparison” metric,
+which “calculates the percentage of pairs of image patches that are matched correctly”.\newline
+Is important to note that the discussed algorithm works with 
+digital puzzles~\ref{fig:figure_digital_puzzle}, and this gives it the advantage of having more precise data.\newline
+Whether this algorithm could work with a real world puzzle~\ref{fig:figure_real_puzzle} will be discussed in section DOTO INSERT RFERENCE.
 

### 2023-06-05 LaTeX_paper/paper.tex
finish section 3.3 (GA)

@@
 
+This paper applies a genetic algorithm to the jigsaw puzzle problem, with some promising results.\newline
+The algorithm seems to have a \(O(N^2)\) time complexity, with time slightly lower than the previous example
+(But it is impossible to know for sure which one is faster, given that they didn't specify the hardware used).\newline
+The paper has used the same method to evaluate accuracy that the previous one used
+(neighbors comparison) so it is easy to compare them.\newline
+The algorithm falls in the “Non binary comparison”~\ref{document:comparator};
+this should give it an advantage, since it has more data to work with.\newline
+Unfortunately this advantage does not compensate for the worst precision
+of the algorithm itself, and the accuracy results are equivalent,
+if not slightly worse than the previous algorithm.\newline
+It is important to keep in mind that for the very nature of genetic algorithms,
+it might be possible that the accuracy would have been better if they had allowed
+it to run for more generations.\newline
+Is also important to note that the discussed algorithm works with digital puzzles,
+and this gives it the advantage of having more precise data.\newline
+Whether this algorithm could work with a real world puzzle will be discussed
+in section DOTO INSERT RFERENCE.
+
 % referneces page

### 2023-06-10 LaTeX_paper/paper.tex
Add third example and objective to paper

--- 2023-06-05 LaTeX_paper/paper.tex
@@
 
-There is  another important distinction between different types of puzzles. They can be divided into “digital” and “real world” jigsaw puzzles.
+There is  another important distinction between different types of puzzles.
+They can be divided into “digital” and “real world” jigsaw puzzles.
+\label{document:DigitalVSReal}
 
@@
 which “calculates the percentage of pairs of image patches that are matched correctly”.\newline
-Is important to note that the discussed algorithm works with 
-digital puzzles~\ref{fig:figure_digital_puzzle}, and this gives it the advantage of having more precise data.\newline
-Whether this algorithm could work with a real world puzzle~\ref{fig:figure_real_puzzle} will be discussed in section DOTO INSERT RFERENCE.
+\label{document:GCL}
 
 \subsection{A Genetic Algorithm-Based Solver for Very Large Jigsaw Puzzles~\cite{GA}}
+This paper applies a genetic algorithm to the jigsaw puzzle problem, with some promising results.\newline
+The algorithm seems to have a \(O(N^2)\) time complexity, with time slightly lower than the previous example
+(But it is impossible to know for sure which one is faster, given that they didn't specify the hardware used).\newline
+The paper has used the same method to evaluate accuracy that the previous one used
+(neighbors comparison) so it is easy to compare them.\newline
+The algorithm falls in the “Non binary comparison”~\ref{document:comparator};
+this should give it an advantage, since it has more data to work with.\newline
+Unfortunately this advantage does not compensate for the worst precision
+of the algorithm itself, and the accuracy results are equivalent,
+if not slightly worse than the previous algorithm.\newline
+It is important to keep in mind that for the very nature of genetic algorithms,
+it might be possible that the accuracy would have been better if they had allowed
+it to run for more generations.\newline
+\label{document:GA}
+
+\subsection{Computer Vision Powers Automatic Jigsaw Puzzle Solver~\cite{Abto}}
+The solutions~\ref{document:GCL} and~\ref{document:GA} can be considered “state of the art” for digital jigsaw puzzles.
+But, as already introduced in section~\ref{document:DigitalVSReal} and better explained in section TODO,
+appalling the solution to the real world can be challenging.\newline
+This solution is possibly a “state of the art” for real world puzzles.\newline
+In reality calling this a “solution” is incorrect,
+since all it does is find the best 8 matches and asks the user which one to place.
+Making the algorithm not autonomous.\newline
+Even ignoring this major detail, making an analysis of this solution has proven to be challenging,
+since the article is more of a publicity stunt than an academic paper.
+In fact, the code is not open source and the information about the time needed to solve the puzzle is missing.\newline
+The article only shows a single puzzle solved, with a 9x6 dimension.\newline
+Even with all of these problems this article still is one of the best example of a solution for real world puzzle.
+
+\section{The objective of this paper}
+After reading some of the previous literature for this problem, some conclusions could be drawn:
+The problem of “digital jigsaw puzzle” has been solved many times, and is already well optimized.\newline
+On the other hand, the problem of “real world jigsaw puzzle” has mostly been ignored\newline
+by the academic community.\newline
+
+The objective of this paper is to fill this void, by answering the following questions:
+\begin{itemize}
+    \item Can the current state of the art solutions for digital puzzles be used for real world puzzles, or the unpredictable nature of real world data makes it impossible?
+    \item If the algorithms cannot be applied to the real world, what is a possible solution that is more redundant to imprecise data?
+
+  \end{itemize}
 
@@
 
+    % abtosoftware real world solution
+    \bibitem{Abto}
+    AbtoSoftware,
+    Computer Vision Powers Automatic Jigsaw Puzzle Solver,
+    2019.
+    \url{https://www.abtosoftware.com/blog/computer-vision-powers-automatic-jigsaw-puzzle-solver}.
+
 \end{thebibliography}

### 2023-06-11 cpp_lib/pre_processing/dataset_processing.cpp
fix CMakeLists.txt opencv finder

@@ -7,7 +7,7 @@ using namespace cv;
 
 
 // on my 5700u laptop this function can process around 110 images/minute
-int deprecated_main(){
+int main(){
 
     string path = "../test_4x4";
 

### 2023-06-11 cpp_lib/pre_processing/dataset_processing.cpp
fix preview in split_pieces_into_single_images function

@@ -9,14 +9,14 @@ using namespace cv;
 // on my 5700u laptop this function can process around 110 images/minute
 int main(){
 
-    string path = "../test_4x4";
+    string path = "../../../dataset/test_4x4";
 
     int number_of_pieces = 500;
-    number_of_pieces = split_pieces_into_single_images(path + "/raw",path + "/divided",1200, false);
+    number_of_pieces = split_pieces_into_single_images(path + "/raw",path + "/divided",1200, true);
 
     cout << "i have found " << number_of_pieces << " puzzle_preview pieces" << endl;
 
-    do_pre_processing(path+"/divided",number_of_pieces, 1200, true, false);
+    //do_pre_processing(path+"/divided",number_of_pieces, 1200, true, false);
 
     cout << "preprocessing finished" << endl;
 

### 2023-06-11 cpp_lib/pre_processing/piece_splitting.cpp

@@ -199,17 +199,21 @@ int split_pieces_into_single_images(const std::string& input_path,const std::str
                 // crop it
                 Mat cropped_image = single_piece(Range(y1,y2),Range(x1,x2));
 
-                if(PreviewManager::is_preview_enabled()){
+                if(PreviewManager::is_preview_enabled() || enable_image_view){
                     Mat cropped_image_resized;
                     Mat to_target_resized;
                     resize(cropped_image, cropped_image_resized, Size(400, 400));
                     Mat to_target = image;
                     rectangle(to_target, Point(x1, y1), Point(x2, y2), Scalar(255, 0, 0, 0), 30);
                     resize(to_target, to_target_resized, Size(550, 800));
-//                    imshow("output", cropped_image_resized);
-//                    imshow("where", to_target_resized);
-//                    waitKey(0);
-                    PreviewManager::output_preview_image(to_target_resized);
+                    if(enable_image_view){
+                        imshow("output", cropped_image_resized);
+                        imshow("where", to_target_resized);
+                        waitKey(0);
+                    }
+                    if(PreviewManager::is_preview_enabled()){
+                        PreviewManager::output_preview_image(to_target_resized);
+                    }
                 }
 
 

### 2023-06-11 cpp_lib/pre_processing/corner_finding.cpp
add better preview and take images for paper

@@ -15,10 +15,27 @@ using namespace std;
 using namespace cv;
 
 void do_pre_processing_thread(const std::string& path, int piece_index, int ppi = DEFAULT_PPI, bool enable_image_view = false);
-void remove_holes(const cv::Mat &input, cv::Mat &output,int ppi = DEFAULT_PPI);
-void remove_knobs(const cv::Mat &input, cv::Mat &output, int ppi = DEFAULT_PPI);
-void find_corners(const cv::Mat &input, cv::Point &p1,  cv::Point &p2,  cv::Point &p3,  cv::Point &p4, int ppi = DEFAULT_PPI);
+void remove_holes(const cv::Mat &input, cv::Mat &output,int ppi = DEFAULT_PPI, bool enable_image_view = false);
+void remove_knobs(const cv::Mat &input, cv::Mat &output, int ppi = DEFAULT_PPI, bool enable_image_view = false);
+void find_corners(const cv::Mat &input, cv::Point &p1,  cv::Point &p2,  cv::Point &p3,  cv::Point &p4, int ppi = DEFAULT_PPI, bool enable_image_view = false);
 
+// handle the resize and the condition for a quick preview
+void quick_image_preview(const cv::Mat &image, bool enable_preview, const string& name_of_image_to_save = ""){
+    if(!enable_preview){
+        return;
+    }
+
+
+    if(!name_of_image_to_save.empty()){
+        imwrite(name_of_image_to_save + ".png", image);
+    }
+
+    Mat resize;
+    cv::resize(image,resize,image.size()/3);
+
+    imshow("preview", resize);
+    waitKey(0);
+}
 
 void find_corners(const std::string& path, int number_of_pieces, int ppi, int number_of_cores, bool enable_image_view){
 
@@ -88,15 +105,15 @@ void do_pre_processing_thread(const std::string& path, int piece_index, int ppi,
 
     // removing the hole of the piece
     Mat piece_no_holes;
-    remove_holes(piece,piece_no_holes,ppi);
+    remove_holes(piece,piece_no_holes,ppi,enable_image_view);
 
     // removing the knobs
     Mat piece_no_knobs;
-    remove_knobs(piece_no_holes,piece_no_knobs,ppi);
+    remove_knobs(piece_no_holes,piece_no_knobs,ppi,enable_image_view);
 
     // finding the points
     Point p1,p2,p3,p4;
-    find_corners(piece_no_knobs,p1,p2,p3,p4,ppi);
[…]

### 2023-06-11 cpp_lib/pre_processing/dataset_processing.cpp

@@ -11,12 +11,12 @@ int main(){
 
     string path = "../../../dataset/test_4x4";
 
-    int number_of_pieces = 500;
-    number_of_pieces = split_pieces_into_single_images(path + "/raw",path + "/divided",1200, true);
+    int number_of_pieces = 16;
+    //number_of_pieces = split_pieces_into_single_images(path + "/raw",path + "/divided",1200, true);
 
     cout << "i have found " << number_of_pieces << " puzzle_preview pieces" << endl;
 
-    //do_pre_processing(path+"/divided",number_of_pieces, 1200, true, false);
+    find_corners(path+"/divided",number_of_pieces, 1200, 1, true);
 
     cout << "preprocessing finished" << endl;
 

### 2023-06-11 LaTeX_paper/paper.tex
paper backup

@@
 \usepackage{changepage}
+
+% for sub figures
+\usepackage{subcaption}
 
@@
     \centering
-
 \end{figure}
@@
 In fact, the code is not open source and the information about the time needed to solve the puzzle is missing.\newline
-The article only shows a single puzzle solved, with a 9x6 dimension.\newline
+The article only shows a single puzzle solved, with a 9$\times$6 dimension.\newline
 Even with all of these problems this article still is one of the best example of a solution for real world puzzle.
 
-\section{The objective of this paper}
+\section{The Objective Of This Paper}
 After reading some of the previous literature for this problem, some conclusions could be drawn:
@@
 
+\section{The Setup}
+
+To answer these questions, some data to start with,
+and an algorithm to analyze the data; in particular the necessary components are:
+
+\subsection{The Puzzle To Solve}
+
+The first step is finding a real world puzzle to solve;
+It has been decided to use a classic 500 piece puzzle, and use a printer's
+scanner to digitize the pieces.\newline
+The puzzle has been scanned in various sub-sizes to allow the testing of different configurations. 
+A resolution of 1200 ppi has been used to ensure a sharp and precise image
+of the piece, as seen in image~\ref{fig:figure_measurement_error}.
+The puzzle has been scanned backward, since the comparator algorithm
+that has been used REF does not use colors,
+and having an uniform color would make splitting the pieces easier.
+
+\subsection{Splitting The Pieces}
+As introduced in section~\ref{document:splitter}, the first step to solve a puzzle
+is to split an image composed of many pieces into individual ones.
+This is relatively straightforward, and can be done with the following steps:
+
+\begin{itemize}
+  \item Apply a threshold and transform an RGB image into a binary mask.
+  \item Find all individual Blobs
+  (a Blob is just set of connected pixels with the same color) and for each one:
+
+  \begin{itemize}
+  \item Calculate the area (the number of pixels the Blob is made of)
+
+  \item Add it to the set of pieces only if his area in within a certain range (to avoid small pieces of dust ending up counted as pieces)
+
+  \end{itemize}
+
+\end{itemize}
+
+\subsection{Splitting The Sides}
+
+The next step following the general template~\ref{document:splitter}
+is to split a pieces into
+his 4 sides, this could be done with the following steps:
+
+\begin{itemize}
+
+  \item \textbf{Remove the holes from the piece:}\newline
+  To do so the program computes the convex hull of the piece,
+  then calculates the difference between the convex hull and the original image,
+  and obtains an image with the “filler areas”.
+  These filler areas have very different shapes,
+  depending on what has generated them (a “hole” or a “knob” in the piece).
+  So they can be classified, and added to the original piece only if
+  they are generated by a hole, obtaining an image without holes.
+
+  \item \textbf{Remove the knobs from he piece}\newline
+  To do so the image without holes gets eroded and then dilated.
+  This generates an image that resembles the original one, but has no knobs.
+  Then the program finds the pixels that are white in the image without holes,
+  but not in the image that has been eroded and dilated. This generates a set of Blobs,
+  but again, the shape of the blob is very different depending on what has generated it
+  (an “angle” or a “knob”), so they can be classified.
+  Then the program removes from the image with no holes all the pixels that are
+  close to a Blob generated by a knob, obtaining an image without knobs and holes.
+
+\end{itemize}
+
+\begin{figure}
+  \begin{subfigure}{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{pictures/remove_holes_convex_hull.png}
+    \caption{Caption for Image 1}
+    \label{fig:image1}
+  \end{subfigure}
+  \begin{subfigure}{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{pictures/remove_holes_convex_hull.png}
+    \caption{Caption for Image 2}
+    \label{fig:image2}
+  \end{subfigure}
+  \caption{Overall caption for the figure}
+  \label{fig:overall}
+\end{figure}
+
 % referneces page
@@
     \url{https://arxiv.org/pdf/1811.03188.pdf}.
-
   % Genetic algorighm

### 2023-06-11 cpp_lib/pre_processing/corner_finding.cpp
add preview for corner finding

@@ -444,9 +444,24 @@ void find_corners(const cv::Mat &input, cv::Point &p1,  cv::Point &p2,  cv::Poin
 
     // find the rectangle
     RotatedRect rect = minAreaRect( main_contour);
+
     // find the 4 points;
     Point2f vertices[4];
     rect.points(vertices);
+
+    if(enable_image_view){
+        Mat preview;
+        cvtColor(piece_with_no_knobs,preview,COLOR_GRAY2BGR);
+
+        for(int i=0; i<4; i++){
+            auto p1 = vertices[i];
+            auto p2 = vertices[(i+1)%4];
+
+            line(preview,p1,p2,Scalar(0,0,255),15);
+        }
+        quick_image_preview(preview,enable_image_view,"find_corners_min_enclosing_rectangle");
+    }
+
 
     //
     //      APPROXIMATION 2
@@ -564,6 +579,18 @@ void find_corners(const cv::Mat &input, cv::Point &p1,  cv::Point &p2,  cv::Poin
         minEnclosingTriangle( main_contour,triangle_points);
         //cout << triangle_points << endl;
 
+        if(enable_image_view){
+            Mat preview;
+            cvtColor(single_corner,preview,COLOR_GRAY2BGR);
+
+            for(int i=0; i<3; i++){
+                auto p1 = triangle_points[i];
+                auto p2 = triangle_points[(i+1)%3];
+
+                line(preview,p1,p2,Scalar(0,0,255),4);
+            }
+            quick_image_preview(preview,enable_image_view,"find_corners_min_enclosing_triangle");
+        }
 
 
         // find the point that is the closest to the original point...

### 2023-06-11 LaTeX_paper/paper.tex
add new images

@@
 
+  \item \textbf{Find the coordinates of the four corners}\newline
+  To find the coordinates of the corners, the program uses a tree steps approximation.
+  It initially finds the minimum enclosing rectangle,
+  and uses the coordinates of the corners of the rectangle
+  as first approximation.\newline
+  As a second approximation it takes
+  the white pixel that is closest to the first approximation.
+  Then it considers only the pixels that are within a certain
+  distance of the second approximation, and finds the minimum
+  enclosing triangle of sed pixels.\newline
+  The corner of the triangle that is closest to the second
+  approximation is the third and final approximation
+  of the corner of the piece.
+
+  \item \textbf{Split each side using the previously found coordinates.}\newline
+	Once the program has found the four coordinates of the corners, to obtain each
+  side,it just needs to rotate and crop the piece, and so obtain a single side.
 \end{itemize}

### 2023-06-11 cpp_lib/main_test.cpp

@@ -28,8 +28,8 @@ void debug_thread(){
 
 int main(){
 
-    PuzzleSolver ps(4, 4, "../work_path", "../../dataset/test_4x4/raw",2);
-    //PuzzleSolver ps("../work_path");
+    //PuzzleSolver ps(4, 4, "../work_path", "../../dataset/test_4x4/raw",2);
+    PuzzleSolver ps("../work_path");
 
     ps.set_threshold(100);
 

### 2023-06-11 cpp_lib/solving/graphic_piece/Side.cpp

@@ -56,6 +56,7 @@ Side::Side(Mat& shape, PieceShape* piece_, int piece_side_, Point p1, Point p2, 
     // applying the threshold since the transformation has blurred the border
     border_shape = border_shape>127;
 
+
     //creating 2 lines from the 2 points to the border of the image
     line(border_shape,p1,p1+(p1-p2), Scalar(255),3);
     line(border_shape,p2,p2+(p2-p1), Scalar(255),3);
@@ -67,7 +68,6 @@ Side::Side(Mat& shape, PieceShape* piece_, int piece_side_, Point p1, Point p2, 
     // flood filling significant points to keep only one border
     floodFill(border_shape,Point(0,0),100);
     border_shape = border_shape != 100;
-
 
     int difference = Side::compare_res*Side::compare_res/2 - countNonZero(border_shape);
 

### 2023-06-11 LaTeX_paper/paper.tex
latex paper backup

@@
 \begin{figure}
-  \begin{subfigure}{0.5\textwidth}
+  \begin{subfigure}{0.3\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{pictures/original_piece.jpeg}
+    \caption{Original binary mask of a piece.}
+    \label{fig:image1}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}{0.3\textwidth}
     \centering
     \includegraphics[width=\linewidth]{pictures/remove_holes_convex_hull.png}
-    \caption{Caption for Image 1}
-    \label{fig:image1}
-  \end{subfigure}
-  \begin{subfigure}{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{pictures/remove_holes_convex_hull.png}
-    \caption{Caption for Image 2}
+    \caption{Convex Hull of a piece.}
     \label{fig:image2}
   \end{subfigure}
-  \caption{Overall caption for the figure}
-  \label{fig:overall}
+  \hfill
+  \begin{subfigure}{0.3\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{pictures/remove_holes_filler_areas.png}
+    \caption{Difference between (b) and (a).}
+    \label{fig:image3}
+  \end{subfigure}
+  %\vspace{1cm}
+  \begin{subfigure}{0.3\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{pictures/piece_with_no_hole.png}
+    \caption{Piece (a) with holes removed.}
+    \label{fig:image4}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}{0.3\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{pictures/remove_knobs_erosion.png}
+    \caption{Mask (d) eroded.}
+    \label{fig:image5}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}{0.3\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{pictures/remove_knobs_expansion.png}
+    \caption{Mask (e) dilated.}
+    \label{fig:imag6}
+  \end{subfigure}
+  \caption{Steps needed to split an image into his four sides.}
+  \label{fig:splitting_sides}
+
 \end{figure}

### 2023-06-12 LaTeX_paper/paper.tex
Latex paper: finish immage grid

@@
     \caption{Original binary mask of a piece.}
-    \label{fig:image1}
+    \label{fig:s_s_og}
   \end{subfigure}
@@
     \caption{Convex Hull of a piece.}
-    \label{fig:image2}
+    \label{fig:s_s_ch}
   \end{subfigure}
@@
     \includegraphics[width=\linewidth]{pictures/remove_holes_filler_areas.png}
-    \caption{Difference between (b) and (a).}
-    \label{fig:image3}
+    \caption{Difference:~\ref{fig:s_s_ch} \textminus~\ref{fig:s_s_og}.}
+    \label{fig:fig:s_s_og_minus_ch}
   \end{subfigure}
-  %\vspace{1cm}
+  \vspace{1cm}
   \begin{subfigure}{0.3\textwidth}
@@
     \includegraphics[width=\linewidth]{pictures/piece_with_no_hole.png}
-    \caption{Piece (a) with holes removed.}
-    \label{fig:image4}
+    \caption{Piece~\ref{fig:s_s_og} with holes removed.}
+    \label{fig:s_s_no_holes}
   \end{subfigure}
@@
     \includegraphics[width=\linewidth]{pictures/remove_knobs_erosion.png}
-    \caption{Mask (d) eroded.}
-    \label{fig:image5}
+    \caption{Mask~\ref{fig:s_s_no_holes} eroded.}
+    \label{fig:s_s_erosion}
   \end{subfigure}
@@
     \includegraphics[width=\linewidth]{pictures/remove_knobs_expansion.png}
-    \caption{Mask (e) dilated.}
-    \label{fig:imag6}
+    \caption{Mask~\ref{fig:s_s_erosion} dilated.}
+    \label{fig:s_s_expansion}
   \end{subfigure}
+  \vspace{1cm}
+  \begin{subfigure}{0.3\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{pictures/remove_knobs_knob_pixels.png}
+    \caption{Difference:~\ref{fig:s_s_no_holes} \textminus~\ref{fig:s_s_expansion}.}
+    \label{fig:s_s_no_holes_minus_expansion}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}{0.3\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{pictures/piece_with_no_knobs.png}
+    \caption{Piece~\ref{fig:s_s_no_holes} with knobs removed.}
+    \label{fig:s_s_no_knobs}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}{0.3\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{pictures/find_corners_min_enclosing_rectangle.png}
+    \caption{Min enclosing rectangle of~\ref{fig:s_s_no_knobs}.}
+    \label{fig:s_s_min_enc_rec}
+  \end{subfigure}
+\end{figure}
+\clearpage
+\begin{figure}\ContinuedFloat
+  \begin{subfigure}{0.3\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{pictures/find_corners_min_enclosing_triangle.png}
+    \caption{Min enclosing triangle of the bottom right corner of~\ref{fig:s_s_no_knobs}.}
+    \label{fig:s_s_min_enc_triangle}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}{0.3\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{pictures/corners_found.png}
+    \caption{The corners of the piece~\ref{fig:s_s_og}.}
+    \label{fig:s_s_corners_found}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}{0.3\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{pictures/piece_side.png}
+    \caption{One of the sides of the piece~\ref{fig:s_s_og}.}
+    \label{fig:s_s_a_piece_side}
+  \end{subfigure}
+
   \caption{Steps needed to split an image into his four sides.}
@@
 % referneces page
-\newpage
+\clearpage
 \begin{thebibliography}{9}

### 2023-06-12 LaTeX_paper/paper.tex
Latex paper commit

@@
   \item \textbf{Remove the holes from the piece:}\newline
-  To do so the program computes the convex hull of the piece,
+  To do so the program computes the convex hull of the piece~\ref{fig:s_s_ch},
   then calculates the difference between the convex hull and the original image,
-  and obtains an image with the “filler areas”.
+  and obtains an image with the “filler areas”~\ref{fig:fig:s_s_og_minus_ch}.
   These filler areas have very different shapes,
@@
   So they can be classified, and added to the original piece only if
-  they are generated by a hole, obtaining an image without holes.
+  they are generated by a hole, obtaining an image without holes~\ref{fig:s_s_no_holes}.
 
   \item \textbf{Remove the knobs from he piece}\newline
-  To do so the image without holes gets eroded and then dilated.
+  To do so the image without holes gets eroded~\ref{fig:s_s_erosion} and then dilated~\ref{fig:s_s_dilatation}.
   This generates an image that resembles the original one, but has no knobs.
   Then the program finds the pixels that are white in the image without holes,
-  but not in the image that has been eroded and dilated. This generates a set of Blobs,
+  but not in the image that has been eroded and dilated.
+  This generates a set of Blobs~\ref{fig:s_s_no_holes_minus_expansion},
   but again, the shape of the blob is very different depending on what has generated it
@@
   Then the program removes from the image with no holes all the pixels that are
-  close to a Blob generated by a knob, obtaining an image without knobs and holes.
+  close to a Blob generated by a knob, obtaining an image without knobs and holes~\ref{fig:s_s_no_knobs}.
 
@@
   and uses the coordinates of the corners of the rectangle
-  as first approximation.\newline
-  As a second approximation it takes
-  the white pixel that is closest to the first approximation.
+  as first approximation~\ref{fig:s_s_min_enc_rec}.\newline
+  As a second approximation it takes,
+  from the white pixels that are close to the first approximation,
+  the pixel that has the most black pixels within a certain distance.
   Then it considers only the pixels that are within a certain
   distance of the second approximation, and finds the minimum
-  enclosing triangle of sed pixels.\newline
+  enclosing triangle of sed pixels~\ref{fig:s_s_min_enc_triangle}.\newline
   The corner of the triangle that is closest to the second
@@
   of the corner of the piece.
+  The position of the four corners can be seen in image~\ref{fig:s_s_corners_found}.
 
@@
 	Once the program has found the four coordinates of the corners, to obtain each
-  side,it just needs to rotate and crop the piece, and so obtain a single side.
+  side. An example of a single side can be seen in image~\ref{fig:s_s_a_piece_side}.
 \end{itemize}
@@
     \caption{Mask~\ref{fig:s_s_erosion} dilated.}
-    \label{fig:s_s_expansion}
+    \label{fig:s_s_dilatation}
   \end{subfigure}
@@
     \includegraphics[width=\linewidth]{pictures/remove_knobs_knob_pixels.png}
-    \caption{Difference:~\ref{fig:s_s_no_holes} \textminus~\ref{fig:s_s_expansion}.}
+    \caption{Difference:~\ref{fig:s_s_no_holes} \textminus~\ref{fig:s_s_erosion}.}
     \label{fig:s_s_no_holes_minus_expansion}

### 2023-06-23 cpp_lib/solving/calculate_connections.cpp
add image to paper

@@ -56,6 +56,12 @@ void piece_comparer_thread(PieceConnection *pieces_connections, PieceShape *piec
                         compatibility = 0;
                     }
 
+
+                    //Mat preview = pieces_shapes[piece_id].get_side(piece_side).get_compare_image(
+                    //        pieces_shapes[other_piece_id].get_side(other_piece_side)
+                    //        );
+                    //imwrite("comparison.png",preview);
+
                     if(PreviewManager::is_preview_enabled()){
                         Mat img = pieces_shapes[piece_id].get_side(piece_side).get_compare_image(
                                 pieces_shapes[other_piece_id].get_side(other_piece_side)

### 2023-06-23 LaTeX_paper/paper.tex
add section 5.4 to paper

@@
 \usepackage{subcaption}
+
+% to allow putting description text to te side of an image
+\usepackage{wrapfig}
 
@@
 
+\subsection{Comparing the sides}
+The last step needed before it is possible to start working on
+a solver algorithm, is to compare the sides that have been
+generated by the previous step.\newline
+In order to generate a compatibility shore,
+the program compute the following steps:
+
+\begin{itemize}
+  \item For each side, it considers only the border, and it makes the border thicker.
+  \item It puts two sides attached to each other using the coordinates of the corners (In the same way a human would do to test if two pieces fit together).
+  \item It calculates the “Or Area”; that is, the number of pixels that belong to the border of one side or the other.
+  \item It calculates the “And Area”; that is, the number of pixels that belong to the border of both sides.
+  \item It calculates the final shore, which is defined as: \(Shore = \frac{And \space Area}{Or \space Area}\), and goes from 0 to 1.
+\end{itemize}
+
+\begin{figure}[htbp]
+  \centering
+  \begin{minipage}[t]{0.44\textwidth}
+    \vspace{3pt} % Ensure alignment of the top of the minipage
+    \includegraphics[width=\textwidth]{pictures/side_comparation.png}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[t]{0.54\textwidth}
+    \caption{\newline
+    In this image we can see two sides that have been
+    compared, one side is drowned in red, the other one in blue.
+    In this picture, the “Or Area” is represented by all non
+    black pixels; The “And Area” is represented by all the
+    purple pixels.}
+  \end{minipage}
+\end{figure}
+\cleardoublepage
+
 % referneces page

### 2023-06-23 cpp_lib/solving/calculate_connections.cpp

@@ -59,7 +59,7 @@ void piece_comparer_thread(PieceConnection *pieces_connections, PieceShape *piec
 
                     //Mat preview = pieces_shapes[piece_id].get_side(piece_side).get_compare_image(
                     //        pieces_shapes[other_piece_id].get_side(other_piece_side)
-                    //        );
+                    //        );    
                     //imwrite("comparison.png",preview);
 
                     if(PreviewManager::is_preview_enabled()){

### 2023-06-25 LaTeX_paper/paper.tex
backup commit
fix typo on paper
add section 6 and 6.1 to paper

@@
 strengths and the weaknesses of each one, to build up some knowledge
-that will be useful for the next section.
+that will be useful for the next sections.
 
@@
 
-\subsection{Comparing the sides}
+\subsection{Comparing the sides}\label{document:my_comparator}
 The last step needed before it is possible to start working on
@@
 \end{figure}
-\cleardoublepage
+\clearpage
+
+\section{Apling already existing algorithm to the real world}
+Now that the setup is completed, it is possible to test the already existing
+algorithms with real world puzzles, to see if they can work. For this test,
+the fist algorithm~\ref{document:GCL} has been chosen, because the paper is full of detail.
+In particular it had some information about the accuracy of the algorithm in
+function to the corruption rate, which are essential for this analysis.
+\newline \newline
+The tests that have been conducted have shown that our comparator algorithm~\ref{document:my_comparator}
+and the “Graph Connection Laplacian” solution~\ref{document:GCL} are not compatible with each other.
+A proof for this claim follows.
+
+\subsection{Proof}
+
+This section will provide a proof for the incompatibility of
+the two algorithms mentioned above.
+\newline \newline
+The comparison algorithm deceived in section~\ref{document:my_comparator} outputs a compatibility
+shore that goes from 0 to 1.\newline
+But the algorithm~\ref{document:GCL} takes as input a binary value,
+which means that it is necessary to apply a threshold to the input
+data to convert them from float to bool.
+\newline \newline
+To find the optimal threshold a small 16 piece puzzle has been solved.
+And the following 4 values have been measured, in function of the threshold:
+
+\begin{itemize}
+  \item \textbf{match\%:}\newline
+  The probability that 2 random sides match.
+
+  \item \textbf{correct combination match\% (or c.c match\%):}\newline
+  The probability that 2 sides match given that in the correct puzzle
+  solution they actually are close to each other. ideally this should be 1.
+
+  \item \textbf{limit match\%:}\newline
+  Given that this measure has been taken on a 16 piece puzzle,
+  the match\% is highly influenced by the correct piece matching.
+  With a bigger puzzle the match\% would be lower.
+  Limit match\% is an approximation of what the match\%
+  would be in the limit for \(N \rightarrow + \infty\) (where N is the number of pieces).
+  This value is obtained by subtracting to match\%
+  the probability of choosing randomly the correct side,
+  multiplied by the probability that the comparison returns true
+  (which is c.c match\%). ideally this should be almost zero.
+  \[limit \: math\% = math\% - \frac{c.c. \: mathc\%}{16 \times 4}\]
+
+  \item \textbf{corruption rate:}\newline
+\end{itemize}
 

### 2023-06-26 LaTeX_paper/paper.tex
add table and graph to paper

@@
 \usepackage{graphicx}
-
-% to have more colors avelable
-\usepackage{xcolor}
 
@@
 \pretocmd{\thefigure}{F}{}{}
+
+% for the table
+\usepackage[table,xcdraw]{xcolor}
+
+% to include svg images
+\usepackage{svg}
 
@@
 
-\subsection{Comparing the sides}\label{document:my_comparator}
+\subsection{Comparing The Sides}\label{document:my_comparator}
 The last step needed before it is possible to start working on
@@
 
-\section{Apling already existing algorithm to the real world}
+\section{Apling Already Existing Algorithms To The Real World}
 Now that the setup is completed, it is possible to test the already existing
@@
   \item \textbf{corruption rate:}\newline
+  Is defined as: \(1-\sqrt{c.c \: match\%}\). ideally this should be 0.
+
 \end{itemize}
+
+% Please add the following required packages to your document preamble:
+% \usepackage[table,xcdraw]{xcolor}
+% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
+\begin{table}[]
+  \centering
+  \begin{tabular}{
+  >{\columncolor[HTML]{FFE599}}c 
+  >{\columncolor[HTML]{B6D7A8}}c 
+  >{\columncolor[HTML]{9FC5E8}}c 
+  >{\columncolor[HTML]{F9CB9C}}c 
+  >{\columncolor[HTML]{D9D2E9}}c }
+  \cline{1-1}
+  \multicolumn{1}{|c|}{\cellcolor[HTML]{F1C232}threshold} &
+    \cellcolor[HTML]{6AA84F}match\% &
+    \cellcolor[HTML]{3C78D8}c.c match\% &
+    \cellcolor[HTML]{E69138}limit match\% &
+    \cellcolor[HTML]{8E7CC3}corruption rate \\ \cline{1-1}
+  0.000 & 1.000 & 1.000 & 0.984 & 0.000 \\
+  0.025 & 0.408 & 1.000 & 0.392 & 0.000 \\
+  0.050 & 0.408 & 1.000 & 0.392 & 0.000 \\
+  0.075 & 0.408 & 1.000 & 0.392 & 0.000 \\
+  0.100 & 0.408 & 1.000 & 0.392 & 0.000 \\
+  0.125 & 0.406 & 1.000 & 0.391 & 0.000 \\
+  0.150 & 0.400 & 1.000 & 0.385 & 0.000 \\
+  0.175 & 0.386 & 1.000 & 0.371 & 0.000 \\
+  0.200 & 0.364 & 1.000 & 0.348 & 0.000 \\
+  0.225 & 0.335 & 1.000 & 0.319 & 0.000 \\
+  0.250 & 0.298 & 1.000 & 0.282 & 0.000 \\
+  0.275 & 0.253 & 1.000 & 0.237 & 0.000 \\
+  0.300 & 0.201 & 1.000 & 0.185 & 0.000 \\
+  0.325 & 0.158 & 1.000 & 0.142 & 0.000 \\
+  0.350 & 0.125 & 0.944 & 0.110 & 0.028 \\
+  0.375 & 0.100 & 0.944 & 0.085 & 0.028 \\
+  0.400 & 0.080 & 0.944 & 0.065 & 0.028 \\
+  \cellcolor[HTML]{FF0000}0.425 &
+    \cellcolor[HTML]{FF0000}0.054 &
+    \cellcolor[HTML]{FF0000}0.889 &
+    \cellcolor[HTML]{FF0000}0.040 &
+    \cellcolor[HTML]{FF0000}0.057 \\
+  0.450 & 0.043 & 0.889 & 0.029 & 0.057 \\
+  0.475 & 0.034 & 0.778 & 0.022 & 0.118 \\
+  0.500 & 0.025 & 0.778 & 0.013 & 0.118 \\
+  0.525 & 0.023 & 0.778 & 0.010 & 0.118 \\
+  0.550 & 0.020 & 0.667 & 0.010 & 0.184 \\
+  0.575 & 0.019 & 0.667 & 0.009 & 0.184 \\
+  0.600 & 0.016 & 0.556 & 0.007 & 0.255 \\
+  0.625 & 0.014 & 0.556 & 0.005 & 0.255 \\
+  0.650 & 0.014 & 0.556 & 0.005 & 0.255 \\
+  0.675 & 0.006 & 0.222 & 0.003 & 0.529 \\
+  0.700 & 0.003 & 0.111 & 0.001 & 0.667 \\
+  0.725 & 0.001 & 0.000 & 0.001 & 1.000 \\
+  0.750 & 0.001 & 0.000 & 0.001 & 1.000 \\
+  0.775 & 0.000 & 0.000 & 0.000 & 1.000 \\
+  0.800 & 0.000 & 0.000 & 0.000 & 1.000 \\
+  0.825 & 0.000 & 0.000 & 0.000 & 1.000 \\
+  0.850 & 0.000 & 0.000 & 0.000 & 1.000 \\
+  0.875 & 0.000 & 0.000 & 0.000 & 1.000 \\
+  0.900 & 0.000 & 0.000 & 0.000 & 1.000 \\
+  0.925 & 0.000 & 0.000 & 0.000 & 1.000 \\
+  0.950 & 0.000 & 0.000 & 0.000 & 1.000 \\
+  0.975 & 0.000 & 0.000 & 0.000 & 1.000 \\
+  1.000 & 0.000 & 0.000 & 0.000 & 1.000
+  \end{tabular}
+  \end{table}
+
+\centering
+\includesvg[height=3.75in]{pictures/match_metrics_vs_threshold_used.svg}
 

### 2023-06-26 LaTeX_paper/paper.tex
add definitions to proff latex paper

@@
 data to convert them from float to bool.
-\newline \newline
+\subsubsection{Input Data}
 To find the optimal threshold a small 16 piece puzzle has been solved.
@@
 
-\centering
+\begin{center}
   \includesvg[height=3.75in]{pictures/match_metrics_vs_threshold_used.svg}
+\end{center}
+
+Assuming the algorithm has to solve a 500 piece puzzle, with a limit match\% of 0.04
+and a corruption rate of 0.057 (data taken from the line in red);
+what would this mean in terms of accuracy of the results?
+
+\subsubsection{Definitions}
+This set of definitions are useful to better understand the next section:
+
+\begin{itemize}
+  \item \textbf{Connection:}\newline
+  When two sides of two different pieces are joined they form a connection.
+  A solved puzzle with \(N\) pieces, (assuming it is squared) has around \(2N\) total connections.
+
+  \item \textbf{Possible Combinations:}\newline
+  A puzzle with N pieces can be put together in many different ways,
+  (even if not all of 	them actually fit together).
+  The total number of possible combinations is \(N! \times 4^N\) where
+  \(N!\) represent all possible way to combinate the pieces in a particular position, and
+  \(4^N\) represents all possible orientations that each piece can have.
+  \item \textbf{Possible Correct Combination:}\newline
+  Is one of the possible combinations where all the connections are considered a match
+  by the comparing algorithm.
+  \item \textbf{Actual Correct Combination:}\newline
+  An Actual Correct Combination is a Possible Combination that
+  is also the correct solution of the original puzzle	
+\end{itemize}
 

### 2023-06-27 LaTeX_paper/paper.tex
begin rust porting

@@
 
+\subsubsection{Corruption Rate Analysis}
+\begin{figure}[h]
+  \caption{Neighbors comparison vs Corruption rate of algorithm \ref{document:GCL}. Image taken from pater \cite{GCL} page 34.}\label{fig:GCL_Corruption_Rate}
+  \centering
+  \includegraphics[height=0.35\textwidth]{pictures/corruption_rate.png}
+\end{figure}
+
+From the graph \ref{fig:GCL_Corruption_Rate}, it can be observed that with a corruption rate of 0.057,
+a neighbors comparison value of about 80\%
+can be expected. Which means that one in every 5 connections on average will be wrong.
+So in a puzzle of 500 pieces (which has approximately 1000 connections),
+200 connections will be wrong on average.
+It is fair to say that this is not an ideal result.
+
+\subsubsection{Limit Match\% Analysis}
+As seen earlier, the limit match percentage is \(4\%\).\newline \newline
+Given that in a puzzle of N pieces there are around \(2N \) connections,
+the probability of one random combination to be a
+possible correct combination is: \(0.054^{2N}\).\newline \newline
+The total number of possible combinations are \(N! \times 4^N\),
+which means that on average, on a puzzle with \(N\) pieces,
+there will be \(0.054^{2N} \times N! \times 4^N \)
+possible correct combinations.\newline \newline
+For \( N = 500 \) the expected number of possible combinations is around \( 1.5 \times 10^{37} \).
+Which makes the chance of finding the actual correct combination basically zero.
+
+\subsubsection{Conclusion}
+In this case both the match\% and the corruption rate are bad enough to make a correct reconstruction impossible.
+\newline \newline 
+To lower the limit match\% is necessary to increase the threshold, but this would increase the corruption rate.
+\newline \newline
+To lower the corruption rate is necessary to decrease the threshold, but this would increase the limit match\%.
+\newline \newline
+This means that, regardless of the threshold chosen, our comparison algorithm \ref{document:my_comparator}
+can not work with a state of the art solver \ref{document:GCL}.
+
+\subsection{Solutions For The Problem}
+
+There are two way to solve this deadlock:
+
+\subsubsection{Improve The Comparator}
+
+Improving the comparator can shortly be done.
+Some minor improvements can be made by spending some time tweaking the current algorithm.
+But it is clear that, for such a task,
+the optimal solution is probably to use machine learning.
+
+\subsubsection{Improving The Solver Algorithm}
+
+Different algorithms have different resilience to corrupted data.
+All the major algorithms that have been proposed since now, focus on speed.
+It is possible that an algorithm that focuses on accuracy over speed
+coud work with our comparator.
+
+\subsubsection{The Path Forward}
+
+Improving the comparator is probably the best long term solution,
+but it comes with a problem:\newline
+Manually testing if some pieces fit together, then making a scan, and finally label
+them to create a dataset would require hundreds if not thousands of hours.\newline
+On the other hand improving the solver is not a good solution long term,
+given that it will almost certainly have a worst time complexity,
+but could have some major short term benefit \newline
+In particular it does not require to create a huge dataset,
+and could be used to build one.
+In Fact it could solve hundreds of small puzzles,
+and automatically label the connections using the solution he created.
+\newline\newline
+Given the two options, the author of this paper has chosen to focus on improving
+the solver algorithm. The choice was driven by the lack of the time needed to build a dataset,
+And the belief that creating a new algorithm,
+for then using that to build a dataset,
+would still be faster compared to building a dataset manually.
+
 % referneces page

### 2023-06-27 cpp_lib/rust_solving/src/main.rs

@@ -1,0 +1,156 @@
+mod shore;
+
+use shore::Shore;
+
+pub enum Orientation{UP, RIGHT, DOWN, LEFT}
+
+/// trait for all piece or group of pieces that can be compared between each other
+pub trait Comparable{
+    /// compare this piece two another piece from an orientation. the recursive orientations are needed to keep track of
+    /// how many times the pieces has been rotated
+    fn compare_to(&self, other: &Self, orientation: Orientation, this_recursive_rotation: i32, other_recursive_rotation: i32) -> Shore{
+        return Shore::new();
+    }
+}
+
+
+/// one single piece, keep the ID and his rotation
+struct SingePiece{
+    id: i32,
+    rotation: i32
+}
+
+impl Comparable for SingePiece{
+    fn compare_to(&self, other: &SingePiece, orientation: Orientation, this_recursive_rotation: i32, other_recursive_rotation: i32) -> Shore{
+        return Shore::new();
+    }
+}
+
+//struct PieceGroup<T: Comparable>{
+struct PieceGroup<'a,T>{
+    pub pieces: [&'a T;4],
+    rotation: i32
+}
+
+impl<'a, T> PieceGroup<'a, T> {
+    fn get_top_left(&self, orientation: i32)->&'a T{
+        self.pieces[(0+self.rotation+orientation)%4]
+    }
+    fn get_top_right(&self, orientation: i32)->&'a T{
+        self.pieces[(1+self.rotation+orientation)%4]
+    }
+    fn get_bottom_left(&self, orientation: i32)->&'a T{
+        self.pieces[(2+self.rotation+orientation)%4]
+    }
+    fn get_bottom_right(&self, orientation: i32)->&'a T{
+        self.pieces[(3+self.rotation+orientation)%4]
+    }
+}
+
+impl<'a, T> Comparable for PieceGroup<'a, T> {
+    fn compare_to(&self, other: &Self, orientation: Orientation, recursive_orientation: i32, recursive_orientation_other: i32) -> Shore{
+        let mut s = Shore::new();
+        match orientation {
+            Orientation::RIGHT => {
+                s += self
+                    .get_top_right(recursive_orientation)
+                    .compare_to(
+                        orientation,
+                        &other.get_top_left(recursive_orientation),
+                        recursive_orientation + orientation,
+                        recursive_orientation_other + other.orientation,
+                    );
+                // Early evaluation to save time.
+                if s.get_shore() == 0 {
+                    return s;
+                }
[…]

### 2023-06-27 cpp_lib/rust_solving/src/shore.rs

@@ -1,0 +1,68 @@
+use std::fmt;
+
+/// This struct keeps track of the shore of each possible combination of pieces,
+/// need to keep track of the average shore, and the number of pieces the shore keeps track of.
+/// `shore` is used to make a weighted average when combining multiple Shores.
+#[derive(Clone, Copy)]
+pub struct Shore {
+    /// The average shore of the n represented connections.
+    shore: u8,
+    /// The number of connections this shore is representing.
+    number: u32,
+}
+
+impl Shore {
+    /// Default constructor, gives a shore with `shore` = 1 and `number` = 0.
+    pub fn new() -> Self {
+        Shore { shore: 1, number: 0 }
+    }
+
+    /// Create a new shore, `number` will be 1.
+    pub fn with_shore(shore: u8) -> Self {
+        Shore { shore, number: 1 }
+    }
+
+    /// Get the shore of the piece.
+    pub fn get_shore(&self) -> u8 {
+        self.shore
+    }
+
+    /// Sum operator, this makes a weighted sum of `shore`, using `number` as weight.
+    pub fn add_assign(&mut self, other: &Shore) {
+        let other_number = other.number;
+        let other_shore = other.shore;
+
+        // If both shores are zero, return immediately to avoid division by zero.
+        if self.number == 0 && other_number == 0 {
+            return;
+        }
+
+        // A connection that is impossible (aka, shore is 0) has to remain impossible even if other
+        // shores are greater.
+        if self.shore == 0 || other_shore == 0 {
+            self.shore = 0;
+            self.number = 1;
+            return;
+        }
+
+        // Calculate new shore with weighted average.
+        let total_number = self.number + other_number;
+        self.shore = ((self.shore as u32 * self.number as u32 + other_shore as u32 * other_number as u32)
+            / total_number) as u8;
+        // Sum numbers.
+        self.number = total_number;
+    }
+
+    /// Sum operator, this makes a weighted sum of `shore`, using `number` as weight.
+    pub fn add(&self, other: &Shore) -> Shore {
+        let mut result = *self;
+        result.add_assign(other);
+        result
+    }
+}
+
+impl fmt::Display for Shore {
+    fn fmt(&self, f: &mut fmt::Formatter<'_>) -> fmt::Result {
+        write!(f, "shore: {} num: {}", self.shore, self.number)
+    }
+}

### 2023-06-27 cpp_lib/solving/groped_pieces/GroupedPieces.h

@@ -1,4 +1,4 @@
-//
+    //
 // Created by luca on 4/20/23.
 //
 

### 2023-06-27 cpp_lib/main_test.cpp
backup commit

@@ -28,8 +28,8 @@ void debug_thread(){
 
 int main(){
 
-    //PuzzleSolver ps(4, 4, "../work_path", "../../dataset/test_4x4/raw",2);
-    PuzzleSolver ps("../work_path");
+    PuzzleSolver ps(4, 4, "../work_path", "../../dataset/test_4x4/raw",2);
+    //PuzzleSolver ps("../work_path");
 
     ps.set_threshold(100);
 
@@ -52,8 +52,8 @@ int main(){
         cout << "skip calculate connections" << endl;
     }
 
-    //thread t1;
-    //t1 = thread(debug_thread);
+    thread t1;
+    t1 = thread(debug_thread);
 
     try{
         ps.solve_puzzle();
@@ -64,7 +64,7 @@ int main(){
     //imshow("lalala",ps.get_result());
     //waitKey(0);
 
-    //t1.join();
+    t1.join();
 
     return 0;
 

### 2023-06-27 cpp_lib/rust_solving/src/main.rs

@@ -1,14 +1,16 @@
 mod shore;
 
+use Direction::DOWN;
 use shore::Shore;
 
-pub enum Orientation{UP, RIGHT, DOWN, LEFT}
+#[derive(Clone,Copy)]
+pub enum Direction {UP, RIGHT, DOWN, LEFT}
 
 /// trait for all piece or group of pieces that can be compared between each other
 pub trait Comparable{
     /// compare this piece two another piece from an orientation. the recursive orientations are needed to keep track of
     /// how many times the pieces has been rotated
-    fn compare_to(&self, other: &Self, orientation: Orientation, this_recursive_rotation: i32, other_recursive_rotation: i32) -> Shore{
+    fn compare_to(&self, direction: Direction,other: &Self, recursive_orientation: usize, recursive_orientation_other: usize) -> Shore{
         return Shore::new();
     }
 }
@@ -16,128 +18,170 @@ pub trait Comparable{
 
 /// one single piece, keep the ID and his rotation
 struct SingePiece{
-    id: i32,
-    rotation: i32
+    id: usize,
+    orientation: usize
 }
 
 impl Comparable for SingePiece{
-    fn compare_to(&self, other: &SingePiece, orientation: Orientation, this_recursive_rotation: i32, other_recursive_rotation: i32) -> Shore{
+    fn compare_to(&self, direction: Direction,other: &Self, recursive_orientation: usize, recursive_orientation_other: usize) -> Shore{
         return Shore::new();
     }
 }
 
-//struct PieceGroup<T: Comparable>{
-struct PieceGroup<'a,T>{
+struct PieceGroup<'a,T: Comparable>{
+//struct PieceGroup<'a,T>{
     pub pieces: [&'a T;4],
-    rotation: i32
+    orientation: usize
 }
 
-impl<'a, T> PieceGroup<'a, T> {
-    fn get_top_left(&self, orientation: i32)->&'a T{
-        self.pieces[(0+self.rotation+orientation)%4]
-    }
-    fn get_top_right(&self, orientation: i32)->&'a T{
-        self.pieces[(1+self.rotation+orientation)%4]
-    }
-    fn get_bottom_left(&self, orientation: i32)->&'a T{
-        self.pieces[(2+self.rotation+orientation)%4]
-    }
-    fn get_bottom_right(&self, orientation: i32)->&'a T{
-        self.pieces[(3+self.rotation+orientation)%4]
-    }
[…]

### 2023-06-27 cpp_lib/solving/calculate_connections.cpp

@@ -56,10 +56,9 @@ void piece_comparer_thread(PieceConnection *pieces_connections, PieceShape *piec
                         compatibility = 0;
                     }
 
-
                     //Mat preview = pieces_shapes[piece_id].get_side(piece_side).get_compare_image(
                     //        pieces_shapes[other_piece_id].get_side(other_piece_side)
-                    //        );    
+                    //        );
                     //imwrite("comparison.png",preview);
 
                     if(PreviewManager::is_preview_enabled()){

### 2023-06-27 cpp_lib/rust_solving/src/main.rs
backup commit

@@ -1,5 +1,7 @@
 mod shore;
 
+use std::collections::HashSet;
+use std::process::id;
 use Direction::DOWN;
 use shore::Shore;
 
@@ -10,39 +12,54 @@ pub enum Direction {UP, RIGHT, DOWN, LEFT}
 pub trait Comparable{
     /// compare this piece two another piece from an orientation. the recursive orientations are needed to keep track of
     /// how many times the pieces has been rotated
-    fn compare_to(&self, direction: Direction,other: &Self, recursive_orientation: usize, recursive_orientation_other: usize) -> Shore{
-        return Shore::new();
-    }
+    fn compare_to(&self, direction: Direction,other: &Self, recursive_orientation: usize, recursive_orientation_other: usize) -> Shore;
 }
 
+/// trait for all the level that has an hash set in ti (all except the first)
+pub trait HasSetInIt{
+    /// get a set containing the ids of the current set
+    fn get_ids(&self) -> &HashSet<usize>;
+}
 
 /// one single piece, keep the ID and his rotation
-struct SingePiece{
+pub struct SingePiece{
     id: usize,
     orientation: usize
+}
+
+impl SingePiece {
+    pub fn get_id(&self) -> usize{
+        self.id
+    }
+    pub fn get_orientation(&self) -> usize{
+        self.orientation
+    }
+    pub fn new(id: usize, orientation: usize) -> Self{
+        assert!(orientation < 4);
+        Self{
+            id,
+            orientation
+        }
+    }
 }
 
 impl Comparable for SingePiece{
     fn compare_to(&self, direction: Direction,other: &Self, recursive_orientation: usize, recursive_orientation_other: usize) -> Shore{
         return Shore::new();
     }
+
 }
 
-struct PieceGroup<'a,T: Comparable>{
-//struct PieceGroup<'a,T>{
+pub struct PieceGroup<'a,T: Comparable>{
     pub pieces: [&'a T;4],
-    orientation: usize
+    orientation: usize,
+    ids: HashSet<usize>
 }
 
-/// when trying to create a new group of piece many things can go wrong, this enum is the result
-/// that represent all the errors, as well as the solution
-pub enum GroupCreationResult<'a, T: Comparable>{
-    Ok(PieceGroup<'a, T>),
-    TopRightImpossibleFit,
-    RopLeftImpossibleFit,
-    BottomLeftImpossibleFit,
[…]

### 2023-06-27 cpp_lib/rust_solving/src/main.rs
finish basic recursive struct in rust port

@@ -2,6 +2,8 @@ mod shore;
 
 use std::collections::HashSet;
 use std::process::id;
+use std::thread::ScopedJoinHandle;
+use CalculateShoreResult::TopRightImpossibleFit;
 use Direction::DOWN;
 use shore::Shore;
 
@@ -53,7 +55,8 @@ impl Comparable for SingePiece{
 pub struct PieceGroup<'a,T: Comparable>{
     pub pieces: [&'a T;4],
     orientation: usize,
-    ids: HashSet<usize>
+    ids: HashSet<usize>,
+    shore: Shore
 }
 
 impl<'a, T: Comparable> HasSetInIt for PieceGroup<'a, T> {
@@ -88,6 +91,75 @@ impl<'a, T: Comparable> PieceGroup<'a, T> {
     }
     fn set_bottom_right(&mut self, to_set: &'a T){
         self.pieces[(3+self.orientation)%4] = to_set;
+    }
+}
+
+impl<'a, T: Comparable> PieceGroup<'a, T> {
+
+    /// calculate the shore of the current group of pieces
+    fn calculate_shore(&self) -> CalculateShoreResult{
+        let mut shore = Shore::new();
+
+        // comparing top border
+        shore += self.get_top_left(0).compare_to(Direction::RIGHT,self.get_top_right(0),self.orientation,self.orientation);
+        // trowing an error if the piece is impossible
+        if shore.get_shore() == 0 {
+            return CalculateShoreResult::TopRightImpossibleFit;
+        }
+
+
+        // comparing right border
+        shore += self.get_top_right(0).compare_to(Direction::DOWN,self.get_bottom_right(0),self.orientation,self.orientation);
+        // trowing an error if the piece is impossible
+        if shore.get_shore() == 0 {
+            return  CalculateShoreResult::BottomRightImpossibleFit;
+        }
+
+
+        // comparing bottom border
+        shore += self.get_bottom_right(0).compare_to(Direction::LEFT,self.get_bottom_left(0),self.orientation,self.orientation);
+        // trowing an error if the piece is impossible
+        if shore.get_shore() == 0 {
+            return CalculateShoreResult::BottomLeftImpossibleFit;
+        }
+
+        // comparing bottom border
+        shore += self.get_bottom_left(0).compare_to(Direction::UP,self.get_top_left(0),self.orientation,self.orientation);
+        // trowing an error if the piece is impossible
+        if shore.get_shore() == 0 {
[…]

### 2023-06-27 cpp_lib/rust_solving/src/shore.rs

@@ -26,9 +26,24 @@ impl Shore {
     pub fn get_shore(&self) -> u8 {
         self.shore
     }
+}
+
+use std::ops;
+
+impl ops::Add for Shore {
+    type Output = Shore;
+    /// Sum operator, this makes a weighted sum of `shore`, using `number` as weight.
+    fn add(self, other: Shore) -> Shore {
+        let mut result = self;
+        result+=other;
+        result
+    }
+}
+
+impl ops::AddAssign for Shore{
 
     /// Sum operator, this makes a weighted sum of `shore`, using `number` as weight.
-    pub fn add_assign(&mut self, other: &Shore) {
+    fn add_assign(&mut self, other: Shore) {
         let other_number = other.number;
         let other_shore = other.shore;
 
@@ -51,13 +66,6 @@ impl Shore {
             / total_number) as u8;
         // Sum numbers.
         self.number = total_number;
-    }
-
-    /// Sum operator, this makes a weighted sum of `shore`, using `number` as weight.
-    pub fn add(&self, other: &Shore) -> Shore {
-        let mut result = *self;
-        result.add_assign(other);
-        result
     }
 }
 

### 2023-06-28 cpp_lib/rust_solving/src/main.rs
add piece array class and testing

@@ -1,6 +1,7 @@
 mod shore;
 
 use std::collections::HashSet;
+use std::fmt::{Debug, Error, Formatter};
 use std::process::id;
 use std::thread::ScopedJoinHandle;
 use CalculateShoreResult::TopRightImpossibleFit;
@@ -24,6 +25,7 @@ pub trait HasSetInIt{
 }
 
 /// one single piece, keep the ID and his rotation
+#[derive(Debug)]
 pub struct SingePiece{
     id: usize,
     orientation: usize
@@ -388,9 +390,106 @@ pub enum CalculateShoreResult{
     AvregeIsTooLow
 }
 
+/// an array of pieces that represent a possible solution,
+/// the struct can comunicate with the C++ library, and offer the following functionalities:
+/// - Can generate a preview image and send it to the c# lib to be analized
+/// - Can Generate an image for shoring, and return a shore that tels how well sed pieces work together
+struct PieceArray{
+    dim_x: usize,
+    dim_y: usize,
+    pieces: Vec<SingePiece>,
+}
+
+impl PieceArray {
+    /// get a reference to a piece at a specific coordinate
+    pub fn get_piece(&self, x: usize, y: usize) -> Result<&SingePiece,()>{
+        if x >= self.dim_x{
+            return Result::Err(());
+        }
+        if y >= self.dim_y{
+            return Result::Err(());
+        }
+
+        return Ok(&self.pieces[y*self.dim_x+x]);
+    }
+    /// set a piece to a specific coordinates
+    pub fn set_piece(&mut self, x: usize, y: usize, to_be_set: SingePiece) -> Result<(),()>{
+        if x >= self.dim_x{
+            return Result::Err(());
+        }
+        if y >= self.dim_y{
+            return Result::Err(());
+        }
+
+        self.pieces[y*self.dim_x+x] = to_be_set;
+
+        return Ok(());
+    }
+
+    /// return a new piece array with the specified dimensions
+    pub fn new(dim_x: usize, dim_y: usize) -> Self{
+
+        let size = dim_y*dim_x;
+
+        let mut vec = Vec::with_capacity(dim_x*dim_y);
+
+        for i in 0..size{
+            vec.push(SingePiece::new(0,0))
+        }
+
+        Self{
+            dim_x,
+            dim_y,
+            pieces: vec
+        }
+    }
+}
+
+impl Debug for PieceArray {
+    fn fmt(&self, f: &mut Formatter<'_>) -> std::fmt::Result {
[…]

### 2023-06-29 cpp_lib/rust_solving/src/PieceArrayDLL/piece_array_dll.cpp
Add File for Piece Array DLL

@@ -1,0 +1,2 @@
+#include "piece_array_dll.h"
+#include "../../../solving/puzzle_preview/PieceArray.h"

### 2023-06-29 cpp_lib/rust_solving/src/PieceArrayDLL/piece_array_dll.h

@@ -1,0 +1,14 @@
+#ifndef PUZZLE_SOLVER_PIECE_ARRAY_DLL_H
+#define PUZZLE_SOLVER_PIECE_ARRAY_DLL_H
+
+// this file allows the rust puzzle solver to access the functionalities of piece array
+
+typedef struct PieceArrayWrapper PieceArrayWrapper;
+
+PieceArrayWrapper* create_piece_array();
+
+void generate_test_image(PieceArrayWrapper* piece_array_wrapper);
+
+void destroy_piece_array_wrapper(PieceArrayWrapper* to_destroy);
+
+#endif //PUZZLE_SOLVER_PIECE_ARRAY_DLL_H

### 2023-06-30 cpp_lib/rust_solving/src/PieceArrayDLL/piece_array_dll.cpp
backup commit

@@ -1,2 +1,27 @@
 #include "piece_array_dll.h"
 #include "../../../solving/puzzle_preview/PieceArray.h"
+#include "opencv2/opencv.hpp"
+
+
+struct PieceArrayWrapper{
+    PieceImage* images
+    PieceArray pa;
+};
+
+PieceArrayWrapper* create_piece_array(){
+    return new PieceArrayWrapper();
+}
+
+void generate_test_image(PieceArrayWrapper* piece_array_wrapper){
+
+    Holder o = Holder()
+
+    piece_array_wrapper->pa.set(x,y,)
+
+    auto img = piece_array_wrapper->pa.get_image(BuildImageMode::PREVIEW);
+    cv::imwrite("test.png",img);
+}
+
+void destroy_piece_array_wrapper(PieceArrayWrapper* to_destroy){
+    delete to_destroy;
+}

### 2023-06-30 cpp_lib/solving/puzzle_preview/PieceArray.h

@@ -48,7 +48,7 @@ public:
     int get_dim_x() const;
     /// returns the y dimension of the 2d array
     int get_dim_y() const;
-    /// create an empty piece array
+    /// create an empty piece array with size 1x1
     PieceArray();
     /// copy constructor
     PieceArray(PieceArray & other);

### 2023-09-24 c#_desktop_app/JigsawGenius/WinFormsApp1/ThresholdTweaking.cs
fix trhrsholdtweeking

@@ -1,4 +1,4 @@
-﻿using System;
+using System;
 using System.Collections.Generic;
 using System.ComponentModel;
 using System.Data;
@@ -29,7 +29,7 @@ namespace JigsawGenius
 
         private void _testButton_Click(object sender, EventArgs e)
         {
-            _comunicator.SetSplitThreshold((byte)thresholdTrackBar.Value);
+            _comunicator.SetSplitThreshold(thresholdTrackBar.Value);
             pictureBox1.Image = _comunicator.GetThresholdPreview();
         }
 

### 2023-09-24 cpp_lib/pre_processing/piece_splitting.cpp

@@ -63,6 +63,9 @@ cv::Mat piece_splitting_get_test_threshold_image(const std::string& input_path){
     threshold(mask, temp, THRESHOLD, 255, THRESH_BINARY);
     mask = temp;
 
+    // create a black rectangle around the image to make shure floodDill has effect
+    rectangle(mask,Point(0,0),Point(mask.cols-1, mask.rows-1),Scalar(0));
+
     // unsung flood feel form the borders to remove the possible black pixels inside the pieces
     floodFill(mask,Point(0,0),100);
     mask = mask != 100;

### 2023-09-24 cpp_lib/PuzzleSolver.cpp
add export of sides

@@ -38,7 +38,7 @@ PuzzleSolver::PuzzleSolver(int dim_x, int dim_y, std::string work_path_, std::st
     filesystem::remove_all(work_path);
 
     // creating the 4 folders used for save the data of the program
-    string paths_to_create[] = {"", "/raw","/divided","/connections","/results"};
+    string paths_to_create[] = {"", "/raw","/divided","/connections","/results", "/results/pieces","/results/sides"};
     for(const auto& to_create: paths_to_create) {
         string path = work_path + to_create;
 
@@ -90,7 +90,7 @@ int PuzzleSolver::split_image() {
     piece_splitting_set_threshold(split_threshold);
 
     // split the images
-    number_of_pieces = split_pieces_into_single_images(work_path + "/raw/", work_path + "/divided/");
+    number_of_pieces = split_pieces_into_single_images(work_path + "/raw/", work_path + "/divided/", work_path + "/results/pieces/");
     // update the state
     state = IMAGE_SPLITTED;
     // save the current status
@@ -195,6 +195,11 @@ void PuzzleSolver::calculate_connections() {
     }
     // calculate all combinations
     calculate_all_connections(work_path + "/divided/", work_path + "/connections", number_of_pieces,number_of_cores,false);
+
+    // save the sides in the result
+    export_sides_result(work_path + "\\results\\pieces\\", work_path + "\\divided\\",work_path + "\\results\\sides\\", number_of_pieces);
+
+
     // update state
     state = CONNECTION_CALCULATED;
 

### 2023-09-24 cpp_lib/main_test.cpp

@@ -6,7 +6,7 @@
 #include "PuzzleSolver.h"
 #include <thread>
 #include <opencv2/opencv.hpp>
-
+#include "pre_processing/corner_finding.h"
 using namespace std;
 using namespace cv;
 
@@ -27,6 +27,11 @@ void debug_thread(){
 }
 
 int main(){
+
+    //export_sides_result("C:\\Users\\lucas\\Desktop\\results\\results\\pieces","C:\\Users\\lucas\\Desktop\\results\\divided","C:\\Users\\lucas\\Desktop\\results\\results\\sides", 16);
+
+    //return 0;
+
 
     cout << "Test" << endl;
 

### 2023-09-24 cpp_lib/pre_processing/corner_finding.cpp

@@ -11,6 +11,8 @@
 #include "../solving/puzzle_preview/PreviewManager.h"
 #include <thread>
 #include "../solving/graphic_piece/PieceShape.h"
+#include <fstream>
+#include <utility>
 
 // if this is defined the program will insert debug images
 //#define DEBUG
@@ -691,4 +693,62 @@ void find_corners(const cv::Mat &input, cv::Point &p1,  cv::Point &p2,  cv::Poin
     p2 = vertices_precise[1];
     p3 = vertices_precise[2];
     p4 = vertices_precise[3];
+}
+
+
+void export_sides_result(const std::string& input_images_path,const std::string& input_coordinates_path,const std::string& output_path, int number_of_pieces){
+
+    for(int i=0; i<number_of_pieces;i++){
+
+        //############## get coordinates ###################
+        Point points[4];
+        string line;
+        ifstream data (input_coordinates_path + "/" + to_string(i) + ".txt");
+
+        assert(data.is_open());
+
+        // read the points
+        for (auto & point : points) {
+            std::getline(data, line);
+            std::stringstream ss(line);
+            char c[6], a;
+            int x, y;
+            ss >> c >> a >> x >> a >> y >> a;
+            point = Point(x, y);
+        }
+
+        //calculate center of the piece
+        Point center = (points[0]+points[1]+points[2]+points[3])/4;
+
+        //############## get image ###################
+
+        Mat image = imread(input_images_path + "/" + to_string(i) + ".jpeg");
+
+
+        for(int side=0; side<4; side++){
+            Point p1 = points[side];
+            Point p2 = points[(side+1)%4];
+
+            Mat border_shape = Mat::zeros(1500, 1500, image.type());
+
+            // Calculate the midpoint between p1 and p2
+            float midX = (p1.x + p2.x) / 2.0f;
+            float midY = (p1.y + p2.y) / 2.0f;
+
+            // Calculate the angle between p1 and p2
+            float angle = std::atan2(p2.y - p1.y, p2.x - p1.x) * 180.0f / CV_PI;
+
+            // Create a transformation matrix to rotate and move the input image
+            // docs: https://docs.opencv.org/3.4/da/d54/group__imgproc__transform.html#gafbbc470ce83812914a70abfb604f4326
+            cv::Mat transform = cv::getRotationMatrix2D(cv::Point2f((p1+p2)/2), angle, 1.0);
+            transform.at<double>(0, 2) += (float)1500/2 - midX;
[…]

### 2023-09-24 cpp_lib/pre_processing/piece_splitting.cpp

@@ -15,7 +15,7 @@ using namespace cv;
 /// how many pixels a piece's area has to be big for it to be considered an actual piece
 #define PIECE_MINIMUM_AREA (50000*ppi/1200)
 /// how many pixel of margin the function keeps when cropping an image
-#define CROP_MARGIN (50*ppi/1200)
+#define CROP_MARGIN (750*ppi/1200)
 /// kernel of the morphologyEx open filter that will be apply to the mask
 #define MORPH_OPEN_KERNEL (10*ppi/1200)
 /// kernel of the morphologyEx open filter that will be apply to the mask
@@ -93,7 +93,7 @@ cv::Mat piece_splitting_get_test_threshold_image(const std::string& input_path){
 
 /// this function take as input a input_path where some scansion of a puzzle_preview is made
 /// and split them into many single pieces
-int split_pieces_into_single_images(const std::string& input_path,const std::string& output_path,const int ppi, bool enable_image_view){
+int split_pieces_into_single_images(const std::string& input_path,const std::string& output_path, const std::string& result_path,const int ppi, bool enable_image_view){
 
     // a temporary value  to quick operations
     Mat temp, kernel;
@@ -201,6 +201,16 @@ int split_pieces_into_single_images(const std::string& input_path,const std::str
 
                 // crop it
                 Mat cropped_image = single_piece(Range(y1,y2),Range(x1,x2));
+
+                // apply the same crop to the original image. export an image that is intended to be used
+                // to train a piece comparing model
+                Mat result_image = image(Range(y1,y2),Range(x1,x2));
+
+                //calculate input_path
+                string result_path_image = result_path + string("/") + to_string(piece_index) + string(".jpeg");
+
+                //save the file
+                imwrite(result_path_image,result_image);
 
                 if(PreviewManager::is_preview_enabled() || enable_image_view){
                     Mat cropped_image_resized;

### 2023-09-24 LaTeX_paper/paper.tex
rewrite abstract

@@
 \section{Abstract}
-The jigsaw puzzle problem has been in the eye of computer scientists for a while,
-and some clever solutions have already been found. These algorithms are made to
-work with a “digital” jigsaw puzzle~\ref{fig:figure_digital_puzzle},
-but there aren't papers (at least not popular enough to be searchable)
-that try to apply the solution
-to a “real world” jigsaw puzzle~\ref{fig:figure_real_puzzle}.\newline
-The problem has been tackled by some small projects. But, as said earlier,
-the process and eventual challenges has never been documented by a full paper,
-this wants to be the first.\newline
-As a bonus the paper will also cover the creation of a user friendly app
-that will be open source and free to use.
+This paper examines the Jigsaw puzzle problem,
+which has already been extensively studied in the literature.
+Several algorithms with efficient time complexity have been developed
+specifically for "digital" jigsaw puzzles. However, the counterpart:
+the "real world" jigsaw puzzle, has received relatively little attention
+in the literature. While some small-scale projects have addressed this issue,
+we were unable to find any papers discussing it.
+
+The puzzle problem can be divided into two separate components: the "Comparator"
+whose objective is to determine whether two sides of two pieces fit together,
+and the "Solver" whose objective is to use the information provided
+by the comparator to find the best way to fit some pieces together.
+
+Solving the problem in the real world has proven to be more challenging compared
+to the digital realm.
+This is because all measurements in the real world are noisier than those
+in the digital world, making it challenging to obtain accurate data from the Comparator.
+The Solver poses its own set of challenges, as it is an example of a
+multiobjective optimization problem. Specifically, one objective is to have
+the fastest algorithm possible,
+while the other objective is to create an algorithm that performs well with
+imprecise data. The latter objective is particularly important when solving
+real-world puzzles.
+
+In the first half of this paper, a Comparator is developed, and its accuracy
+is evaluated.
+The data is then used to demonstrate its incompatibility with the current
+state-of-the-art algorithm. At this juncture,
+two options remain to solve the problem:
+either create a superior Comparator or design a
+Solver that can operate with noisier data.
+
+The most promising approach to improving the Comparator
+involves utilizing machine learning, but this requires a substantial amount of data.
+Conversely, creating a better Solver is a less straightforward task.
+However, if successful, it could potentially serve as a labeling tool
+to generate the dataset needed to train a superior Comparator.
+
+The second part of this paper focuses on developing a
+new Solver algorithm specifically designed to work with noisy data.
+While the Solver created may not be considered state-of-the-art,
+as its time complexity ultimately ends up being worse than the current
+best algorithms, it could still play a fundamental role in solving the problem.
+As mentioned earlier, it could be employed to solve many small-sized
+puzzles and use the results to train a better Comparator.
+
+In conclusion, this paper outlines the additional challenges that the real-world
+puzzle problem presents compared to its digital counterpart.
+Additionally, it lays the groundwork for a superior machine learning-based Comparator.
 

### 2023-09-27 LaTeX_paper/paper.tex
fix paper error

@@
 % to include svg images
-\usepackage{svg}
+%\usepackage{svg}
 
-% settings for how to indend the page when neaded
+% settings for how to indent the page when needed
 \newenvironment{indented_section}
@@
 Several algorithms with efficient time complexity have been developed
-specifically for "digital" jigsaw puzzles. However, the counterpart:
-the "real world" jigsaw puzzle, has received relatively little attention
+specifically for 'digital' jigsaw puzzles. However, the counterpart:
+the 'real world' jigsaw puzzle, has received relatively little attention
 in the literature. While some small-scale projects have addressed this issue,
@@
 
-The puzzle problem can be divided into two separate components: the "Comparator"
+The puzzle problem can be divided into two separate components: the 'Comparator'
 whose objective is to determine whether two sides of two pieces fit together,
-and the "Solver" whose objective is to use the information provided
+and the 'Solver' whose objective is to use the information provided
 by the comparator to find the best way to fit some pieces together.
@@
 There is  another important distinction between different types of puzzles.
-They can be divided into “digital” and “real world” jigsaw puzzles.
-\label{document:DigitalVSReal}
+They can be divided into “digital” and “real world” jigsaw puzzles.\label{document:DigitalVSReal}
 
@@
     containing all the pieces. It then split all the pieces from each other,
-    9and split each piece into his four sides.\label{document:splitter}
+    and split each piece into his four sides.\label{document:splitter}
 
@@
 \subsection{Solving Jigsaw Puzzles By The Graph Connection Laplacian~\cite{GCL}}
-This algorithm falls in the “binary comparison” category~\ref{document:comparator}.
+This algorithm falls in the “binary comparison” category~\cref{document:comparator}.
 And can be used to understand the strength and weaknesses
@@
 
-\begin{center}
-  \includesvg[height=3.75in]{pictures/match_metrics_vs_threshold_used.svg}
-\end{center}
+\begin{figure}[h]
+    \caption{match metrics vs threshold used}\label{fig:match_metrics_vs_threshold_used}
+    \centering
+    \includegraphics[height=0.5\textwidth]{pictures/match_metrics_vs_threshold_used.png}
+\end{figure}
 

### 2023-09-28 cpp_lib/PuzzleSolver.cpp
minor changes

@@ -28,7 +28,7 @@ PuzzleSolver::PuzzleSolver(int dim_x, int dim_y, std::string work_path_, std::st
 
     number_of_pieces = 0;
 
-    split_threshold = 100;
+    split_threshold = 70;
 
     communication_image = PngImageClass();
 

### 2023-09-28 cpp_lib/rust_solving/src/solver.rs

@@ -41,7 +41,6 @@ pub fn solve<T: NextLevelOrPanic + Debug>(pgh: &PieceGroupHolder<T>, output_path
                 'bottom_right_loop:
                 for bottom_right in match_for_all_pieces.get_matches_with_higher_index(top_right, Direction::DOWN,top_left_index){
 
-
                     'bottom_left_loop:
                     for bottom_left in match_for_all_pieces.get_matches_with_higher_index(bottom_right, Direction::LEFT,top_left_index){
 
@@ -62,36 +61,36 @@ pub fn solve<T: NextLevelOrPanic + Debug>(pgh: &PieceGroupHolder<T>, output_path
 
                         // now it is possible to check if the pieces match graphically, calling the c++ func
 
-                        // create the piece array with the appropriate size
-                        let mut pa = PieceArray::new(
-                            PieceGroup::<T>::SIDE_LEN,
-                            PieceGroup::<T>::SIDE_LEN
-                        );
+                        if T::LEVEL < 2{
+                            // create the piece array with the appropriate size
+                            let mut pa = PieceArray::new(
+                                PieceGroup::<T>::SIDE_LEN,
+                                PieceGroup::<T>::SIDE_LEN
+                            );
 
-                        // fill the piece array with the piece group
-                        pg.fill_piece_array(&mut pa, 0, 0, 0);
+                            // fill the piece array with the piece group
+                            pg.fill_piece_array(&mut pa, 0, 0, 0);
 
-                        // calling the c++ dll
-                        unsafe {
-                            let mut paw = pa.get_piece_array_wrapper();
+                            // calling the c++ dll
+                            unsafe {
+                                let mut paw = pa.get_piece_array_wrapper();
 
-                            // if the shore is to low i continue on the next iteration
+                                // if the shore is to low i continue on the next iteration
 
-                            if (*paw).get_shore() < MIN_SHORE_PIECE_ARRAY {
-                                //println!("skip because of: MIN_SHORE_PIECE_ARRAY: {}",(*paw).get_shore());
+                                if (*paw).get_shore() < MIN_SHORE_PIECE_ARRAY {
+                                    //println!("skip because of: MIN_SHORE_PIECE_ARRAY: {}",(*paw).get_shore());
+                                    (*paw).destroy_piece_array_wrapper();
+                                    continue;
+                                }
+                                //println!("{:?}",pg);
+                                // send the prevew image to the c# backend
+                                CALL_BACK_FUNC(paw);
[…]

### 2023-09-28 LaTeX_paper/paper.tex

@@
 \usepackage{graphicx}
+
+% to have precise image placement
+\usepackage{float}
 
@@
 Several algorithms with efficient time complexity have been developed
-specifically for 'digital' jigsaw puzzles. However, the counterpart:
-the 'real world' jigsaw puzzle, has received relatively little attention
+specifically for ``digital''~\ref{fig:figure_digital_puzzle} jigsaw puzzles. However, the counterpart:
+the ``real world' jigsaw puzzle, has received relatively little attention
 in the literature. While some small-scale projects have addressed this issue,
@@
 
-The puzzle problem can be divided into two separate components: the 'Comparator'
+The puzzle problem can be divided into two separate components: the ``Comparator''~\ref{document:comparator}
 whose objective is to determine whether two sides of two pieces fit together,
-and the 'Solver' whose objective is to use the information provided
+and the ``Solver''~\ref{document:solver} whose objective is to use the information provided
 by the comparator to find the best way to fit some pieces together.
@@
 % figure of digital jigsaw puzzle    
-\begin{figure}[h]
+\begin{figure}[H]
     \caption{An example of a “digital” jigsaw  puzzle}\label{fig:figure_digital_puzzle}
@@
 % figure of real jigsaw puzzle    
-\begin{figure}[h]
-    \caption{An example of a “real world” jigsaw  puzzle}\label{fig:figure_real_puzzle}
+\begin{figure}[H]
+    \caption{An example of a ``real world'' jigsaw  puzzle}~\label{fig:figure_real_puzzle}
     \includegraphics[height=0.25\textwidth]{pictures/real_puzzle.jpg}
@@
 
-% figure of a mesurement error
-\begin{figure}[h]
+% figure of a measurement error
+\begin{figure}[H]
     \caption{An example of what can go wrong when dealing with the real world}\label{fig:figure_measurement_error}
@@
 \subsection{Solving Jigsaw Puzzles By The Graph Connection Laplacian~\cite{GCL}}
-This algorithm falls in the “binary comparison” category~\cref{document:comparator}.
+This algorithm falls in the ``binary comparison'' category~\cref{document:comparator}.
 And can be used to understand the strength and weaknesses
@@
 minimum for jigsaw puzzle solving, according to the study:
-“No easy puzzles: Hardness results for jigsaw puzzles~\cite{ON2Claim}”.\newline
+``No easy puzzles: Hardness results for jigsaw puzzles~\cite{ON2Claim}''.\newline
 The negative aspect might be the accuracy, since by using only two states
 (match or not match) some informations are lost, compared to a non binary comparison.
-To quantify accuracy the paper used the “neighbors comparison” metric,
-which “calculates the percentage of pairs of image patches that are matched correctly”.\newline
-\label{document:GCL}
+To quantify accuracy the paper used the ``neighbors compariso'' metric,
+which ``calculates the percentage of pairs of image patches that are matched correctly''.\label{document:GCL}
 
@@
 it might be possible that the accuracy would have been better if they had allowed
-it to run for more generations.\newline
-\label{document:GA}
+it to run for more generations.\label{document:GA}
 
 \subsection{Computer Vision Powers Automatic Jigsaw Puzzle Solver~\cite{Abto}}
-The solutions~\ref{document:GCL} and~\ref{document:GA} can be considered “state of the art” for digital jigsaw puzzles.
-But, as already introduced in section~\ref{document:DigitalVSReal} and better explained in section TODO,
+The solutions~\ref{document:GCL} and~\ref{document:GA} can be considered ``state-of-the-art'' for digital jigsaw puzzles.
+But, as already introduced in section~\ref{document:DigitalVSReal},
 appalling the solution to the real world can be challenging.\newline
-This solution is possibly a “state of the art” for real world puzzles.\newline
-In reality calling this a “solution” is incorrect,
+This solution is one of the best, and well documented implementations for real world puzzles.\newline
+In reality calling this ``solution'' is incorrect,
 since all it does is find the best 8 matches and asks the user which one to place.
@@
 since the article is more of a publicity stunt than an academic paper.
-In fact, the code is not open source and the information about the time needed to solve the puzzle is missing.\newline
+In fact, the code is not open source and the informations about the time needed to solve the puzzle are missing.\newline
 The article only shows a single puzzle solved, with a 9$\times$6 dimension.\newline
-Even with all of these problems this article still is one of the best example of a solution for real world puzzle.
+Even with all of these caveats this article still is one of the best example of a solution for real world puzzles.
 
@@
 After reading some of the previous literature for this problem, some conclusions could be drawn:
-The problem of “digital jigsaw puzzle” has been solved many times, and is already well optimized.\newline
-On the other hand, the problem of “real world jigsaw puzzle” has mostly been ignored\newline
+The problem of ``digital'' jigsaw puzzle has been solved many times, and is already well optimized.\newline
+On the other hand, the problem of ``real world'' jigsaw puzzle has mostly been ignored
 by the academic community.\newline
-
-The objective of this paper is to fill this void, by answering the following questions:
-\begin{itemize}
-    \item Can the current state of the art solutions for digital puzzles be used for real world puzzles, or the unpredictable nature of real world data makes it impossible?
-    \item If the algorithms cannot be applied to the real world, what is a possible solution that is more redundant to imprecise data?
-
-  \end{itemize}
+The first objective for this paper is to fill this void, and been the first formal paper to analyze the
+``real world'' jigsaw puzzle problem.\newline
+The second objective of this paper is to use the research that has been done to create a labeling tool.\newline
+The reason behind this objective is that the biggest challenge for real world puzzles is creating a
+reliable comparator~\ref{document:comparator}. That can deal with all the noisy 
+mages you get from the real world.\newline
+It is easy to see how a machine learning based comparator would probably be the best solution, 
+but this has some problems, in fact having to manually scan and label thousands of individual puzzle
+pieces to train the model would take ages.
+Instead using an automatic tool would be abel to scan a small $4\times4$ puzzle in one shot,
+solve it, and return the labeled data in just a couple minutes.
 
@@
 
-To answer these questions, some data to start with,
-and an algorithm to analyze the data; in particular the necessary components are:
+This is the
 
@@
 The first step is finding a real world puzzle to solve;
-It has been decided to use a classic 500 piece puzzle, and use a printer's
+It has been decided to use a classic 1000 piece 66cm x 50cm  puzzle, and use a printer's
 scanner to digitize the pieces.\newline 
@@
 of the piece, as seen in image~\ref{fig:figure_measurement_error}.
-The puzzle has been scanned backward, since the comparator algorithm
-that has been used REF does not use colors,
-and having an uniform color would make splitting the pieces easier.
+The puzzle has been scanned backward, using a black background.
+
+This choice has been dictated by the fact that the scanner used has the flashlight
+slightly off centered from the scanner's sensor.
+And this causes a shadows to be cast on one side of the pieces.
+A black background has been chosen to solve the problem of the shadow.
+And then the pieces has been flipped backward, since many of them where black,
+and it was difficult to separate them from the background.
+In the future it would be possible to scan the pieces in the correct orientation,
+by using a different scanner.
 

### 2023-09-28 LaTeX_paper/paper.tex
continue paper

@@
 reliable comparator~\ref{document:comparator}. That can deal with all the noisy 
-mages you get from the real world.\newline
+images you get from the real world.\newline
 It is easy to see how a machine learning based comparator would probably be the best solution, 
@@
 pieces to train the model would take ages.
-Instead using an automatic tool would be abel to scan a small $4\times4$ puzzle in one shot,
+Instead an automatic tool would be abel to scan a small $4\times4$ puzzle in one shot,
 solve it, and return the labeled data in just a couple minutes.
@@
 
-This is the
+To fulfill the objective of this paper three some data to work with are needed.
+This section will cover the input data used, and the Splitter~\ref{document:splitter}
+and Comparator~\ref{document:comparator} algorithms.
 
@@
   This generates a set of Blobs~\ref{fig:s_s_no_holes_minus_expansion},
-  but again, the shape of the blob is very different depending on what has generated it
+  but again, the shape of one blob is very different depending on what has generated it
   (an “angle” or a “knob”), so they can be classified.
@@
 
-\section{Apling Already Existing Algorithms To The Real World}
+\section{Applying Already Existing Algorithms To The Real World}
 Now that the setup is completed, it is possible to test the already existing
@@
 function to the corruption rate, which are essential for this analysis.
-\newline \newline
+
 The tests that have been conducted have shown that our comparator algorithm~\ref{document:my_comparator}
@@
 the two algorithms mentioned above.
-\newline \newline
+\newline
 The comparison algorithm deceived in section~\ref{document:my_comparator} outputs a compatibility
@@
 Manually testing if some pieces fit together, then making a scan, and finally label
-them to create a dataset would require hundreds if not thousands of hours.\newline
+them to create a dataset would require hundreds if not thousands of hours.
+
 On the other hand improving the solver is not a good solution long term,
 given that it will almost certainly have a worst time complexity,
-but could have some major short term benefit \newline
+but could have some major short term benefit.
+
 In particular it does not require to create a huge dataset,
@@
 and automatically label the connections using the solution he created.
-\newline\newline
+
 Given the two options, the author of this paper has chosen to focus on improving
-the solver algorithm. The choice was driven by the lack of the time needed to build a dataset,
-And the belief that creating a new algorithm,
+the solver algorithm. The choice was driven by the belief that creating a new algorithm,
 for then using that to build a dataset,
 would still be faster compared to building a dataset manually.
+
+\section{The Solver}
+The Solver that has been created is not the main focus of this paper,
+and cannot be considered state-of-the-art if compared with the current best
+digital puzzle solver. But can probably be considered so if compared with current
+"real world" puzzle Solvers.
+
+\subsection{The Algorithm}
 

### 2023-09-30 LaTeX_paper/paper.tex
continue section 4

@@
 Which makes the chance of finding the actual correct combination basically zero.
-
 \subsubsection{Conclusion}
 In this case both the match\% and the corruption rate are bad enough to make a correct reconstruction impossible.
-\newline \newline 
 To lower the limit match\% is necessary to increase the threshold, but this would increase the corruption rate.
-\newline \newline
 To lower the corruption rate is necessary to decrease the threshold, but this would increase the limit match\%.
-\newline \newline
 This means that, regardless of the threshold chosen, our comparison algorithm \ref{document:my_comparator}
@@
 It is possible that an algorithm that focuses on accuracy over speed
-coud work with our comparator.
+could work with our comparator.
 
@@
 digital puzzle solver. But can probably be considered so if compared with current
-"real world" puzzle Solvers.
+``real world'' puzzle Solvers.z
 
+\subsection{Overview}
+The algorithm itself is relatively simple.
+It is a recursive procedure that begins by identifying all 2x2 sets of pieces that match by combining four individual pieces.
+It then proceeds to identify all 4x4 sets of matching pieces by combining four 2x2 pieces, and so on.\newline
+
+\subsection{Basic Components}
+To solve the puzzle two fundamental object are used
+\begin{itemize}
+  \item SinglePiece: which contains information about a single puzzle piece.
+  \item PieceGroup\(<\)T\(>\) where T can be either a PieceGroup or a SinglePiece\newline
+  This element encompasses four elements of type T, each with its own position (top right, top left, bottom left, bottom right).
+\end{itemize}
+Both SinglePiece and PieceGroup have an ``orientation'' attribute that goes from 0 to 3~\ref{fig:orientation}.
+\begin{figure}[H]
+  \caption{orientation attribute of an object}\label{fig:orientation}
+  \centering
+  \includegraphics[height=0.3\textwidth]{pictures/orientation.png}
+\end{figure}
+
+\subsubsection{The Levels}
+
+These objects are assigned levels:
+\begin{itemize}
+\item SinglePiece is at level 0, representing a 1x1 ``solution'' to a puzzle.
+\item PieceGroup\(<\)SinglePiece\(>\) is at level 1, representing a 2x2 solution to a puzzle.
+\item PieceGroup\(<\)PieceGroup\(<\)SinglePiece\(>>\) is at level 2, representing a 4x4 solution to a puzzle, and so forth.
+\end{itemize}
+
+\subsubsection{The Behaviors}
+
+These basic objects also have the following shared behaviors:
+\begin{itemize}
+  \item 4 objects of level N can be combined to build an object of level N+1.
+  \item One object of level N has 4 sides, each of which can be compared with a side of an element of level N. This results in a compatibility shore.
+  \begin{itemize}
+    \item The comparing shore for level 0 objects is just the shore given by the comparator~\ref{document:comparator}.
+    \item The comparing shore for level N+1 objects is the average between two comparisons made with objects of level N
+  \end{itemize}
+\end{itemize}
+
+\subsubsection{Combining four objects}
+
+When combining four objects into one, some comparisons are executed to ensure that the resulting piece is a valid  combination.
+\begin{itemize}
+  \item The right side of the object in the top left position is compared with the left side of the object in the top right position~\ref{fig:merge_pieces}(1).
+  \item The bottom side of the objection the top right position is compared with the top side of the object in the bottom right position~\ref{fig:merge_pieces}(2).
+  \item The left side of the objection the bottom right position is compared with the right side of the object in the bottom left position~\ref{fig:merge_pieces}(3).
+  \item The top side of the objection the bottom left position is compared with the bottom side of the object in the top left position~\ref{fig:merge_pieces}(4).
+\end{itemize}
+
+\begin{figure}[H]
+  \caption{Example of a combination of four objects in to one}\label{fig:merge_pieces}
+  \centering
+  \includegraphics[height=0.3\textwidth]{pictures/merge_pieces.png}
+\end{figure}
+
+In order for the created object to be considered valid all of the comparisons must have a shore higher
+than the constant MIN\_SHORE\_SINGLE\_SIDE. And the average of the four comparisons must be greater
+than the constant MIN\_SHORE\_PIECE\_GROUP.
+
+The process also checks that all individual pieces inside a newly
+created object are different (because obviously is impossible to reuse the same piece twice to solve a puzzle)
 \subsection{The Algorithm}

### 2023-09-30 LaTeX_paper/paper.tex
finish section 7

@@
 \usepackage[table,xcdraw]{xcolor}
+
+% code highlighter
+\usepackage{listings}
+
+\usepackage{color}
+
+\definecolor{dkgreen}{rgb}{0,0.6,0}
+\definecolor{gray}{rgb}{0.5,0.5,0.5}
+\definecolor{mauve}{rgb}{0.58,0,0.82}
+\definecolor{orage}{rgb}{0,0.26,0.99}
+
+\lstset{frame=tb,
+  language=python,
+  aboveskip=3mm,
+  belowskip=3mm,
+  showstringspaces=false,
+  columns=flexible,
+  basicstyle={\small\ttfamily},
+  numbers=none,
+  numberstyle=\tiny\color{orage},
+  keywordstyle=\color{blue},
+  commentstyle=\color{dkgreen},
+  stringstyle=\color{mauve},
+  breaklines=true,
+  breakatwhitespace=true,
+  tabsize=3
+}
 
@@
 
+As mentioned earlier, the algorithm is implemented with a recursive function.
+The function is generic, and can take as input objects of any level.
+
+A Function of level N takes as input a list of objects of level N,
+and creates all possible objects with level N+1.
+Then it uses the newly created objects to generate a recursive call on a version
+of itself with level N+1.
+This process is repeated until the desired size is reached.
+
+\begin{minipage}{\textwidth}
+\begin{lstlisting}
+  # This function returns a list of object that match with `piece_to_match'
+  # along the direction `direction'.
+  # It also filters the data to return only pieces with an index greater than `index_filter'
+  # This function is executed in constant time, since it relies on some pre-processing of the data
+  def get_matches(piece_to_match, direction, index_filter):
+      ...
+
+  def solve<T>(pieces: List<T>):
+
+      number_of_pieces = pieces.length()
+
+      found_pieces = List::<PieceGroup<T>>::new()
+
+      # this function compare all pieces with the others, and build some data structures
+      # that are used from the function `get_matches'
+	   # the time complexity is o(N^2)
+      do_pre_processing(pieces)
+
+      # test all possible combinations for the top left piece
+      for top_left_index in 0..number_of_pieces:
+	       for top_left_orientation in 0..4:
+
+          # get the top left piece
+          top_left = get_piece(top_left_index, top_left_orientation)
+
+          # test all possible combinations of top_right, bottom_right and bottom_left
+          for top_right in get_matches(top_left, RIGHT, top_left_index):
+	           for bottom_right in get_matches(top_right, DOWN , top_left_index):
+                  for bottom_left in get_matches(bottom_right, LEFT, top_left_index):
+
+                      # try to create the new piece group
+                      new_element = PieceGroup::new(top_left, top_right, bottom_right,bottom_left)
+
+                      if new_element.is_valid():
+                          # if the 4 pieces can fit together the newly created piece
+                          # is added to the list of found pieces
+                          found_pieces.add_element(new_element)
+                      else:
+                          # otherwise the program check what the case of the 
+                          # invalid creation is, and generate a continue
+                          # on the respective loop, to speed up the operations
+                          continue_failure_cause_loop()
+
+      # at the end a recursive call is generated 
+      return solve::<PieceGroup<T>>(found_pieces)
+
+\end{lstlisting}
+\end{minipage}
+The procedure begins by testing all possible pieces and orientations as the top\_right piece.
+Then continues by finding all the other 3 pieces in an efficient way thanks to get\_matches.
+When the program has an hypothesis on the 4 pieces that can build a new piece it tries to create it.\newline
+The creation process does some checks, and if everything is successful it adds the piece to the list of found pieces.
+If the creation is not successful it figures out which piece has caused the failure, and moves to the next iteration of the respective loop.\newline
+When all combinations have been found, the function makes a recursive call and the process is repeated.\newline
+The process ensures that the piece in the top\_left is always the one with the lower index.
+This is done to avoid building the same piece 4 times with 4 different orientations.\newline
+One advantage of this algorithm is that the outer edge for loop can be easily parallelized to achieve better performances.
+
 % referneces page

### 2023-10-01 LaTeX_paper/paper.tex
add labeling tool section

@@
 
+\section{The Labeling tool}
+When the program solves a puzzle it also exports some files that could be used in the future to train
+a machine-learning based comparator.
+This section is here to explain the data available and the format used.
+
+One piece is uniquely identified by his id piece\_id.
+The id is an integer that goes from 0 to Number of pieces - 1.
+Each piece has 4 sides that can be identified by the side side\_id,
+an integer that goes from 0 to 3.
+
+\subsection{Image of each piece}
+
+Inside the folder results/pieces the program will generate one image
+for each one of the pieces of the puzzle. The pieces will be named \{piece\_id\}.jpeg.
+An example can be seen in \ref{fig:result_pieces}
+
+\begin{figure}[H]
+  \caption{}\label{fig:result_pieces}
+  \centering
+  \includegraphics[height=0.3\textwidth]{pictures/result_pieces.jpeg}
+\end{figure}
+
+\subsection{Image of each side}
+
+Inside the folder results/sides the program will generate one image 
+for each side of each piece. The images will be named \{piece\_id\}\_\{side\_id\}.jpeg.
+An example can be seen in \ref{fig:result_sides}
+
+\begin{figure}[H]
+  \caption{}\label{fig:result_sides}
+  \centering
+  \includegraphics[height=0.3\textwidth]{pictures/result_sides.jpeg}
+\end{figure}
+
+\subsection{Corners of each piece}
+The file corners.json will be generated inside the folder results.
+This file will contain a list of pieces.
+Each piece has 4 sides, and each side has the coordinates of the two points
+that delimit itself.\newline
+An example of the generated json can be seen below.
+
+\begin{minipage}{\textwidth}
+  \begin{lstlisting}
+    [
+      {
+        "piece_id": 0,
+        "side_0": {
+          "p1": {"x":955, "y":1924},
+          "p2": {"x":1024, "y":1016}
+        },
+        "side_1": {
+          "p1": {"x":1024, "y":1016},
+          "p2": {"x":1850, "y":1028}
+        },
+        "side_2": {
+          "p1": {"x":1850, "y":1028},
+          "p2": {"x":1814, "y":1992}
+        },
+        "side_3": {
+          "p1": {"x":1814, "y":1992},
+          "p2": {"x":955, "y":1924}
+        }
+      },
+      {...},
+      {...},
+      ...
+    ]
+  \end{lstlisting}
+\end{minipage}
+
+\subsection{Match for each side}
+The file connections\_result.json will be generated
+inside the folder results. This file will contain a list of pieces,
+each piece has 4 sides, and each side has a link to the side of the piece
+that matches it. The link can be null if the side is along the border.\newline
+An example of the generated json can be seen below.
+
+\begin{minipage}{\textwidth}
+  \begin{lstlisting}
+    [
+      {
+        "piece_id": 12,
+        "side_0": {
+            "piece": 5,
+            "side": 0
+        },
+        "side_1": {
+            "piece": 8,
+            "side": 0
+        },
+        "side_2": {
+            "piece": 0,
+            "side": 0
+        },
+        "side_3": null
+      },
+      {...},
+      {...},
+      ...
+    ]
+
+  \end{lstlisting}
+\end{minipage}
+
+\section{Conclusions}
+In conclusion, this paper's objective can be considered achieved.
+It has been documented why real-world puzzles are harder than digital puzzles.
+It has also been shown that the same algorithm can have drastically worse
+performance when working with real-world puzzles compared to digital ones.
+
+A highly effective labeling tool has also been developed.
+It could be used in the future to create a machine learning-based comparator that could significantly
+improve the time needed to solve this problem by providing more accurate data.
+
+Even the solver that has been created can be considered a success.
+His time complexity is horrible if compared with current state-of-the-art digital puzzle solvers.
+But if compared with real world one the algorithm is probably one of the best, if not the best, available online.
+
 % referneces page

### 2023-10-01 LaTeX_paper/paper.tex
finish paper V1

@@
 \usepackage{wrapfig}
+
+\usepackage{multirow}
 
@@
 
-\section{The Objective Of This Paper}
+\section{The Objective Of This Paper}\label{document:objective}
 After reading some of the previous literature for this problem, some conclusions could be drawn:
@@
 
-\subsubsection{Definitions}
+\subsubsection{Definitions}\label{document:proof_definitions}
 This set of definitions are useful to better understand the next section:
@@
 
-\section{The Solver}
+\section{The Solver}\label{document:my_solver}
 The Solver that has been created is not the main focus of this paper,
@@
 
-\subsubsection{Combining four objects}
+\subsubsection{Combining four objects}\label{document:combining_four_objects}
 
@@
 One advantage of this algorithm is that the outer edge for loop can be easily parallelized to achieve better performances.
+
+\section{Testing Results}
+
+In this section the solver that has been proposed by this paper will be tested.
+This test will serve two purposes:
+Understanding the performance and limitations of the proposed algorithm
+Been able to test the same algorithm with both digital, and real world jigsaw puzzles, to understand the differences between the two.
+
+\subsection{Setup}
+The test sample consist in 5 different puzzle:
+\begin{itemize}
+  \item a 4x4 real world puzzle
+  \item a 8x8 real world puzzle
+  \item a 4x4 digital puzzle
+  \item a 8x8 digital puzzle
+  \item a 16x16 digital puzzle
+\end{itemize}
+The real world puzzles have been obtained with a printer’s scanner,
+and the digital puzzles have been obtained from \url{https://puzzle.telegnom.org/}.\newline
+The constants MIN\_SHORE\_SINGLE\_SIDE and MIN\_SHORE\_PIECE\_GROUP mentioned in section
+\ref{document:combining_four_objects} were set at different values
+depending on the nature of the puzzle (real or digital).\newline
+The test has been performed on a ryzen 5 5600 CPU with 16 GB of RAM.
+The time measured in the test does not include the execution time of the Comparator
+\ref{document:my_comparator}, but only the one of the Solver~\ref{document:my_solver}.
+
+\subsection{Results}
+
+\begin{table}[H]
+  \centering
+  \begin{tabular}{
+  >{\columncolor[HTML]{D9EAD3}}c 
+  >{\columncolor[HTML]{D0E0E3}}c 
+  >{\columncolor[HTML]{E6B8AF}}c 
+  >{\columncolor[HTML]{FCE5CD}}c }
+  \cellcolor[HTML]{B6D7A8} &
+    \cellcolor[HTML]{A2C4C9} &
+    \multicolumn{2}{c}{\cellcolor[HTML]{EA9999}Execution time {[}s{]}} \\
+  \multirow{-2}{*}{\cellcolor[HTML]{B6D7A8}Size} &
+    \multirow{-2}{*}{\cellcolor[HTML]{A2C4C9}Pieces} &
+    \cellcolor[HTML]{DD7E6B}Digital puzzle &
+    \cellcolor[HTML]{F9CB9C}Real Puzzle \\
+  4x4   & 16  & 4   & 59   \\
+  8x8   & 64  & 30  & 2851 \\
+  16X16 & 256 & 377 & N/A 
+  \end{tabular}
+\end{table}
+
+\subsection{Accuracy}
+It is important to note that the project does not have a way to evaluate the accuracy
+of the results automatically. But the accuracy for the two real world puzzles
+has been asserted manually. And both of them are 100\% correct.
+
+\subsection{Analysis}
+
+This paper has claimed from the start that real world puzzles were harder than digital ones.
+Some intuitive explanations were given to justify this claim,
+but a formal proof has never been given.
+This test finally proves the claim, by showing that the same algorithm can have vastly
+different time performances depending on the accuracy of the input data.
+
+It is fair to say that the performance of the algorithm are not amazing,
+but they are good enough to achieve the objective of this paper \ref{document:objective}.
+It is also worth remembering that the problem itself is extremely complex.
+Using the formula introduced in section \ref{document:proof_definitions} we can calculate that a 64 piece puzzle,
+like the one that has been solved before, has approximately \(4 \cdot 10^{127}\) possible combinations.
+\[C = N! \cdot 4^N =  64! \cdot 4^{64} \approx 4.32 \cdot 10^{127}\]
 

### 2023-10-01 LaTeX_paper/paper.tex
backup commit

@@
 is evaluated.
-The data is then used to demonstrate its incompatibility with the current
+The data are then used to demonstrate its incompatibility with the current
 state-of-the-art algorithm. At this juncture,
@@
 \subsection{Classification}
-This paper will focus on type 2 puzzles. A type 2 puzzle is a puzzle where the position, and the orientation of each piece is unknown. 
+This paper will focus on Type 2 puzzles. A Type 2 puzzle is one where the position and orientation of each piece are unknown.
 \subsection{Digital vs Real-World Jigsaw Puzzles}
@@
 There is  another important distinction between different types of puzzles.
-They can be divided into “digital” and “real world” jigsaw puzzles.\label{document:DigitalVSReal}
+They can be divided into “digital”~\ref{fig:figure_digital_puzzle} and “real world”~\ref{fig:figure_real_puzzle} jigsaw puzzles.
+The difference between the two is quite self explanatory, and can be observed in the respective pictures.
+\label{document:DigitalVSReal}
 
@@
 is far easier with a digital puzzle,
-since there are far less things that can go wrong.
+since there are far fewer things that can go wrong.
+For example, a piece's shape may be distorted by
+a low-quality cut, as seen in picture \ref{fig:figure_measurement_error}
 
@@
 \section{Previous Literature}
-This section will analyze 3 different algorithms that have been proposed
-as a solution of type 2 puzzles. The objective is to understand the
-strengths and the weaknesses of each one, to build up some knowledge
-that will be useful for the next sections.
+This section will analyze three different algorithms that have been
+proposed as solutions for type 2 puzzles.
+The objective is to understand the strengths and weaknesses of each one,
+in order to build up knowledge that will be useful for the next sections.
 
@@
     \subsubsection{The Splitter:} This component takes as input one or more images
-    containing all the pieces. It then split all the pieces from each other,
+    containing all the pieces. It then separates all the pieces from each other,
     and split each piece into his four sides.\label{document:splitter}
@@
 
-    \subsubsection{The Solver:} This component  uses the information provided by the
-    Comparator~\ref{document:comparator}, and tries to find a solution
+    \subsubsection{The Solver:} This component utilizes the information provided by the
+    Comparator~\ref{document:comparator}, and attempts to find a solution
     (i.e.\ a position and an orientation for each piece)
@@
 \subsection{Solving Jigsaw Puzzles By The Graph Connection Laplacian~\cite{GCL}}
-This algorithm falls in the ``binary comparison'' category~\cref{document:comparator}.
+This algorithm falls within the ``binary comparison'' category~\ref{document:comparator}.
 And can be used to understand the strength and weaknesses
 of this approach.\newline
-The main benefit of this approach is speed,  having a binary comparison allows
-some specific optimization, in particular the use of some graph theory techniques.\newline
-The  algorithm has a time complexity of ruffly \(O(N^2)\). Which is in line with the theoretical
-minimum for jigsaw puzzle solving, according to the study:
+The primary advantage of this approach lies in its speed;
+the utilization of binary comparison permits specific optimizations,
+particularly leveraging graph theory techniques.\newline
+The algorithm exhibits a time complexity of approximately \(O(N^2)\),
+a value consistent with the theoretical minimum for
+jigsaw puzzle solving, as outlined in the study
 ``No easy puzzles: Hardness results for jigsaw puzzles~\cite{ON2Claim}''.\newline
-The negative aspect might be the accuracy, since by using only two states
-(match or not match) some informations are lost, compared to a non binary comparison.
+However, a potential drawback may arise in terms of accuracy.
+This stems from the fact that, with only two states
+(matching or not matching),
+certain details may be lost when compared to a non-binary comparison. 
 To quantify accuracy the paper used the ``neighbors compariso'' metric,
@@
 \subsection{A Genetic Algorithm-Based Solver for Very Large Jigsaw Puzzles~\cite{GA}}
-This paper applies a genetic algorithm to the jigsaw puzzle problem, with some promising results.\newline
-The algorithm seems to have a \(O(N^2)\) time complexity, with time slightly lower than the previous example
-(But it is impossible to know for sure which one is faster, given that they didn't specify the hardware used).\newline
-The paper has used the same method to evaluate accuracy that the previous one used
-(neighbors comparison) so it is easy to compare them.\newline
-The algorithm falls in the “Non binary comparison”~\ref{document:comparator};
-this should give it an advantage, since it has more data to work with.\newline
+This paper employs genetic algorithms to address the
+jigsaw puzzle problem, yielding promising results.\newline
+The algorithm seems to have a \(O(N^2)\) time complexity,
+with execution time slightly lower than the previous example
+(However, it remains uncertain which one is faster, as the papers did not specify
+the particular hardware configuration used).\newline
+The paper adopts the same evaluation method for accuracy as the previous example,
+namely neighbor comparison, facilitating direct comparison between the two approaches.
+This algorithm falls under the category of “Non binary comparison”~\ref{document:comparator}
+a distinction that theoretically grants it an advantage due to the increased granularity
+of input data.
 Unfortunately this advantage does not compensate for the worst precision
@@
 it might be possible that the accuracy would have been better if they had allowed
-it to run for more generations.\label{document:GA}
+the algorithm to run for more generations.\label{document:GA}
 
 \subsection{Computer Vision Powers Automatic Jigsaw Puzzle Solver~\cite{Abto}}
-The solutions~\ref{document:GCL} and~\ref{document:GA} can be considered ``state-of-the-art'' for digital jigsaw puzzles.
-But, as already introduced in section~\ref{document:DigitalVSReal},
-appalling the solution to the real world can be challenging.\newline
-This solution is one of the best, and well documented implementations for real world puzzles.\newline
-In reality calling this ``solution'' is incorrect,
-since all it does is find the best 8 matches and asks the user which one to place.
-Making the algorithm not autonomous.\newline
-Even ignoring this major detail, making an analysis of this solution has proven to be challenging,
-since the article is more of a publicity stunt than an academic paper.
-In fact, the code is not open source and the informations about the time needed to solve the puzzle are missing.\newline
-The article only shows a single puzzle solved, with a 9$\times$6 dimension.\newline
-Even with all of these caveats this article still is one of the best example of a solution for real world puzzles.
+Solutions~\ref{document:GCL} and~\ref{document:GA} can be considered ``state-of-the-art''
+for digital jigsaw puzzles.
+However, as already introduced in section ~\ref{document:DigitalVSReal},
+translating these solutions to the real world can be challenging.\newline
+This article represents one of the most comprehensive and well-documented
+implementations for real-world puzzles. However,
+it's important to note that referring to this approach as a 'solution'
+may be misleading, as it primarily identifies the top eight matching
+pieces for a specific point and subsequently relies on user input to make
+the final placement decision
+This aspect renders the algorithm non-autonomous..\newline
+Even disregarding this significant detail,
+conducting an analysis of this solution has proven to be challenging,
+as the article leans more towards a publicity stunt than an academic paper.
+In fact, the code is not open source, and information regarding the time needed
+to solve the puzzle is absent. The article only showcases a single puzzle solved,
+with dimensions of 9\(\times\)6.\newline
+Despite these limitations, this article still stands as one of the best examples of a solution
+for real-world puzzles.
 
 \section{The Objective Of This Paper}\label{document:objective}
-After reading some of the previous literature for this problem, some conclusions could be drawn:
-The problem of ``digital'' jigsaw puzzle has been solved many times, and is already well optimized.\newline
-On the other hand, the problem of ``real world'' jigsaw puzzle has mostly been ignored
+After reading some of the previous literature on this problem, some conclusions could be drawn:
+The problem of digital jigsaw puzzle has been solved many times, and is already well optimized.\newline
+On the other hand, the problem of real-world jigsaw puzzle has mostly been ignored
 by the academic community.\newline
 The first objective for this paper is to fill this void, and been the first formal paper to analyze the
-``real world'' jigsaw puzzle problem.\newline
-The second objective of this paper is to use the research that has been done to create a labeling tool.\newline
+real-world jigsaw puzzle problem.\newline
+The second objective is to use the research that will be conducted for this paper to create a labeling tool.\newline
 The reason behind this objective is that the biggest challenge for real world puzzles is creating a
-reliable comparator~\ref{document:comparator}. That can deal with all the noisy 
-images you get from the real world.\newline
+reliable comparator~\ref{document:comparator}, that could provide accurate information even with noisy 
+input data, that are obtained from real-world measure.\newline
 It is easy to see how a machine learning based comparator would probably be the best solution, 
@@
 pieces to train the model would take ages.
-Instead an automatic tool would be abel to scan a small $4\times4$ puzzle in one shot,
-solve it, and return the labeled data in just a couple minutes.
+Instead an automatic tool would allow to scan a small $4\times4$ puzzle in one shot,
+solve it, and return the labeled data in just minutes.
 
@@
 
-To fulfill the objective of this paper three some data to work with are needed.
-This section will cover the input data used, and the Splitter~\ref{document:splitter}
+To fulfill the objective of this paper some data to work with are needed.
+This section will cover the input data used as well as the Splitter~\ref{document:splitter}
 and Comparator~\ref{document:comparator} algorithms.

### 2023-10-05 LaTeX_paper/paper.tex
correct paper to section 5.1

@@
 \section{The Objective Of This Paper}\label{document:objective}
-After reading some of the previous literature on this problem, some conclusions could be drawn:
-The problem of digital jigsaw puzzle has been solved many times, and is already well optimized.\newline
-On the other hand, the problem of real-world jigsaw puzzle has mostly been ignored
-by the academic community.\newline
-The first objective for this paper is to fill this void, and been the first formal paper to analyze the
-real-world jigsaw puzzle problem.\newline
-The second objective is to use the research that will be conducted for this paper to create a labeling tool.\newline
-The reason behind this objective is that the biggest challenge for real world puzzles is creating a
+After a review of the existing literature on this problem, some conclusions could be drawn:
+The "digital" jigsaw puzzle dilemma has been extensively addressed and is already
+well-optimized. Conversely, the "real-world" counterpart has largely been
+overlooked within the academic community.\newline
+The first objective for this paper is to fill this void, and been the first formal paper
+to analyze the real-world jigsaw puzzle problem.\newline
+The second objective is to use the forthcoming research to create a labeling tool.\newline
+This objective is motivated by the fact that the biggest challenge for real world puzzles is creating a
 reliable comparator~\ref{document:comparator}, that could provide accurate information even with noisy 
-input data, that are obtained from real-world measure.\newline
+input images, that are obtained from real-world measure.\newline
 It is easy to see how a machine learning based comparator would probably be the best solution, 
-but this has some problems, in fact having to manually scan and label thousands of individual puzzle
+but this poses problems, in fact having to manually scan and label thousands of individual puzzle
 pieces to train the model would take ages.
@@
 
-To fulfill the objective of this paper some data to work with are needed.
-This section will cover the input data used as well as the Splitter~\ref{document:splitter}
+To fulfill the objectives of this paper,
+it is essential to have the necessary data for analysis.
+This section will encompass the input data utilized,
+as well as the Splitter~\ref{document:splitter}
 and Comparator~\ref{document:comparator} algorithms.
@@
 
-The first step is finding a real world puzzle to solve;
-It has been decided to use a classic 1000 piece 66cm x 50cm  puzzle, and use a printer's
-scanner to digitize the pieces.\newline 
-The puzzle has been scanned in various sub-sizes to allow the testing of different configurations. 
-A resolution of 1200 ppi has been used to ensure a sharp and precise image
-of the piece, as seen in image~\ref{fig:figure_measurement_error}.
+The first step involves selecting a real-world
+puzzle for solving. It has been decided to utilize a
+classic 1000-piece puzzle measuring 66cm x 50cm.
+A printer's scanner is employed to digitize the individual pieces.\newline
+
+The puzzle has been scanned in various sub-sizes to facilitate the testing of different configurations.
+A resolution of 1200 pixels per inch (ppi) has been employed to ensure a sharp and precise
+depiction of the pieces, as seen in image~\ref{fig:figure_measurement_error}.
 The puzzle has been scanned backward, using a black background.
@@
 This choice has been dictated by the fact that the scanner used has the flashlight
-slightly off centered from the scanner's sensor.
+slightly off-centered from the scanner's sensor.
 And this causes a shadows to be cast on one side of the pieces.

### 2023-10-06 LaTeX_paper/paper.tex
finish review of section 6

@@
 \subsection{Splitting The Pieces}
-As introduced in section~\ref{document:splitter}, the first step to solve a puzzle
-is to split an image composed of many pieces into individual ones.
+
+As introduced in section~\ref{document:splitter},  the initial stage in puzzle solving involves
+splitting an image composed of many pieces into individual ones.
 This is relatively straightforward, and can be done with the following steps:
@@
   \item Find all individual Blobs
-  (a Blob is just set of connected pixels with the same color) and for each one:
+  (a Blob is defined as a set of connected pixels with the same color) and for each one:
 
@@
 
-The next step following the general template~\ref{document:splitter}
-is to split a pieces into
+The next step following the general structure~\ref{document:splitter}
+is to split a piece into
 his 4 sides, this could be done with the following steps:
@@
   \item \textbf{Remove the holes from the piece:}\newline
-  To do so the program computes the convex hull of the piece~\ref{fig:s_s_ch},
-  then calculates the difference between the convex hull and the original image,
-  and obtains an image with the “filler areas”~\ref{fig:fig:s_s_og_minus_ch}.
-  These filler areas have very different shapes,
-  depending on what has generated them (a “hole” or a “knob” in the piece).
-  So they can be classified, and added to the original piece only if
-  they are generated by a hole, obtaining an image without holes~\ref{fig:s_s_no_holes}.
-
-  \item \textbf{Remove the knobs from he piece}\newline
-  To do so the image without holes gets eroded~\ref{fig:s_s_erosion} and then dilated~\ref{fig:s_s_dilatation}.
-  This generates an image that resembles the original one, but has no knobs.
-  Then the program finds the pixels that are white in the image without holes,
-  but not in the image that has been eroded and dilated.
-  This generates a set of Blobs~\ref{fig:s_s_no_holes_minus_expansion},
-  but again, the shape of one blob is very different depending on what has generated it
-  (an “angle” or a “knob”), so they can be classified.
-  Then the program removes from the image with no holes all the pixels that are
-  close to a Blob generated by a knob, obtaining an image without knobs and holes~\ref{fig:s_s_no_knobs}.
-
-  \item \textbf{Find the coordinates of the four corners}\newline
-  To find the coordinates of the corners, the program uses a tree steps approximation.
-  It initially finds the minimum enclosing rectangle,
-  and uses the coordinates of the corners of the rectangle
-  as first approximation~\ref{fig:s_s_min_enc_rec}.\newline
-  As a second approximation it takes,
-  from the white pixels that are close to the first approximation,
-  the pixel that has the most black pixels within a certain distance.
+  To remove the holes from the piece, the program employs a three-step process. Initially it
+  computes the convex hull of the piece~\ref{fig:s_s_ch}.
+  Subsequently it calculates the difference between the convex hull and the original image,
+  resulting in an ``image with filler areas''~\ref{fig:fig:s_s_og_minus_ch}.
+  It can be noted that these filler areas have distinct shapes,
+  depending on what has generated them (either a ``hole'' or a ``knob'').
+  Therefore they can be categorized.
+  Finally the filler areas are added back to the only if
+  they originated from a hole. This results in an image where the holes
+  have been filled~\ref{fig:s_s_no_holes}
+
+  \item \textbf{Remove the knobs from he piece:}\newline
+  In order to remove the knobs from the piece, the image without holes
+  undergoes an erosion~\ref{fig:s_s_erosion} followed by a dilation~\ref{fig:s_s_dilatation}.
+  This process results in an image that resembles the original, but without any knobs.
+  Subsequently, the program identifies the pixels that are white in the image without holes~\ref{fig:s_s_no_holes},
+  but not in the eroded and dilated version~\ref{fig:s_s_dilatation}.
+  This leads to the formation of a set of blobs ~\ref{fig:s_s_no_holes_minus_expansion}.
+  It is important to note that the shape of a blob can vary significantly depending on whether it originated
+  from an ``angle'' or a ``knob'' and thus they can be classified accordingly.
+  Following this, the program proceeds to eliminate from the hole-free
+  image all pixels that are in close proximity to a blob generated by a knob.
+  This operation yields an image that is both devoid of knobs and holes~\ref{fig:s_s_no_knobs}.
+
+  \item \textbf{Find the coordinates of the four corners:}\newline
+  In order to determine the coordinates of the corners,
+  the program employs a three-step approximation method.
+  Initially, it identifies the minimum enclosing rectangle and
+  utilizes the coordinates of its corners
+  as the first approximation~\ref{fig:s_s_min_enc_rec}.\newline
+  For the second approximation, the program selects,
+  from the white pixels in close proximity to the first approximation,
+  the pixel that contains the highest number of black pixels
+  within a specified range.
   Then it considers only the pixels that are within a certain
@@
   enclosing triangle of sed pixels~\ref{fig:s_s_min_enc_triangle}.\newline
-  The corner of the triangle that is closest to the second
-  approximation is the third and final approximation
-  of the corner of the piece.
+  The corner of the triangle that is nearest to the second
+  approximation serves as the third and final approximation
+  for the corner of the puzzle piece.
   The position of the four corners can be seen in image~\ref{fig:s_s_corners_found}.
 
-  \item \textbf{Split each side using the previously found coordinates.}\newline
-	Once the program has found the four coordinates of the corners, to obtain each
-  side. An example of a single side can be seen in image~\ref{fig:s_s_a_piece_side}.
+  \item \textbf{Split each piece into four sides using the previously found coordinates:}\newline
+	After the program has successfully identified the four corner coordinates,
+  it can straightforwardly derive each of the four sides.
+  An example of a single side can be seen in image F4l.~\ref{fig:s_s_a_piece_side}.
 \end{itemize}
@@
 \subsection{Comparing The Sides}\label{document:my_comparator}
-The last step needed before it is possible to start working on
-a solver algorithm, is to compare the sides that have been
-generated by the previous step.\newline
+The last step in the setup, is to compare the sides that have been
+generated before.\newline
 In order to generate a compatibility shore,
@@
 \begin{itemize}
-  \item For each side, it considers only the border, and it makes the border thicker.
+  \item For each side, it considers only the border, and  makes it thicker.
   \item It puts two sides attached to each other using the coordinates of the corners (In the same way a human would do to test if two pieces fit together).
@@
 \section{Applying Already Existing Algorithms To The Real World}
-Now that the setup is completed, it is possible to test the already existing
-algorithms with real world puzzles, to see if they can work. For this test,
-the fist algorithm~\ref{document:GCL} has been chosen, because the paper is full of detail.
-In particular it had some information about the accuracy of the algorithm in
-function to the corruption rate, which are essential for this analysis.
-
-The tests that have been conducted have shown that our comparator algorithm~\ref{document:my_comparator}
-and the “Graph Connection Laplacian” solution~\ref{document:GCL} are not compatible with each other.
-A proof for this claim follows.
+With the initial setup completed, it is now possible to
+test the existing algorithms with real-world puzzle. For this test,
+the fist algorithm~\ref{document:GCL} is selected due to the comprehensive
+details provided in the paper. Notably, it contains information
+regarding the algorithm's accuracy in relation to the corruption rate,
+which is crucial for this analysis.
+
+The conducted tests reveal that the Comparator developed in this paper~\ref{document:my_comparator}
+and the "Graph Connection Laplacian" solution ~\ref{document:my_comparator} are not compatible with each other.
+A formal proof supporting this assertion is presented subsequently.
 
@@
 
-This section will provide a proof for the incompatibility of
-the two algorithms mentioned above.
-\newline
 The comparison algorithm deceived in section~\ref{document:my_comparator} outputs a compatibility
 shore that goes from 0 to 1.\newline
-But the algorithm~\ref{document:GCL} takes as input a binary value,
-which means that it is necessary to apply a threshold to the input
+But the algorithm~\ref{document:GCL} takes as input a binary value.
+Which means that it is necessary to apply a threshold to the input
 data to convert them from float to bool.
@@
   \item \textbf{match\%:}\newline
-  The probability that 2 random sides match.
+  The probability that 2 randomly selected sides matches.
 
   \item \textbf{correct combination match\% (or c.c match\%):}\newline
-  The probability that 2 sides match given that in the correct puzzle
-  solution they actually are close to each other. ideally this should be 1.
+  The probability that 2 randomly selected sides matches given that in the correct puzzle
+  solution they are actually close to each other. Ideally this should be 1.
 
@@
   Given that this measure has been taken on a 16 piece puzzle,
-  the match\% is highly influenced by the correct piece matching.
-  With a bigger puzzle the match\% would be lower.
+  the match\% is highly influenced by the correct piece matching together.
+  With a bigger puzzle the match\% would be lower (Given that the amount
+  of correct couple of sides scales with N, while the amount of
+  possible couple of sides scales with \(N^2\). Where N is the number of pieces).\newline
   Limit match\% is an approximation of what the match\%
-  would be in the limit for \(N \rightarrow + \infty\) (where N is the number of pieces).
+  would be in the limit for \(N \rightarrow + \infty\).
   This value is obtained by subtracting to match\%
@@
   multiplied by the probability that the comparison returns true
-  (which is c.c match\%). ideally this should be almost zero.
+  (which is c.c match\%). \newline
+  Ideally limit match\% should be almost zero.
   \[limit \: math\% = math\% - \frac{c.c. \: mathc\%}{16 \times 4}\]
@@
   \item \textbf{corruption rate:}\newline
-  Is defined as: \(1-\sqrt{c.c \: match\%}\). ideally this should be 0.
+  Is defined as: \(1-\sqrt{c.c \: match\%}\). Ideally this should be 0.
 
@@
 % If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
-\begin{table}[]
+\begin{table}[H]
   \centering
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
     \caption{match metrics vs threshold used}\label{fig:match_metrics_vs_threshold_used}
@@
 
-Assuming the algorithm has to solve a 500 piece puzzle, with a limit match\% of 0.04
-and a corruption rate of 0.057 (data taken from the line in red);
-what would this mean in terms of accuracy of the results?
+Now, let's consider Algorithm \ref{document:GCL} tasked with solving a 500-piece puzzle
+using our Comparator \ref{document:my_comparator}.
+A threshold of 0.425 is chosen;
+This implies a imit match\% of 0.04 and a corruption rate of 0.057.
+What would this mean in terms of accuracy of the results?
 
@@
   A puzzle with N pieces can be put together in many different ways,
-  (even if not all of 	them actually fit together).
+  (Even if not all of 	them actually fit together).
   The total number of possible combinations is \(N! \times 4^N\) where
@@
 
-From the graph \ref{fig:GCL_Corruption_Rate}, it can be observed that with a corruption rate of 0.057,
-a neighbors comparison value of about 80\%
-can be expected. Which means that one in every 5 connections on average will be wrong.
-So in a puzzle of 500 pieces (which has approximately 1000 connections),
-200 connections will be wrong on average.
-It is fair to say that this is not an ideal result.
+In Figure \ref{fig:GCL_Corruption_Rate}, it can be observed that at a corruption rate of 0.057,
+a neighbors comparison metric of roughly 80\% can be anticipated.
+This implies that, on average, one out of every five connections will be incorrect.
+In the context of a puzzle comprising 500 pieces (equating to approximately 1000 connections),
+an estimated 200 connections will be inaccurate on average.
+It is reasonable to assert that this outcome is suboptimal.
 
 \subsubsection{Limit Match\% Analysis}
-As seen earlier, the limit match percentage is \(4\%\).\newline \newline
-Given that in a puzzle of N pieces there are around \(2N \) connections,
+Let's remember that \(limit\_match\% = 0.04\).
+
+Given that in a puzzle with N pieces there are around \(2N \) connections,
 the probability of one random combination to be a
-possible correct combination is: \(0.054^{2N}\).\newline \newline
+possible correct combination is: \(0.04^{2N}\).
+
 The total number of possible combinations are \(N! \times 4^N\),
-which means that on average, on a puzzle with \(N\) pieces,
-there will be \(0.054^{2N} \times N! \times 4^N \)
-possible correct combinations.\newline \newline
+which means that on average, in a puzzle with \(N\) pieces,
+there will be \(0.04^{2N} \times N! \times 4^N \)
+possible correct combinations.
+
 For \( N = 500 \) the expected number of possible combinations is around \( 1.5 \times 10^{37} \).
@@
 In this case both the match\% and the corruption rate are bad enough to make a correct reconstruction impossible.
-To lower the limit match\% is necessary to increase the threshold, but this would increase the corruption rate.
+To lower limit match\% is necessary to increase the threshold, but this would increase the corruption rate.
 To lower the corruption rate is necessary to decrease the threshold, but this would increase the limit match\%.
@@
 
-There are two way to solve this deadlock:
+There are two viable approaches to overcome this challenge.
+It is either necessary to enhance the Comparator while continuing
+to utilize the state-of-the-art solver,
+or it is possible to re-design the solver algorithm and create one
+specifically designed to operate with noisier data.
 
@@
 Improving the comparator can shortly be done.
-Some minor improvements can be made by spending some time tweaking the current algorithm.
-But it is clear that, for such a task,
-the optimal solution is probably to use machine learning.
+Some minor improvements can be made by spending some time
+tweaking the current algorithm.
+However, it is evident that for a task of this nature,
+the most viable solution would likely involve
+leveraging machine learning techniques.
 
@@
 
-Different algorithms have different resilience to corrupted data.
-All the major algorithms that have been proposed since now, focus on speed.
-It is possible that an algorithm that focuses on accuracy over speed
-could work with our comparator.
+The puzzle dilemma is a ``multiobjective optimization problem'',
+where one objective is optimizing the time complexity,
+and the other is optimizing the accuracy of the algorithm
+in the presence of corrupted data.
+All the major algorithms proposed up to this point have prioritize speed.
+However, it is conceivable, and even probable,
+that an algorithm prioritizing accuracy over speed could prove
+effective with our comparator
 
@@
 
-Improving the comparator is probably the best long term solution,
-but it comes with a problem:\newline
-Manually testing if some pieces fit together, then making a scan, and finally label
-them to create a dataset would require hundreds if not thousands of hours.
-
-On the other hand improving the solver is not a good solution long term,
-given that it will almost certainly have a worst time complexity,
-but could have some major short term benefit.
-
-In particular it does not require to create a huge dataset,
-and could be used to build one.
-In Fact it could solve hundreds of small puzzles,
-and automatically label the connections using the solution he created.
-
-Given the two options, the author of this paper has chosen to focus on improving
-the solver algorithm. The choice was driven by the belief that creating a new algorithm,
-for then using that to build a dataset,
-would still be faster compared to building a dataset manually.
+Improving the comparator is likely the most effective long-term solution,
+but it presents a significant challenge: manually testing if certain
+pieces fit together, followed by scanning and labeling,
+is a time-intensive process that could require hundreds,
+if not thousands, of hours.
+
+On the other hand, improving the solver may not be the optimal long-term
+solution, as it is likely to result in a worse time complexity.
+However, it could yield significant short-term benefits.
+
+Notably, this approach does not necessitate the creation of an extensive dataset
+and has the potential to facilitate its development.
+In fact, it could have the capability to solve numerous small
+puzzles and subsequently auto-label the connections
+based on the solutions it generates.
+
+Given the two options, it has been decided to focus on improving
+the solver algorithm. This choice was driven by the belief
+that creating a new algorithm, and subsequently using it to
+generate a dataset, would still be a more time-efficient
+approach compared to manually constructing a dataset.
 
@@
 digital puzzle solver. But can probably be considered so if compared with current
-``real world'' puzzle Solvers.z
+``real world'' puzzle Solvers.
 
@@
   8x8   & 64  & 30  & 2851 \\
-  16X16 & 256 & 377 & N/A 
+  16x16 & 256 & 377 & N/A 
   \end{tabular}

### 2023-10-06 LaTeX_paper/paper.tex
fix typos

@@
 To quantify accuracy the paper used the ``neighbors compariso'' metric,
-which ``calculates the percentage of pairs of image patches that are matched correctly''.\label{document:GCL}
+which ``calculates the percentage of pairs of image patches that are matched correctly''.
+This will be useful later\label{document:GCL}
 
@@
 implementations for real-world puzzles. However,
-it's important to note that referring to this approach as a 'solution'
+it's important to note that referring to this approach as a ``solution''
 may be misleading, as it primarily identifies the top eight matching
 pieces for a specific point and subsequently relies on user input to make
-the final placement decision
+the final placement decision.
 This aspect renders the algorithm non-autonomous..\newline
@@
 as the article leans more towards a publicity stunt than an academic paper.
-In fact, the code is not open source, and information regarding the time needed
-to solve the puzzle is absent. The article only showcases a single puzzle solved,
+In fact, the code is not open source, and informations regarding the time needed
+to solve the puzzle are absent. The article only showcases a single puzzle solved,
 with dimensions of 9\(\times\)6.\newline
@@
 After a review of the existing literature on this problem, some conclusions could be drawn:
-The "digital" jigsaw puzzle dilemma has been extensively addressed and is already
-well-optimized. Conversely, the "real-world" counterpart has largely been
-overlooked within the academic community.\newline
+The ``digital'' jigsaw puzzle dilemma has been extensively addressed and is already
+well-optimized. Conversely, the ``real-world'' counterpart has largely been
+overlooked within the academic community.
+
 The first objective for this paper is to fill this void, and been the first formal paper
-to analyze the real-world jigsaw puzzle problem.\newline
-The second objective is to use the forthcoming research to create a labeling tool.\newline
+to analyze the real-world jigsaw puzzle problem.
+
+The second objective is to use the forthcoming research to create a labeling tool.
+
 This objective is motivated by the fact that the biggest challenge for real world puzzles is creating a
 reliable comparator~\ref{document:comparator}, that could provide accurate information even with noisy 
-input images, that are obtained from real-world measure.\newline
+input images, that are obtained from real-world measure.
+
 It is easy to see how a machine learning based comparator would probably be the best solution, 
@@
 classic 1000-piece puzzle measuring 66cm x 50cm.
-A printer's scanner is employed to digitize the individual pieces.\newline
+A printer's scanner is employed to digitize the individual pieces.
 
@@
   Therefore they can be categorized.
-  Finally the filler areas are added back to the only if
+  Finally the filler areas are added back to the original only if
   they originated from a hole. This results in an image where the holes
@@
   Following this, the program proceeds to eliminate from the hole-free
-  image all pixels that are in close proximity to a blob generated by a knob.
+  image~\ref{fig:s_s_no_holes} all pixels that are in close proximity to a blob generated by a knob.
   This operation yields an image that is both devoid of knobs and holes~\ref{fig:s_s_no_knobs}.
@@
   it can straightforwardly derive each of the four sides.
-  An example of a single side can be seen in image F4l.~\ref{fig:s_s_a_piece_side}.
+  An example of a single side can be seen in image .~\ref{fig:s_s_a_piece_side}.
 \end{itemize}
@@
 The last step in the setup, is to compare the sides that have been
-generated before.\newline
+generated before.
 In order to generate a compatibility shore,
@@
 The conducted tests reveal that the Comparator developed in this paper~\ref{document:my_comparator}
-and the "Graph Connection Laplacian" solution ~\ref{document:my_comparator} are not compatible with each other.
+and the ``Graph Connection Laplacian'' solution ~\ref{document:my_comparator} are not compatible with each other.
 A formal proof supporting this assertion is presented subsequently.
@@
   \item \textbf{limit match\%:}\newline
-  Given that this measure has been taken on a 16 piece puzzle,
+  Given that this measures has been taken on a 16 piece puzzle,
   the match\% is highly influenced by the correct piece matching together.
@@
 A threshold of 0.425 is chosen;
-This implies a imit match\% of 0.04 and a corruption rate of 0.057.
+This implies a limit match\% of 0.04 and a corruption rate of 0.057.
 What would this mean in terms of accuracy of the results?
@@
 \section{The Solver}\label{document:my_solver}
-The Solver that has been created is not the main focus of this paper,
-and cannot be considered state-of-the-art if compared with the current best
-digital puzzle solver. But can probably be considered so if compared with current
-``real world'' puzzle Solvers.
+The Solver that has been developed is not the primary focus of this
+paper and cannot be considered state-of-the-art when compared
+to the current best digital puzzle solvers. However, it may be
+considered as such when compared to existing ``real-world'' puzzle solvers.
 
 \subsection{Overview}
-The algorithm itself is relatively simple.
-It is a recursive procedure that begins by identifying all 2x2 sets of pieces that match by combining four individual pieces.
-It then proceeds to identify all 4x4 sets of matching pieces by combining four 2x2 pieces, and so on.\newline
+The algorithm itself is relatively straightforward.
+It operates as a recursive procedure, initiating by recognizing all 2x2
+sets of matching pieces through the combination of four individual pieces.
+Subsequently, it extends this process to identify all 4x4 sets of matching pieces
+by aggregating four 2x2 pieces, and this pattern continues recursively.
 
 \subsection{Basic Components}
-To solve the puzzle two fundamental object are used
+To implement the algorithm two fundamental object are defined
 \begin{itemize}
@@
   \begin{itemize}
-    \item The comparing shore for level 0 objects is just the shore given by the comparator~\ref{document:comparator}.
+    \item The comparing shore for level 0 objects is just the shore given by the Comparator~\ref{document:comparator}.
     \item The comparing shore for level N+1 objects is the average between two comparisons made with objects of level N
@@
 
-In order for the created object to be considered valid all of the comparisons must have a shore higher
+In order for the created object to be considered valid all of the comparisons must have a shore greater
 than the constant MIN\_SHORE\_SINGLE\_SIDE. And the average of the four comparisons must be greater
@@
 
-In this section the solver that has been proposed by this paper will be tested.
-This test will serve two purposes:
-Understanding the performance and limitations of the proposed algorithm
-Been able to test the same algorithm with both digital, and real world jigsaw puzzles, to understand the differences between the two.
+In this section, the solver proposed by this paper will be put to the test.
+This evaluation serves two key purposes:
+
+\begin{itemize}
+  \item Gaining insight into the performance and limitations of the proposed algorithm.
+  \item Conducting tests using both digital and real-world jigsaw puzzles to discern the distinctions between the two contexts.
+\end{itemize}
 
@@
 The real world puzzles have been obtained with a printer’s scanner,
-and the digital puzzles have been obtained from \url{https://puzzle.telegnom.org/}.\newline
+and the digital puzzles have been obtained from \url{https://puzzle.telegnom.org/}.
+
 The constants MIN\_SHORE\_SINGLE\_SIDE and MIN\_SHORE\_PIECE\_GROUP mentioned in section
 \ref{document:combining_four_objects} were set at different values
-depending on the nature of the puzzle (real or digital).\newline
+depending on the nature of the puzzle (real or digital).
+
 The test has been performed on a ryzen 5 5600 CPU with 16 GB of RAM.
@@
 \subsection{Accuracy}
-It is important to note that the project does not have a way to evaluate the accuracy
-of the results automatically. But the accuracy for the two real world puzzles
-has been asserted manually. And both of them are 100\% correct.
+It is crucial to mention that the project currently lacks an automated
+method for evaluating the accuracy of results. However, the accuracy
+of the two real-world puzzles has been manually confirmed,
+with both achieving a 100\% correctness.
 
@@
 
-This paper has claimed from the start that real world puzzles were harder than digital ones.
-Some intuitive explanations were given to justify this claim,
-but a formal proof has never been given.
-This test finally proves the claim, by showing that the same algorithm can have vastly
-different time performances depending on the accuracy of the input data.
-
-It is fair to say that the performance of the algorithm are not amazing,
+This paper has asserted from the beginning that real-world puzzles
+pose greater challenges compared to their digital counterparts.
+While some intuitive explanations were provided to support this assertion,
+a proof has not yet been presented. This test ultimately substantiates 
+the claim, demonstrating that the performance of the same
+algorithm can vary significantly depending on the accuracy of the input data.
+
+It is fair to point out that the performances of the algorithm are not amazing,
 but they are good enough to achieve the objective of this paper \ref{document:objective}.
@@
 \section{The Labeling tool}
-When the program solves a puzzle it also exports some files that could be used in the future to train
-a machine-learning based comparator.
-This section is here to explain the data available and the format used.
+When the program runs, it also exports files that could be utilized
+in the future for training a machine-learning-based comparator.
+This section will list the available data and explain the format employed.
+
+\subsection{Basic notions}
 
 One piece is uniquely identified by his id piece\_id.
-The id is an integer that goes from 0 to Number of pieces - 1.
+The id is an integer that goes from 0 to \mbox{Number of pieces - 1}.
 Each piece has 4 sides that can be identified by the side side\_id,
@@
 Inside the folder results/pieces the program will generate one image
-for each one of the pieces of the puzzle. The pieces will be named \{piece\_id\}.jpeg.
+for each one of the pieces of the puzzle. The file will be named \{piece\_id\}.jpeg.
 An example can be seen in \ref{fig:result_pieces}
@@
 \section{Conclusions}
-In conclusion, this paper's objective can be considered achieved.
-It has been documented why real-world puzzles are harder than digital puzzles.
-It has also been shown that the same algorithm can have drastically worse
+In conclusion, this paper has successfully achieved its objectives.
+It has provided a comprehensive explanation of why real-world puzzles
+present greater challenges compared to their digital counterparts.
+Additionally, it has been shown that the same algorithm can have drastically worse
 performance when working with real-world puzzles compared to digital ones.
 
-A highly effective labeling tool has also been developed.
-It could be used in the future to create a machine learning-based comparator that could significantly
-improve the time needed to solve this problem by providing more accurate data.
-
-Even the solver that has been created can be considered a success.
-His time complexity is horrible if compared with current state-of-the-art digital puzzle solvers.
-But if compared with real world one the algorithm is probably one of the best, if not the best, available online.
+Furthermore, we have developed a highly effective labeling tool,
+which holds great promise for future applications in creating a
+machine learning-based comparator. Such a comparator has the potential
+to greatly facilitate puzzle-solving algorithms by providing more
+accurate data.
+
+Even the solver we have created can be considered a success.
+While its time complexity may be less favorable when compared to state-of-the-art
+digital puzzle solvers, it stands as a strong contender in the realm of
+real-world puzzle-solving algorithms. In fact, it may even be considered
+one of the best available online for tackling real-world puzzles.
 

### 2023-10-07 LaTeX_paper/paper.tex
fix typos and minor stuff

@@
 which ``calculates the percentage of pairs of image patches that are matched correctly''.
-This will be useful later\label{document:GCL}
+This will be useful later.\label{document:GCL}
 
@@
 \subsection{Setup}
-The test sample consist in 5 different puzzle:
+The test sample consist in 5 different puzzles:
 \begin{itemize}
@@
 While some intuitive explanations were provided to support this assertion,
-a proof has not yet been presented. This test ultimately substantiates 
+a proof hasn't been been presented until now. This test ultimately substantiates 
 the claim, demonstrating that the performance of the same
@@
 It is fair to point out that the performances of the algorithm are not amazing,
-but they are good enough to achieve the objective of this paper \ref{document:objective}.
+but they are good enough to achieve the objectives of this paper \ref{document:objective}.
 It is also worth remembering that the problem itself is extremely complex.

### 2023-10-08 cpp_lib/puzzle_solver_command.cpp
Add command line export program

@@ -1,0 +1,64 @@
+// this is the command used to have access to the puzzle solver's functionalities from the terminal
+#include <iostream>
+#include "PuzzleSolver.h"
+using namespace std;
+
+
+// CommandExample
+// PuzzleSolver "input_file_path" "output_file_path" "threshold_to_use" "puzzle_height" "puzzle_width" "number_of_cores"
+int main(int argc, char ** argv){
+
+    if(argc != 7){
+        cout << "Wrong number of arguments, expected 6 got " << argc-1 << endl;
+        cout << "The command must be in the following format:" << endl;
+        cout << "\t" << "PuzzleSolver \"input_file_path\" \"output_file_path\" \"threshold_to_use\" \"puzzle_height\" \"puzzle_width\" \"number_of_cores\"" << endl;
+        return -1;
+    }
+
+    char* input_path = argv[1];
+    char* output_path = argv[2];
+
+    int threshold = std::strtol(argv[3],NULL,10);
+    int height = std::strtol(argv[4],NULL,10);
+    int width = std::strtol(argv[5],NULL,10);
+    int cores = std::strtol(argv[6],NULL,10);
+
+    if (threshold < 0 || threshold > 255){
+        cout << "threshold must be between 0 and 255" << endl;
+        return -1;
+    }
+
+    if (height < 0){
+        cout << "height must be positive" << endl;
+        return -1;
+    }
+
+    if (width < 0){
+        cout << "width must be positive" << endl;
+        return -1;
+    }
+
+    if (cores < 0) {
+        cout << "number of cores must be positive" << endl;
+        return -1;
+    }
+
+    cout << "You have selected: " << endl;
+    cout << "\t input_path: " << input_path << endl;
+    cout << "\t output_path: " << output_path << endl;
+    cout << "\t threshold: " << threshold << endl;
+    cout << "\t height: " << height << endl;
+    cout << "\t width: " << width << endl;
+    cout << "\t number_of_cores: " << cores << endl;
+
+    PuzzleSolver ps(width, height, output_path,input_path,cores);
+
+    ps.set_threshold(threshold);
+
+    ps.split_image();
+    ps.process_corners();
+    ps.calculate_connections();
+    ps.solve_puzzle();
+
+    return 0;
+}

### 2023-11-19 cpp_lib/rust_solving/src/constants.rs
Fix bugs

@@ -1,5 +1,5 @@
 pub const MIN_SHORE_PIECE_ARRAY: f32 = 0.975;
-pub const MIN_SHORE_PIECE_GROUP: u8 = 150;
-pub const MIN_SHORE_SINGLE_SIDE: u8 = 125;
-//pub const MIN_SHORE_PIECE_GROUP: u8 = 125;
-//pub const MIN_SHORE_SINGLE_SIDE: u8 = 70;
+//pub const MIN_SHORE_PIECE_GROUP: u8 = 150;
+//pub const MIN_SHORE_SINGLE_SIDE: u8 = 125;
+pub const MIN_SHORE_PIECE_GROUP: u8 = 125;
+pub const MIN_SHORE_SINGLE_SIDE: u8 = 70;

### 2023-11-19 cpp_lib/rust_solving/src/finalize_piece_array.rs

@@ -12,6 +12,24 @@ use crate::piece_group_holder::PieceGroupHolder;
 /// puzzle with a wide aspect ration (greater that 2:1) are not supported by this function)
 pub fn finalize_piece_array<T: NextLevelOrPanic>(pgh: &PieceGroupHolder<T>, output_path: &str ,size_x: u64, size_y: u64) -> bool{
 
+
+    for i in 0..pgh.get_size(){
+        let piece = pgh.get(i,0);
+        let mut pa = PieceArray::new(T::SIDE_LEN,T::SIDE_LEN);
+        piece.fill_piece_array(&mut pa, 0,0,0);
+
+        // calculate the shore of the current piece
+        unsafe {
+            // call c++ dll
+            let mut paw = pa.get_piece_array_wrapper();
+            println!("{:?}",pa);
+            (*paw).generate_test_image(&format!("{}.png",i));
+            // deallocate memory
+            (*paw).destroy_piece_array_wrapper();
+        }
+
+    }
+
     let mut candidates = Mutex::new(Vec::<PieceArray>::new());
     println!("{}",T::SIDE_LEN);
     let shrink_size_x =  T::SIDE_LEN*2 - size_x;
@@ -22,19 +40,19 @@ pub fn finalize_piece_array<T: NextLevelOrPanic>(pgh: &PieceGroupHolder<T>, outp
 
             let top_left = pgh.get(top_left_id,top_left_orientation);
 
-            for top_right_id in (top_left_id+1)..pgh.get_size(){
+            for top_right_id in 0..pgh.get_size(){
                 'tr_orientation:
                 for top_right_orientation in 0..4{
 
                     let top_right = pgh.get(top_right_id,top_right_orientation);
 
-                    for bottom_right_id in (top_left_id+1)..pgh.get_size(){
+                    for bottom_right_id in 0..pgh.get_size(){
                         'br_orientation:
                         for bottom_right_orientation in 0..4{
 
                             let bottom_right = pgh.get(bottom_right_id,bottom_right_orientation);
 
-                            for bottom_left_id in (top_left_id+1)..pgh.get_size(){
+                            for bottom_left_id in 0..pgh.get_size(){
                                 'bl_orientation:
                                 for bottom_left_orientation in 0..4{
 
@@ -81,6 +99,8 @@ pub fn finalize_piece_array<T: NextLevelOrPanic>(pgh: &PieceGroupHolder<T>, outp
         function(top_left_id);
     });
 
[…]

### 2023-11-19 cpp_lib/rust_solving/src/piece_group/next_level_or_panic.rs

@@ -26,7 +26,7 @@ macro_rules! implement_next {
         impl NextLevelOrPanic for $i{
             fn next_or_panic(pgh: &PieceGroupHolder<PieceGroup<Self>>, output_path: &str, size_x: u64, size_y: u64) -> bool {
                 // when the limit is reached, call the finalize function
-                if PieceGroup::<Self>::SIDE_LEN*2 >= size_y || PieceGroup::<Self>::SIDE_LEN*2 >= size_x{
+                if PieceGroup::<Self>::SIDE_LEN*2 > size_y || PieceGroup::<Self>::SIDE_LEN*2 > size_x{
                     return finalize_piece_array::<PieceGroup<Self>>(&pgh,output_path,size_x,size_y);
                 }
                 return solve::<PieceGroup<Self>>(pgh, output_path, size_x, size_y);

### 2023-11-19 cpp_lib/rust_solving/src/solver.rs

@@ -61,7 +61,7 @@ pub fn solve<T: NextLevelOrPanic + Debug>(pgh: &PieceGroupHolder<T>, output_path
 
                         // now it is possible to check if the pieces match graphically, calling the c++ func
 
-                        if T::LEVEL < 2 && false{
+                        if T::LEVEL < 2{
                             // create the piece array with the appropriate size
                             let mut pa = PieceArray::new(
                                 PieceGroup::<T>::SIDE_LEN,

### 2023-11-19 cpp_lib/main_test.cpp
add dataset for 3x4

@@ -31,9 +31,9 @@ int main(){
 
     // function to call if you only want to compare the pieces:
     //*
-    calculate_all_connections(R"(C:\Users\lucas\CLionProjects\Puzzle_Solver\dataset\test_5x7_digital\divided)",
-                              R"(C:\Users\lucas\CLionProjects\Puzzle_Solver\dataset\test_5x7_digital\connections)",
-                              35,3, false);
+    calculate_all_connections(R"(C:\Users\lucas\CLionProjects\Puzzle_Solver\dataset\test_3x4_digital\divided)",
+                              R"(C:\Users\lucas\CLionProjects\Puzzle_Solver\dataset\test_3x4_digital\connections)",
+                              12,3, false);
     return 0;
     //*/
 

### 2023-11-19 cpp_lib/main_test.cpp
ok

@@ -31,9 +31,9 @@ int main(){
 
     // function to call if you only want to compare the pieces:
     //*
-    calculate_all_connections(R"(C:\Users\lucas\CLionProjects\Puzzle_Solver\dataset\test_3x4_digital\divided)",
-                              R"(C:\Users\lucas\CLionProjects\Puzzle_Solver\dataset\test_3x4_digital\connections)",
-                              12,3, false);
+    calculate_all_connections(R"(C:\Users\lucas\CLionProjects\Puzzle_Solver\dataset\test_8x12_digital\divided)",
+                              R"(C:\Users\lucas\CLionProjects\Puzzle_Solver\dataset\test_8x12_digital\connections)",
+                              96,3, false);
     return 0;
     //*/
 

### 2023-11-21 cpp_lib/rust_solving/src/finalize_piece_array.rs
Fix bug in finalize_piece_array

@@ -12,66 +12,68 @@ use crate::piece_group_holder::PieceGroupHolder;
 /// puzzle with a wide aspect ration (greater that 2:1) are not supported by this function)
 pub fn finalize_piece_array<T: NextLevelOrPanic>(pgh: &PieceGroupHolder<T>, output_path: &str ,size_x: u64, size_y: u64) -> bool{
 
-
-    for i in 0..pgh.get_size(){
-        let piece = pgh.get(i,0);
-        let mut pa = PieceArray::new(T::SIDE_LEN,T::SIDE_LEN);
-        piece.fill_piece_array(&mut pa, 0,0,0);
-
-        // calculate the shore of the current piece
-        unsafe {
-            // call c++ dll
-            let mut paw = pa.get_piece_array_wrapper();
-            println!("{:?}",pa);
-            (*paw).generate_test_image(&format!("{}.png",i));
-            // deallocate memory
-            (*paw).destroy_piece_array_wrapper();
-        }
-
-    }
-
     let mut candidates = Mutex::new(Vec::<PieceArray>::new());
     println!("{}",T::SIDE_LEN);
     let shrink_size_x =  T::SIDE_LEN*2 - size_x;
     let shrink_size_y = T::SIDE_LEN*2 - size_y;
 
+    let mut piece_arrays = Vec::new();
+
+    for id in 0..pgh.get_size(){
+        let mut pa_slice = [
+            PieceArray::new(T::SIDE_LEN,T::SIDE_LEN),
+            PieceArray::new(T::SIDE_LEN,T::SIDE_LEN),
+            PieceArray::new(T::SIDE_LEN,T::SIDE_LEN),
+            PieceArray::new(T::SIDE_LEN,T::SIDE_LEN)
+        ];
+        for orientation in 0..4 {
+            pgh.get(id,orientation).fill_piece_array(&mut pa_slice[orientation],0,0,0);
+        }
+        piece_arrays.push(pa_slice);
+    }
+    let piece_arrays = piece_arrays;
+
     let function= |top_left_id: usize|  {
         for top_left_orientation in 0..4{
 
             let top_left = pgh.get(top_left_id,top_left_orientation);
+            let top_left_pa = &piece_arrays[top_left_id][top_left_orientation];
 
             for top_right_id in 0..pgh.get_size(){
                 'tr_orientation:
                 for top_right_orientation in 0..4{
 
                     let top_right = pgh.get(top_right_id,top_right_orientation);
[…]

### 2023-11-21 cpp_lib/rust_solving/src/piece_array.rs

@@ -227,6 +227,17 @@ impl PieceArray {
     pub unsafe fn get_piece_array_wrapper(&mut self) -> *mut PieceArrayWrapper{
         create_piece_array_wrapper(self.dim_x,self.dim_y,self.pieces.as_mut_ptr())
     }
+
+    pub fn are_all_pieces_unique(&self) -> bool{
+        let mut set = HashSet::<u64>::new();
+        for piece in &self.pieces{
+            if set.contains(&piece.id){
+                return false;
+            }
+            set.insert(piece.id);
+        }
+        true
+    }
 }
 
 #[derive(Serialize, Deserialize, Debug, Copy, Clone)]

### 2023-11-21 cpp_lib/rust_solving/src/piece_group/intersection_comparable.rs

@@ -9,11 +9,11 @@ use super::Comparable;
 /// (given that the puzzle is not always a prefect square with a side that is a power of two)
 /// this trait is used to compare two pieces assuming that tey have an intersection with each other.
 pub trait IntersectionComparable: Comparable{
-    fn compare_to_with_intersection(&self, direction: Direction,other: &Self,intersection_width: u64) -> Shore;
+    fn compare_to_with_intersection(&self, direction: Direction,other: &Self,intersection_width: u64, self_piece_array: &PieceArray, other_piece_array: &PieceArray) -> Shore;
 }
 
 impl IntersectionComparable for SingePiece {
-    fn compare_to_with_intersection(&self, direction: Direction, other: &Self, intersection_width: u64) -> Shore {
+    fn compare_to_with_intersection(&self, direction: Direction, other: &Self, intersection_width: u64, _self_piece_array: &PieceArray, _other_piece_array: &PieceArray) -> Shore {
         if intersection_width == 0{
             self.compare_to(direction,other,0,0)
         }else if intersection_width == 1{
@@ -29,7 +29,7 @@ impl IntersectionComparable for SingePiece {
 }
 
 impl<T:Comparable + Clone + IsSubComponent + PieceArrayFiller + HasKnownLevel> IntersectionComparable for PieceGroup<'_,T> {
-    fn compare_to_with_intersection(&self, direction: Direction, other: &Self, intersection_width: u64) -> Shore {
+    fn compare_to_with_intersection(&self, direction: Direction, other: &Self, intersection_width: u64, self_piece_array: &PieceArray, other_piece_array: &PieceArray) -> Shore {
 
         let side_len = PieceGroup::<T>::SIDE_LEN;
 
@@ -39,12 +39,6 @@ impl<T:Comparable + Clone + IsSubComponent + PieceArrayFiller + HasKnownLevel> I
         if intersection_width > PieceGroup::<T>::SIDE_LEN{
             panic!("Comparing with an intersection that is longer that the piece itself is impossible")
         }
-
-        // create the piece array slice
-        let mut pa_self = PieceArray::new(side_len, side_len);
-        self.fill_piece_array(&mut pa_self, 0, 0, 0);
-        let mut pa_other = PieceArray::new( side_len, side_len);
-        other.fill_piece_array(&mut pa_other,0,0,0);
 
         fn get_slice(pa: &PieceArray, direction: Direction, width: u64) -> PieceArraySlice{
[…]

### 2023-11-21 LaTeX_paper/paper.tex
add result pictures
start fixing margins
Add more test cases

@@
 % to set the margin of the page
-\usepackage[a4paper, total={6.5in, 9in}]{geometry}
+\usepackage[a4paper, left=25mm,top=20mm,bottom=20mm,right=15mm]{geomet ry}
 
@@
 \subsection{Setup}
-The test sample consist in 5 different puzzles:
-\begin{itemize}
-  \item a 4x4 real world puzzle
-  \item a 8x8 real world puzzle
-  \item a 4x4 digital puzzle
-  \item a 8x8 digital puzzle
-  \item a 16x16 digital puzzle
-\end{itemize}
-The real world puzzles have been obtained with a printer’s scanner,
-and the digital puzzles have been obtained from \url{https://puzzle.telegnom.org/}.
+We have tested many different sizes of real, and digital puzzles.
+The real world puzzles have been obtained with a printer’s scanner, more data are available in REF SETUP.
+The digital puzzles have been obtained from \url{https://puzzle.telegnom.org/}.
+This web app can generate a puzzle from a dimension and a jitter value. The jitter is a parameter that controls
+how unique and distorted the puzzle images are, see \ref{fig:jiiter}.
+The default jitter used in the tests is 5\%.
+
+\begin{figure}[H]
+  \caption{Effect of jitter on jigsaw pieces}\label{fig:jiiter}
+  \centering
+  \includegraphics[height=0.3\textwidth]{pictures/jitter.png}
+\end{figure}
 
@@
 
-\subsection{Results}
-
+\subsection{Digital vs Real World Puzzles}
+
+In the table below we can see how the same algorithm
+can have vastly different performance depending on the kind of puzzle 
+it is working with.
 \begin{table}[H]
@@
   >{\columncolor[HTML]{D0E0E3}}c 
-  >{\columncolor[HTML]{E6B8AF}}c 
+  >{\columncolor[HTML]{F4CCCC}}c 
   >{\columncolor[HTML]{FCE5CD}}c }
@@
     \cellcolor[HTML]{F9CB9C}Real Puzzle \\
+  2x3   & 6   & 1   & 4    \\
+  3x4   & 12  & 3   & 14   \\
   4x4   & 16  & 4   & 59   \\
+  4x5   & 20  & 4   & 48   \\
+  5x8   & 40  & 20  & 627  \\
   8x8   & 64  & 30  & 2851 \\
+  8x12  & 96  & 660 & N/A  \\
   16x16 & 256 & 377 & N/A 
@@
 
+Looking at the data we can spot to anomalies:
+\begin{itemize}
+  \item The 4x5 real puzzle has a lower execution time than the 4x4 real puzzle. This is not a big
+  difference and can be attribute to run to run variation.
+  \item The 8x12 digital puzzle has a much higher execution time than the 16x16 digital puzzle.
+  This is also easily explainable, as puzzles whose side is not a power of two are in general
+  harder compared to those who fulfill this condition. As they require an extra step compared to
+  the simple algorithm shown in section REF.
+\end{itemize}
+
+\subsubitem{Effect of Jitter on Execution Time}
+
+Intuitively increasing the jitter would make the pieces harder to
+match with each other, and consequently making the puzzle easier to solve.
+And we can observe that this intuition is correct in the table below.
+
+\begin{table}[H]
+  \centering
+  \begin{tabular}{
+  >{\columncolor[HTML]{D0E0E3}}c 
+  >{\columncolor[HTML]{C9DAF8}}c }
+  \multicolumn{2}{c}{\cellcolor[HTML]{B6D7A8}Jitter effect on an 8x8 digital puzzle} \\
+  \cellcolor[HTML]{A2C4C9}Jitter   & \cellcolor[HTML]{A4C2F4}Execution time {[}s{]}  \\
+  4\%                              & 104                                             \\
+  5\%                              & 30                                              \\
+  6\%                              & 17                                              \\
+  8\%                              & 17                                              \\
+  10\%                             & 16                                             
+  \end{tabular}
+  \end{table}
+
+This shows how the execution time can be six times faster just by making
+each piece more unique. This notion can be applied to the real world puzzle,
+in fact the current version of the comparator REF is not using the color
+of the piece, only the shape. Adding the color to the available
+data could significantly increase the uniqueness of each piece,
+bringing down the execution time.
+
+\subsection{Run to Run Variation}
+
+Another feature of the algorithm that is worth testing is his consistency.
+The table below shows how the algorithm performs using a set of different
+same-sized puzzles as input.
+\begin{table}[H]
+  \centering
+  \begin{tabular}{
+  >{\columncolor[HTML]{FCE5CD}}c 
+  >{\columncolor[HTML]{FFF2CC}}c 
+  >{\columncolor[HTML]{EAD1DC}}c }
+  \multicolumn{3}{c}{\cellcolor[HTML]{EA9999}Run to run vairance on a 4x4 real puzzle}                                                             \\
+  \cellcolor[HTML]{F9CB9C}Execution time {[}s{]} & \cellcolor[HTML]{FFE599}Avrege                 & \cellcolor[HTML]{D5A6BD}Standard deviation     \\
+  64 & \cellcolor[HTML]{FFF2CC} & \cellcolor[HTML]{EAD1DC} \\
+  68 & \cellcolor[HTML]{FFF2CC} & \cellcolor[HTML]{EAD1DC} \\
+  43 & \cellcolor[HTML]{FFF2CC} & \cellcolor[HTML]{EAD1DC} \\
+  24 & \cellcolor[HTML]{FFF2CC} & \cellcolor[HTML]{EAD1DC} \\
+  29 & \cellcolor[HTML]{FFF2CC} & \cellcolor[HTML]{EAD1DC} \\
+  59 & \multirow{-6}{*}{\cellcolor[HTML]{FFF2CC}47.8} & \multirow{-6}{*}{\cellcolor[HTML]{EAD1DC}18.6}
+\end{tabular}
+\end{table}
+
 \subsection{Accuracy}
@@
 method for evaluating the accuracy of results. However, the accuracy
-of the two real-world puzzles has been manually confirmed,
+of two real-world puzzles (4x4 and 8x8) has been manually confirmed,
 with both achieving a 100\% correctness.
@@
 
+\begin{figure}[h]
+  \caption{example of a result render of a digital puzzle}\label{fig:result_digital}
+  \centering
+  \includegraphics[height=0.6\textwidth]{pictures/result_digital.png}
+\end{figure}
+
+\begin{figure}[h]
+  \caption{example of a result render of a real world puzzle}\label{fig:result_real}
+  \centering
+  \includegraphics[height=0.6\textwidth]{pictures/result_real.png}
+\end{figure}
+
 % referneces page

### 2023-11-22 LaTeX_paper/paper.tex
fix abstract
Add introduction

@@
 
-\section{Abstract}
+\begin{abstract}
 This paper examines the Jigsaw puzzle problem,
@@
 
+\end{abstract}
+
 \section{Introduction}
-\subsection{Classification}
+It is fair to say that we are all familiar with jigsaw puzzles.
+Understanding the ``rules'' necessary to solve a puzzle is
+extremely easy, but actually solving large-sized puzzles
+is not an easy task, neither for humans nor for computers.
+
+While the problem may appear to be a futile style exercise,
+it could have concrete applications in the future. For instance,
+it could be applied to the reconstruction of archaeological finds,
+such as a terracotta pot~\ref{fig:pot}.
+
+% figure of real jigsaw puzzle    
+\begin{figure}[h]
+  \caption{A practical application of a jigsaw puzzle}~\label{fig:pot}
+  \includegraphics[height=0.25\textwidth]{pictures/terracotta_pot.jpg}
+  \centering
+\end{figure}
+
+\subsection{context}
+\subsubsection{Classification}
 This paper will focus on Type 2 puzzles. A Type 2 puzzle is one where the position and orientation of each piece are unknown.

### 2023-11-22 LaTeX_paper/paper.tex
add context

@@
 
-\subsection{context}
+\subsection{Context}
+This section will provide some basic knowledge
+related to the jigsaw problem that will be useful
+  for the next sections.
 \subsubsection{Classification}
-This paper will focus on Type 2 puzzles. A Type 2 puzzle is one where the position and orientation of each piece are unknown.
-\subsection{Digital vs Real-World Jigsaw Puzzles}
+Puzzles are categorized in different types, for example 
+\begin{itemize}
+  \item Type 1 puzzles have the orientation of the pieces known, but the position unknown. 
+  \item Type 2 puzzles have both the orientation and the position of the pieces unknown.
+  \item Type 3 puzzles have the orientation of the pieces unknown, but the position is known.
+\end{itemize}
+Between these categories type 2 are the hardest, and will be the focus of this paper.
+
+\subsubsection{Digital vs Real-World Jigsaw Puzzles}
 
 There is  another important distinction between different types of puzzles.
-They can be divided into “digital”~\ref{fig:figure_digital_puzzle} and “real world”~\ref{fig:figure_real_puzzle} jigsaw puzzles.
-The difference between the two is quite self explanatory, and can be observed in the respective pictures.
+They can be divided into “digital”~\ref{fig:figure_digital_puzzle} and
+“real world”~\ref{fig:figure_real_puzzle} jigsaw puzzles.
+The difference between the two is quite self explanatory,
+and can be observed in the respective pictures.
 \label{document:DigitalVSReal}
@@
 For example, a piece's shape may be distorted by
-a low-quality cut, as seen in picture \ref{fig:figure_measurement_error}
+a low-quality cut, as seen in picture~\ref{fig:figure_measurement_error}
 
@@
 \end{figure}
-
-\section{Previous Literature}
-This section will analyze three different algorithms that have been
-proposed as solutions for type 2 puzzles.
-The objective is to understand the strengths and weaknesses of each one,
-in order to build up knowledge that will be useful for the next sections.
 
@@
 \end{indented_section}
+
+\section{Previous Literature}
+This section will analyze three different algorithms that have been
+proposed as solutions for type 2 puzzles.
+The objective is to understand the strengths and weaknesses of each one,
+in order to build up knowledge that will be useful for the next sections.
 

### 2023-11-22 LaTeX_paper/paper.tex
switch to cref

@@
 % to have better references
-\usepackage[noabbrev]{cleveref}
+\usepackage[nameinlink]{cleveref}
+
+%\usepackage[noabbrev]{cleveref}
 
@@
 \usepackage{multirow}
-
-% rule for reference to fugures
-\pretocmd{\thefigure}{F}{}{}
 
@@
 Several algorithms with efficient time complexity have been developed
-specifically for ``digital''~\ref{fig:figure_digital_puzzle} jigsaw puzzles. However, the counterpart:
+specifically for ``digital''~\cref{fig:figure_digital_puzzle} jigsaw puzzles. However, the counterpart:
 the ``real world' jigsaw puzzle, has received relatively little attention
@@
 
-The puzzle problem can be divided into two separate components: the ``Comparator''~\ref{document:comparator}
+The puzzle problem can be divided into two separate components: the ``Comparator''~\cref{document:comparator}
 whose objective is to determine whether two sides of two pieces fit together,
-and the ``Solver''~\ref{document:solver} whose objective is to use the information provided
+and the ``Solver''~\cref{document:solver} whose objective is to use the information provided
 by the comparator to find the best way to fit some pieces together.
@@
 it could be applied to the reconstruction of archaeological finds,
-such as a terracotta pot~\ref{fig:pot}.
+such as a terracotta pot~\cref{fig:pot}.
 
@@
 There is  another important distinction between different types of puzzles.
-They can be divided into “digital”~\ref{fig:figure_digital_puzzle} and
-“real world”~\ref{fig:figure_real_puzzle} jigsaw puzzles.
+They can be divided into “digital”~\cref{fig:figure_digital_puzzle} and
+“real world”~\cref{fig:figure_real_puzzle} jigsaw puzzles.
 The difference between the two is quite self explanatory,
@@
 For example, a piece's shape may be distorted by
-a low-quality cut, as seen in picture~\ref{fig:figure_measurement_error}
+a low-quality cut, as seen in picture~\cref{fig:figure_measurement_error}
 
@@
 
-All the algorithms that will be analyzed are composed of 3 sub algorithms:
+A puzzle solver program can be divided into 3 sub algorithms,
+The Splitter, The Comparator and The Solver.
+This generalization can be applied not only to our solution,
+but also to all the algorithms analyzed in the related
+work section of this paper~\cref{document:related_work}.
 
@@
     \subsubsection{The Solver:} This component utilizes the information provided by the
-    Comparator~\ref{document:comparator}, and attempts to find a solution
+    Comparator~\cref{document:comparator}, and attempts to find a solution
     (i.e.\ a position and an orientation for each piece)
@@
 \end{indented_section}
-
-\section{Previous Literature}
-This section will analyze three different algorithms that have been
-proposed as solutions for type 2 puzzles.
-The objective is to understand the strengths and weaknesses of each one,
-in order to build up knowledge that will be useful for the next sections.
-
-\subsection{Solving Jigsaw Puzzles By The Graph Connection Laplacian~\cite{GCL}}
-This algorithm falls within the ``binary comparison'' category~\ref{document:comparator}.
-And can be used to understand the strength and weaknesses
-of this approach.\newline
-The primary advantage of this approach lies in its speed;
-the utilization of binary comparison permits specific optimizations,
-particularly leveraging graph theory techniques.\newline
-The algorithm exhibits a time complexity of approximately \(O(N^2)\),
-a value consistent with the theoretical minimum for
-jigsaw puzzle solving, as outlined in the study
-``No easy puzzles: Hardness results for jigsaw puzzles~\cite{ON2Claim}''.\newline
-However, a potential drawback may arise in terms of accuracy.
-This stems from the fact that, with only two states
-(matching or not matching),
-certain details may be lost when compared to a non-binary comparison. 
-To quantify accuracy the paper used the ``neighbors compariso'' metric,
-which ``calculates the percentage of pairs of image patches that are matched correctly''.
-This will be useful later.\label{document:GCL}
-
-\subsection{A Genetic Algorithm-Based Solver for Very Large Jigsaw Puzzles~\cite{GA}}
-This paper employs genetic algorithms to address the
-jigsaw puzzle problem, yielding promising results.\newline
-The algorithm seems to have a \(O(N^2)\) time complexity,
-with execution time slightly lower than the previous example
-(However, it remains uncertain which one is faster, as the papers did not specify
-the particular hardware configuration used).\newline
-The paper adopts the same evaluation method for accuracy as the previous example,
-namely neighbor comparison, facilitating direct comparison between the two approaches.
-This algorithm falls under the category of “Non binary comparison”~\ref{document:comparator}
-a distinction that theoretically grants it an advantage due to the increased granularity
-of input data.
-Unfortunately this advantage does not compensate for the worst precision
-of the algorithm itself, and the accuracy results are equivalent,
-if not slightly worse than the previous algorithm.\newline
-It is important to keep in mind that for the very nature of genetic algorithms,
-it might be possible that the accuracy would have been better if they had allowed
-the algorithm to run for more generations.\label{document:GA}
-
-\subsection{Computer Vision Powers Automatic Jigsaw Puzzle Solver~\cite{Abto}}
-Solutions~\ref{document:GCL} and~\ref{document:GA} can be considered ``state-of-the-art''
-for digital jigsaw puzzles.
-However, as already introduced in section ~\ref{document:DigitalVSReal},
-translating these solutions to the real world can be challenging.\newline
-This article represents one of the most comprehensive and well-documented
-implementations for real-world puzzles. However,
-it's important to note that referring to this approach as a ``solution''
-may be misleading, as it primarily identifies the top eight matching
-pieces for a specific point and subsequently relies on user input to make
-the final placement decision.
-This aspect renders the algorithm non-autonomous..\newline
-Even disregarding this significant detail,
-conducting an analysis of this solution has proven to be challenging,
-as the article leans more towards a publicity stunt than an academic paper.
-In fact, the code is not open source, and informations regarding the time needed
-to solve the puzzle are absent. The article only showcases a single puzzle solved,
-with dimensions of 9\(\times\)6.\newline
-Despite these limitations, this article still stands as one of the best examples of a solution
-for real-world puzzles.
 
@@
 This objective is motivated by the fact that the biggest challenge for real world puzzles is creating a
-reliable comparator~\ref{document:comparator}, that could provide accurate information even with noisy 
+reliable comparator~\cref{document:comparator}, that could provide accurate information even with noisy 
 input images, that are obtained from real-world measure.
@@
 This section will encompass the input data utilized,
-as well as the Splitter~\ref{document:splitter}
-and Comparator~\ref{document:comparator} algorithms.
+as well as the Splitter~\cref{document:splitter}
+and Comparator~\cref{document:comparator} algorithms.
 
@@
 A resolution of 1200 pixels per inch (ppi) has been employed to ensure a sharp and precise
-depiction of the pieces, as seen in image~\ref{fig:figure_measurement_error}.
+depiction of the pieces, as seen in image~\cref{fig:figure_measurement_error}.
 The puzzle has been scanned backward, using a black background.
@@
 
-As introduced in section~\ref{document:splitter},  the initial stage in puzzle solving involves
+As introduced in~\cref{document:splitter},  the initial stage in puzzle solving involves
 splitting an image composed of many pieces into individual ones.
@@
 
-The next step following the general structure~\ref{document:splitter}
+The next step following the general structure~\cref{document:splitter}
 is to split a piece into
@@
   To remove the holes from the piece, the program employs a three-step process. Initially it
-  computes the convex hull of the piece~\ref{fig:s_s_ch}.
+  computes the convex hull of the piece~\cref{fig:s_s_ch}.
   Subsequently it calculates the difference between the convex hull and the original image,
-  resulting in an ``image with filler areas''~\ref{fig:fig:s_s_og_minus_ch}.
+  resulting in an ``image with filler areas''~\cref{fig:fig:s_s_og_minus_ch}.
   It can be noted that these filler areas have distinct shapes,
@@
   they originated from a hole. This results in an image where the holes
-  have been filled~\ref{fig:s_s_no_holes}
+  have been filled~\cref{fig:s_s_no_holes}
 
@@
   In order to remove the knobs from the piece, the image without holes
-  undergoes an erosion~\ref{fig:s_s_erosion} followed by a dilation~\ref{fig:s_s_dilatation}.
+  undergoes an erosion~\cref{fig:s_s_erosion} followed by a dilation~\cref{fig:s_s_dilatation}.
   This process results in an image that resembles the original, but without any knobs.
-  Subsequently, the program identifies the pixels that are white in the image without holes~\ref{fig:s_s_no_holes},
-  but not in the eroded and dilated version~\ref{fig:s_s_dilatation}.
-  This leads to the formation of a set of blobs ~\ref{fig:s_s_no_holes_minus_expansion}.
+  Subsequently, the program identifies the pixels that are white in the image without holes~\cref{fig:s_s_no_holes},
+  but not in the eroded and dilated version~\cref{fig:s_s_dilatation}.
+  This leads to the formation of a set of blobs ~\cref{fig:s_s_no_holes_minus_expansion}.
   It is important to note that the shape of a blob can vary significantly depending on whether it originated
@@
   Following this, the program proceeds to eliminate from the hole-free
-  image~\ref{fig:s_s_no_holes} all pixels that are in close proximity to a blob generated by a knob.
-  This operation yields an image that is both devoid of knobs and holes~\ref{fig:s_s_no_knobs}.
+  image~\cref{fig:s_s_no_holes} all pixels that are in close proximity to a blob generated by a knob.
+  This operation yields an image that is both devoid of knobs and holes~\cref{fig:s_s_no_knobs}.
 
@@
   utilizes the coordinates of its corners
-  as the first approximation~\ref{fig:s_s_min_enc_rec}.\newline
+  as the first approximation~\cref{fig:s_s_min_enc_rec}.\newline
   For the second approximation, the program selects,
@@
   distance of the second approximation, and finds the minimum
-  enclosing triangle of sed pixels~\ref{fig:s_s_min_enc_triangle}.\newline
+  enclosing triangle of sed pixels~\cref{fig:s_s_min_enc_triangle}.\newline
   The corner of the triangle that is nearest to the second
@@
   for the corner of the puzzle piece.
-  The position of the four corners can be seen in image~\ref{fig:s_s_corners_found}.
+  The position of the four corners can be seen in image~\cref{fig:s_s_corners_found}.
 
@@
   it can straightforwardly derive each of the four sides.
-  An example of a single side can be seen in image .~\ref{fig:s_s_a_piece_side}.
+  An example of a single side can be seen in image .~\cref{fig:s_s_a_piece_side}.
 \end{itemize}
@@
     \includegraphics[width=\linewidth]{pictures/remove_holes_filler_areas.png}
-    \caption{Difference:~\ref{fig:s_s_ch} \textminus~\ref{fig:s_s_og}.}
+    \caption{Difference:~\cref{fig:s_s_ch} \textminus~\cref{fig:s_s_og}.}
     \label{fig:fig:s_s_og_minus_ch}
@@
     \includegraphics[width=\linewidth]{pictures/piece_with_no_hole.png}
-    \caption{Piece~\ref{fig:s_s_og} with holes removed.}
+    \caption{Piece~\cref{fig:s_s_og} with holes removed.}
     \label{fig:s_s_no_holes}
@@
     \includegraphics[width=\linewidth]{pictures/remove_knobs_erosion.png}
-    \caption{Mask~\ref{fig:s_s_no_holes} eroded.}
+    \caption{Mask~\cref{fig:s_s_no_holes} eroded.}
     \label{fig:s_s_erosion}
@@
     \includegraphics[width=\linewidth]{pictures/remove_knobs_expansion.png}
-    \caption{Mask~\ref{fig:s_s_erosion} dilated.}
+    \caption{Mask~\cref{fig:s_s_erosion} dilated.}
     \label{fig:s_s_dilatation}
@@
     \includegraphics[width=\linewidth]{pictures/remove_knobs_knob_pixels.png}
-    \caption{Difference:~\ref{fig:s_s_no_holes} \textminus~\ref{fig:s_s_erosion}.}
+    \caption{Difference:~\cref{fig:s_s_no_holes} \textminus~\cref{fig:s_s_erosion}.}
     \label{fig:s_s_no_holes_minus_expansion}
@@
     \includegraphics[width=\linewidth]{pictures/piece_with_no_knobs.png}
-    \caption{Piece~\ref{fig:s_s_no_holes} with knobs removed.}
+    \caption{Piece~\cref{fig:s_s_no_holes} with knobs removed.}
     \label{fig:s_s_no_knobs}
@@
     \includegraphics[width=\linewidth]{pictures/find_corners_min_enclosing_rectangle.png}
-    \caption{Min enclosing rectangle of~\ref{fig:s_s_no_knobs}.}
+    \caption{Min enclosing rectangle of~\cref{fig:s_s_no_knobs}.}
     \label{fig:s_s_min_enc_rec}
@@
     \includegraphics[width=\linewidth]{pictures/find_corners_min_enclosing_triangle.png}
-    \caption{Min enclosing triangle of the bottom right corner of~\ref{fig:s_s_no_knobs}.}
+    \caption{Min enclosing triangle of the bottom right corner of~\cref{fig:s_s_no_knobs}.}
     \label{fig:s_s_min_enc_triangle}
@@
     \includegraphics[width=\linewidth]{pictures/corners_found.png}
-    \caption{The corners of the piece~\ref{fig:s_s_og}.}
+    \caption{The corners of the piece~\cref{fig:s_s_og}.}
     \label{fig:s_s_corners_found}
@@
     \includegraphics[width=\linewidth]{pictures/piece_side.png}
-    \caption{One of the sides of the piece~\ref{fig:s_s_og}.}
+    \caption{One of the sides of the piece~\cref{fig:s_s_og}.}
     \label{fig:s_s_a_piece_side}
@@
 test the existing algorithms with real-world puzzle. For this test,
-the fist algorithm~\ref{document:GCL} is selected due to the comprehensive
+the fist algorithm~\cref{document:GCL} is selected due to the comprehensive
 details provided in the paper. Notably, it contains information
@@
 
-The conducted tests reveal that the Comparator developed in this paper~\ref{document:my_comparator}
-and the ``Graph Connection Laplacian'' solution ~\ref{document:my_comparator} are not compatible with each other.
+The conducted tests reveal that the Comparator developed in this paper~\cref{document:my_comparator}
+and the ``Graph Connection Laplacian'' solution ~\cref{document:my_comparator} are not compatible with each other.
 A formal proof supporting this assertion is presented subsequently.
@@
 
-The comparison algorithm deceived in section~\ref{document:my_comparator} outputs a compatibility
+The comparison algorithm deceived in section~\cref{document:my_comparator} outputs a compatibility
 shore that goes from 0 to 1.\newline
-But the algorithm~\ref{document:GCL} takes as input a binary value.
+But the algorithm~\cref{document:GCL} takes as input a binary value.
 Which means that it is necessary to apply a threshold to the input
@@
 
-Now, let's consider Algorithm \ref{document:GCL} tasked with solving a 500-piece puzzle
-using our Comparator \ref{document:my_comparator}.
+Now, let's consider Algorithm \cref{document:GCL} tasked with solving a 500-piece puzzle
+using our Comparator \cref{document:my_comparator}.
 A threshold of 0.425 is chosen;
@@
 \begin{figure}[h]
-  \caption{Neighbors comparison vs Corruption rate of algorithm \ref{document:GCL}. Image taken from pater \cite{GCL} page 34.}\label{fig:GCL_Corruption_Rate}
+  \caption{Neighbors comparison vs Corruption rate of algorithm \cref{document:GCL}. Image taken from pater \cite{GCL} page 34.}\label{fig:GCL_Corruption_Rate}
   \centering
@@
 
-In Figure \ref{fig:GCL_Corruption_Rate}, it can be observed that at a corruption rate of 0.057,
+In Figure \cref{fig:GCL_Corruption_Rate}, it can be observed that at a corruption rate of 0.057,
 a neighbors comparison metric of roughly 80\% can be anticipated.
@@
 To lower the corruption rate is necessary to decrease the threshold, but this would increase the limit match\%.
-This means that, regardless of the threshold chosen, our comparison algorithm \ref{document:my_comparator}
-can not work with a state of the art solver \ref{document:GCL}.
+This means that, regardless of the threshold chosen, our comparison algorithm \cref{document:my_comparator}
+can not work with a state of the art solver \cref{document:GCL}.
 
@@
 \end{itemize}
-Both SinglePiece and PieceGroup have an ``orientation'' attribute that goes from 0 to 3~\ref{fig:orientation}.
+Both SinglePiece and PieceGroup have an ``orientation'' attribute that goes from 0 to 3~\cref{fig:orientation}.
 \begin{figure}[H]
@@
   \begin{itemize}
-    \item The comparing shore for level 0 objects is just the shore given by the Comparator~\ref{document:comparator}.
+    \item The comparing shore for level 0 objects is just the shore given by the Comparator~\cref{document:comparator}.
     \item The comparing shore for level N+1 objects is the average between two comparisons made with objects of level N
@@
 \begin{itemize}
-  \item The right side of the object in the top left position is compared with the left side of the object in the top right position~\ref{fig:merge_pieces}(1).
-  \item The bottom side of the objection the top right position is compared with the top side of the object in the bottom right position~\ref{fig:merge_pieces}(2).
-  \item The left side of the objection the bottom right position is compared with the right side of the object in the bottom left position~\ref{fig:merge_pieces}(3).
-  \item The top side of the objection the bottom left position is compared with the bottom side of the object in the top left position~\ref{fig:merge_pieces}(4).
+  \item The right side of the object in the top left position is compared with the left side of the object in the top right position~\cref{fig:merge_pieces}(1).
+  \item The bottom side of the objection the top right position is compared with the top side of the object in the bottom right position~\cref{fig:merge_pieces}(2).
+  \item The left side of the objection the bottom right position is compared with the right side of the object in the bottom left position~\cref{fig:merge_pieces}(3).
+  \item The top side of the objection the bottom left position is compared with the bottom side of the object in the top left position~\cref{fig:merge_pieces}(4).
 \end{itemize}
@@
 This web app can generate a puzzle from a dimension and a jitter value. The jitter is a parameter that controls
-how unique and distorted the puzzle images are, see \ref{fig:jiiter}.
+how unique and distorted the puzzle images are, see \cref{fig:jiiter}.
 The default jitter used in the tests is 5\%.
@@
 The constants MIN\_SHORE\_SINGLE\_SIDE and MIN\_SHORE\_PIECE\_GROUP mentioned in section
-\ref{document:combining_four_objects} were set at different values
+\cref{document:combining_four_objects} were set at different values
 depending on the nature of the puzzle (real or digital).
@@
 The time measured in the test does not include the execution time of the Comparator
-\ref{document:my_comparator}, but only the one of the Solver~\ref{document:my_solver}.
+\cref{document:my_comparator}, but only the one of the Solver~\cref{document:my_solver}.
 
@@
 It is fair to point out that the performances of the algorithm are not amazing,
-but they are good enough to achieve the objectives of this paper \ref{document:objective}.
+but they are good enough to achieve the objectives of this paper \cref{document:objective}.
 It is also worth remembering that the problem itself is extremely complex.
-Using the formula introduced in section \ref{document:proof_definitions} we can calculate that a 64 piece puzzle,
+Using the formula introduced in section \cref{document:proof_definitions} we can calculate that a 64 piece puzzle,
 like the one that has been solved before, has approximately \(4 \cdot 10^{127}\) possible combinations.
@@
 for each one of the pieces of the puzzle. The file will be named \{piece\_id\}.jpeg.
-An example can be seen in \ref{fig:result_pieces}
+An example can be seen in \cref{fig:result_pieces}
 
@@
 for each side of each piece. The images will be named \{piece\_id\}\_\{side\_id\}.jpeg.
-An example can be seen in \ref{fig:result_sides}
+An example can be seen in \cref{fig:result_sides}
 
@@
 
+\section{Related work}\label{document:related_work}
+This section will analyze three different algorithms that have been
+proposed as solutions for type 2 puzzles.
+The objective is to understand the strengths and weaknesses of each one,
+in order to build up knowledge that will be useful for the next sections.
+
+\subsection{Solving Jigsaw Puzzles By The Graph Connection Laplacian~\cite{GCL}}
+This algorithm falls within the ``binary comparison'' category~\cref{document:comparator}.
+And can be used to understand the strength and weaknesses
+of this approach.\newline
+The primary advantage of this approach lies in its speed;
+the utilization of binary comparison permits specific optimizations,
+particularly leveraging graph theory techniques.\newline
+The algorithm exhibits a time complexity of approximately \(O(N^2)\),
+a value consistent with the theoretical minimum for
+jigsaw puzzle solving, as outlined in the study
+``No easy puzzles: Hardness results for jigsaw puzzles~\cite{ON2Claim}''.\newline
+However, a potential drawback may arise in terms of accuracy.
+This stems from the fact that, with only two states
+(matching or not matching),
+certain details may be lost when compared to a non-binary comparison. 
+To quantify accuracy the paper used the ``neighbors compariso'' metric,
+which ``calculates the percentage of pairs of image patches that are matched correctly''.
+This will be useful later.\label{document:GCL}
+
+\subsection{A Genetic Algorithm-Based Solver for Very Large Jigsaw Puzzles~\cite{GA}}
+This paper employs genetic algorithms to address the
+jigsaw puzzle problem, yielding promising results.\newline
+The algorithm seems to have a \(O(N^2)\) time complexity,
+with execution time slightly lower than the previous example
+(However, it remains uncertain which one is faster, as the papers did not specify
+the particular hardware configuration used).\newline
+The paper adopts the same evaluation method for accuracy as the previous example,
+namely neighbor comparison, facilitating direct comparison between the two approaches.
+This algorithm falls under the category of “Non binary comparison”~\cref{document:comparator}
+a distinction that theoretically grants it an advantage due to the increased granularity
+of input data.
+Unfortunately this advantage does not compensate for the worst precision
+of the algorithm itself, and the accuracy results are equivalent,
+if not slightly worse than the previous algorithm.\newline
+It is important to keep in mind that for the very nature of genetic algorithms,
+it might be possible that the accuracy would have been better if they had allowed
+the algorithm to run for more generations.\label{document:GA}
+
+\subsection{Computer Vision Powers Automatic Jigsaw Puzzle Solver~\cite{Abto}}
+Solutions~\cref{document:GCL} and~\cref{document:GA} can be considered ``state-of-the-art''
+for digital jigsaw puzzles.
+However, as already introduced in section ~\cref{document:DigitalVSReal},
+translating these solutions to the real world can be challenging.\newline
+This article represents one of the most comprehensive and well-documented
+implementations for real-world puzzles. However,
+it's important to note that referring to this approach as a ``solution''
+may be misleading, as it primarily identifies the top eight matching
+pieces for a specific point and subsequently relies on user input to make
+the final placement decision.
+This aspect renders the algorithm non-autonomous..\newline
+Even disregarding this significant detail,
+conducting an analysis of this solution has proven to be challenging,
+as the article leans more towards a publicity stunt than an academic paper.
+In fact, the code is not open source, and informations regarding the time needed
+to solve the puzzle are absent. The article only showcases a single puzzle solved,
+with dimensions of 9\(\times\)6.\newline
+Despite these limitations, this article still stands as one of the best examples of a solution
+for real-world puzzles.
+
 \section{Conclusions}

### 2023-11-23 LaTeX_paper/paper.tex
format sections

@@
 specifically for ``digital''~\cref{fig:figure_digital_puzzle} jigsaw puzzles. However, the counterpart:
-the ``real world' jigsaw puzzle, has received relatively little attention
+the ``real world'' jigsaw puzzle~\cref{fig:figure_real_puzzle}, has received relatively little attention
 in the literature. While some small-scale projects have addressed this issue,
@@
 
-\section{The Objective Of This Paper}\label{document:objective}
+\subsection{The Objective Of This Paper}\label{document:objective}
 After a review of the existing literature on this problem, some conclusions could be drawn:

### 2023-11-23 LaTeX_paper/paper.tex
Move dataset definition to introduction

@@
 \subsection{The Objective Of This Paper}\label{document:objective}
-After a review of the existing literature on this problem, some conclusions could be drawn:
-The ``digital'' jigsaw puzzle dilemma has been extensively addressed and is already
-well-optimized. Conversely, the ``real-world'' counterpart has largely been
-overlooked within the academic community.
-
-The first objective for this paper is to fill this void, and been the first formal paper
-to analyze the real-world jigsaw puzzle problem.
-
-The second objective is to use the forthcoming research to create a labeling tool.
-
-This objective is motivated by the fact that the biggest challenge for real world puzzles is creating a
-reliable comparator~\cref{document:comparator}, that could provide accurate information even with noisy 
-input images, that are obtained from real-world measure.
-
-It is easy to see how a machine learning based comparator would probably be the best solution, 
-but this poses problems, in fact having to manually scan and label thousands of individual puzzle
-pieces to train the model would take ages.
-Instead an automatic tool would allow to scan a small $4\times4$ puzzle in one shot,
-solve it, and return the labeled data in just minutes.
-
-\section{The Setup}
-
-To fulfill the objectives of this paper,
-it is essential to have the necessary data for analysis.
-This section will encompass the input data utilized,
-as well as the Splitter~\cref{document:splitter}
-and Comparator~\cref{document:comparator} algorithms.
-
-\subsection{The Puzzle To Solve}
-
+
+This paper is not the first to tackle the jigsaw puzzle problem in computer science,
+in fact there have been several more that are mentioned in the related work section (\cref{document:related_work}).
+
+All the papers we read focused on digital jigsaw puzzles exclusively,
+and we couldn't find any paper that mentioned real-world puzzles.
+It should be mentioned that we did find some open source project that solved the
+real-world puzzle problem, but they didn’t document the creation process nor the
+findings given that they weren't trying to write a paper.
+
+This paper’s objective is to focus on both digital and real-world jigsaw puzzles,
+and document why the real-world version is harder, and try to quantify by how much.
+In other to achieve this objective we want to answer these two questions:
+\begin{itemize}
+  \item \textbf{What is the difference in execution time between
+                digital and real-world puzzles?}
+
+  To answer this question we decided to build a puzzle solver from the ground up,
+  and measure his performance across a set of digital, and real-world puzzles.
+  Our focus when developing this component wasn't to build a state of the art algorithm,
+  as there has already been extensive research put into that;
+  We simply needed something that could work with both digital and real-world puzzles.
+
+  \item \textbf{What are the challenges to use the current state of the art algorithms developed for digital
+                puzzles in the real-world, and how can we overcome them?}
+
+	Answering this question is a bit trickier, as an algorithm is divided into Comparator~\cref{document:comparator}
+  and Solver~\cref{document:solver}. Due to the intrinsic difference of digital and real-world jigsaw puzzles
+  reusing the Comparator is impossible, but there is the possibility to reuse the Sover,
+  assuming we could build a Comparator for real-world puzzles that is in the same realm
+  of accuracy achieved by Comparators for digital puzzles.
+  So another way to write this question is: ``Can we build a Comparator for real-world
+  puzzles that is accurate enough to work with current state-of-the-art  digital
+  puzzle Solvers?''
+
+	To answer this question we will measure the accuracy of the comparator we developed
+  to answer the previous question and observe what would happen if that accuracy is
+  applied to a digital puzzle solver. We will then propose a solution to improve
+  the accuracy of real-world Comparators.
+
+\end{itemize}
+
+\subsection{The Dataset}
+The last step of the introduction is defining our
+testing dataset. We need both digital and real world
+puzzles to solve. The dataset used, as well as
+the code, can be seen in the public GitHub
+repository:~\url{https://github.com/lucaSartore/PuzzleSolver}.
+
+\subsubsection{The Real-World Puzzle}
 The first step involves selecting a real-world
@@
 by using a different scanner.
+
+\subsubsection{The Digital Puzzle}
+
+\section{Our Implementation Of A Puzzle Solver}
 

### 2023-11-25 LaTeX_paper/paper.tex
unify the content section

@@
 \usepackage{color}
+
+% To have a paragraph look like a subsubsubsection
+\usepackage{titlesec}
+
+\setcounter{secnumdepth}{4}
+
+\titleformat{\paragraph}
+{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
+\titlespacing*{\paragraph}
+{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}
 
@@
 repository:~\url{https://github.com/lucaSartore/PuzzleSolver}.
-
+\label{document:dataset}
 \subsubsection{The Real-World Puzzle}
 The first step involves selecting a real-world
-puzzle for solving. It has been decided to utilize a
+puzzle to solve. It has been decided to utilize a
 classic 1000-piece puzzle measuring 66cm x 50cm.
@@
 A resolution of 1200 pixels per inch (ppi) has been employed to ensure a sharp and precise
-depiction of the pieces, as seen in image~\cref{fig:figure_measurement_error}.
+depiction of the pieces, as seen in~\cref{fig:figure_measurement_error}.
 The puzzle has been scanned backward, using a black background.
@@
 \subsubsection{The Digital Puzzle}
+The digital puzzles have been obtained from \url{https://puzzle.telegnom.org/}.
+This web app can generate a puzzle from a dimension and a jitter value. The jitter is a parameter that controls
+how unique and distorted the puzzle images are, see \cref{fig:jiiter}.
+The default jitter used in the tests is 5\%.
 
@@
 
-\subsection{Splitting The Pieces}
+\subsection{Our Splitter}
+
+\subsubsection{Splitting The Pieces}
 
@@
 
-\subsection{Splitting The Sides}
+\subsubsection{Splitting The Sides}
 
@@
 
-\subsection{Comparing The Sides}\label{document:my_comparator}
+\subsection{Our Comparator}\label{document:my_comparator}
 The last step in the setup, is to compare the sides that have been
@@
 \clearpage
+
+\subsection{Our Solver}\label{document:my_solver}
+The Solver that has been developed is not the primary focus of this
+paper and cannot be considered state-of-the-art when compared
+to the current best digital puzzle solvers. However, it may be
+considered as such when compared to existing ``real-world'' puzzle solvers.
+
+\subsubsection{Overview}
+The algorithm itself is relatively straightforward.
+It operates as a recursive procedure, initiating by recognizing all 2x2
+sets of matching pieces through the combination of four individual pieces.
+Subsequently, it extends this process to identify all 4x4 sets of matching pieces
+by aggregating four 2x2 pieces, and this pattern continues recursively.
+
+\subsubsection{Basic Components}
+To implement the algorithm two fundamental object are defined
+\begin{itemize}
+  \item SinglePiece: which contains information about a single puzzle piece.
+  \item PieceGroup\(<\)T\(>\) where T can be either a PieceGroup or a SinglePiece\newline
+  This element encompasses four elements of type T, each with its own position (top right, top left, bottom left, bottom right).
+\end{itemize}
+Both SinglePiece and PieceGroup have an ``orientation'' attribute that goes from 0 to 3~\cref{fig:orientation}.
+\begin{figure}[H]
+  \caption{orientation attribute of an object}\label{fig:orientation}
+  \centering
+  \includegraphics[height=0.3\textwidth]{pictures/orientation.png}
+\end{figure}
+
+\paragraph{The Levels}
+
+These objects are assigned levels:
+\begin{itemize}
+\item SinglePiece is at level 0, representing a 1x1 ``solution'' to a puzzle.
+\item PieceGroup\(<\)SinglePiece\(>\) is at level 1, representing a 2x2 solution to a puzzle.
+\item PieceGroup\(<\)PieceGroup\(<\)SinglePiece\(>>\) is at level 2, representing a 4x4 solution to a puzzle, and so forth.
+\end{itemize}
+
+\paragraph{The Behaviors}
+
+These basic objects also have the following shared behaviors:
+\begin{itemize}
+  \item 4 objects of level N can be combined to build an object of level N+1.
+  \item One object of level N has 4 sides, each of which can be compared with a side of an element of level N. This results in a compatibility shore.
+  \begin{itemize}
+    \item The comparing shore for level 0 objects is just the shore given by the Comparator~\cref{document:comparator}.
+    \item The comparing shore for level N+1 objects is the average between two comparisons made with objects of level N
+  \end{itemize}
+\end{itemize}
+
+\paragraph{Combining four objects}\label{document:combining_four_objects}
+
+When combining four objects into one, some comparisons are executed to ensure that the resulting piece is a valid  combination.
+\begin{itemize}
+  \item The right side of the object in the top left position is compared with the left side of the object in the top right position~\cref{fig:merge_pieces}(1).
+  \item The bottom side of the objection the top right position is compared with the top side of the object in the bottom right position~\cref{fig:merge_pieces}(2).
+  \item The left side of the objection the bottom right position is compared with the right side of the object in the bottom left position~\cref{fig:merge_pieces}(3).
+  \item The top side of the objection the bottom left position is compared with the bottom side of the object in the top left position~\cref{fig:merge_pieces}(4).
+\end{itemize}
+
+\begin{figure}[H]
+  \caption{Example of a combination of four objects in to one}\label{fig:merge_pieces}
+  \centering
+  \includegraphics[height=0.3\textwidth]{pictures/merge_pieces.png}
+\end{figure}
+
+In order for the created object to be considered valid all of the comparisons must have a shore greater
+than the constant MIN\_SHORE\_SINGLE\_SIDE. And the average of the four comparisons must be greater
+than the constant MIN\_SHORE\_PIECE\_GROUP.
+
+The process also checks that all individual pieces inside a newly
+created object are different (because obviously is impossible to reuse the same piece twice to solve a puzzle)
+\subsubsection{The Algorithm}
+
+As mentioned earlier, the algorithm is implemented with a recursive function.
+The function is generic, and can take as input objects of any level.
+
+A Function of level N takes as input a list of objects of level N,
+and creates all possible objects with level N+1.
+Then it uses the newly created objects to generate a recursive call on a version
+of itself with level N+1.
+This process is repeated until the desired size is reached.
+
+\begin{minipage}{\textwidth}
+\begin{lstlisting}
+  # This function returns a list of object that match with `piece_to_match'
+  # along the direction `direction'.
+  # It also filters the data to return only pieces with an index greater than `index_filter'
+  # This function is executed in constant time, since it relies on some pre-processing of the data
+  def get_matches(piece_to_match, direction, index_filter):
+      ...
+
+  def solve<T>(pieces: List<T>):
+
+      number_of_pieces = pieces.length()
+
+      found_pieces = List::<PieceGroup<T>>::new()
+
+      # this function compare all pieces with the others, and build some data structures
+      # that are used from the function `get_matches'
+	   # the time complexity is o(N^2)
+      do_pre_processing(pieces)
+
+      # test all possible combinations for the top left piece
+      for top_left_index in 0..number_of_pieces:
+	       for top_left_orientation in 0..4:
+
+          # get the top left piece
+          top_left = get_piece(top_left_index, top_left_orientation)
+
+          # test all possible combinations of top_right, bottom_right and bottom_left
+          for top_right in get_matches(top_left, RIGHT, top_left_index):
+	           for bottom_right in get_matches(top_right, DOWN , top_left_index):
+                  for bottom_left in get_matches(bottom_right, LEFT, top_left_index):
+
+                      # try to create the new piece group
+                      new_element = PieceGroup::new(top_left, top_right, bottom_right,bottom_left)
+
+                      if new_element.is_valid():
+                          # if the 4 pieces can fit together the newly created piece
+                          # is added to the list of found pieces
+                          found_pieces.add_element(new_element)
+                      else:
+                          # otherwise the program check what the case of the 
+                          # invalid creation is, and generate a continue
+                          # on the respective loop, to speed up the operations
+                          continue_failure_cause_loop()
+
+      # at the end a recursive call is generated 
+      return solve::<PieceGroup<T>>(found_pieces)
+
+\end{lstlisting}
+\end{minipage}
+The procedure begins by testing all possible pieces and orientations as the top\_right piece.
+Then continues by finding all the other 3 pieces in an efficient way thanks to get\_matches.
+When the program has an hypothesis on the 4 pieces that can build a new piece it tries to create it.\newline
+The creation process does some checks, and if everything is successful it adds the piece to the list of found pieces.
+If the creation is not successful it figures out which piece has caused the failure, and moves to the next iteration of the respective loop.\newline
+When all combinations have been found, the function makes a recursive call and the process is repeated.\newline
+The process ensures that the piece in the top\_left is always the one with the lower index.
+This is done to avoid building the same piece 4 times with 4 different orientations.\newline
+One advantage of this algorithm is that the outer edge for loop can be easily parallelized to achieve better performances.
 
@@
 
-\section{The Solver}\label{document:my_solver}
-The Solver that has been developed is not the primary focus of this
-paper and cannot be considered state-of-the-art when compared
-to the current best digital puzzle solvers. However, it may be
-considered as such when compared to existing ``real-world'' puzzle solvers.
-
-\subsection{Overview}
-The algorithm itself is relatively straightforward.
-It operates as a recursive procedure, initiating by recognizing all 2x2
-sets of matching pieces through the combination of four individual pieces.
-Subsequently, it extends this process to identify all 4x4 sets of matching pieces
-by aggregating four 2x2 pieces, and this pattern continues recursively.
-
-\subsection{Basic Components}
-To implement the algorithm two fundamental object are defined
-\begin{itemize}
-  \item SinglePiece: which contains information about a single puzzle piece.
-  \item PieceGroup\(<\)T\(>\) where T can be either a PieceGroup or a SinglePiece\newline
-  This element encompasses four elements of type T, each with its own position (top right, top left, bottom left, bottom right).
-\end{itemize}
-Both SinglePiece and PieceGroup have an ``orientation'' attribute that goes from 0 to 3~\cref{fig:orientation}.
-\begin{figure}[H]
-  \caption{orientation attribute of an object}\label{fig:orientation}
-  \centering
-  \includegraphics[height=0.3\textwidth]{pictures/orientation.png}
-\end{figure}
-
-\subsubsection{The Levels}
-
-These objects are assigned levels:
-\begin{itemize}
-\item SinglePiece is at level 0, representing a 1x1 ``solution'' to a puzzle.
-\item PieceGroup\(<\)SinglePiece\(>\) is at level 1, representing a 2x2 solution to a puzzle.
-\item PieceGroup\(<\)PieceGroup\(<\)SinglePiece\(>>\) is at level 2, representing a 4x4 solution to a puzzle, and so forth.
-\end{itemize}
-
-\subsubsection{The Behaviors}
-
-These basic objects also have the following shared behaviors:
-\begin{itemize}
-  \item 4 objects of level N can be combined to build an object of level N+1.
-  \item One object of level N has 4 sides, each of which can be compared with a side of an element of level N. This results in a compatibility shore.
-  \begin{itemize}
-    \item The comparing shore for level 0 objects is just the shore given by the Comparator~\cref{document:comparator}.
-    \item The comparing shore for level N+1 objects is the average between two comparisons made with objects of level N
-  \end{itemize}
-\end{itemize}
-
-\subsubsection{Combining four objects}\label{document:combining_four_objects}
-
-When combining four objects into one, some comparisons are executed to ensure that the resulting piece is a valid  combination.
-\begin{itemize}
-  \item The right side of the object in the top left position is compared with the left side of the object in the top right position~\cref{fig:merge_pieces}(1).
-  \item The bottom side of the objection the top right position is compared with the top side of the object in the bottom right position~\cref{fig:merge_pieces}(2).
-  \item The left side of the objection the bottom right position is compared with the right side of the object in the bottom left position~\cref{fig:merge_pieces}(3).
-  \item The top side of the objection the bottom left position is compared with the bottom side of the object in the top left position~\cref{fig:merge_pieces}(4).
-\end{itemize}
-
-\begin{figure}[H]
-  \caption{Example of a combination of four objects in to one}\label{fig:merge_pieces}
-  \centering
-  \includegraphics[height=0.3\textwidth]{pictures/merge_pieces.png}
-\end{figure}
-
-In order for the created object to be considered valid all of the comparisons must have a shore greater
-than the constant MIN\_SHORE\_SINGLE\_SIDE. And the average of the four comparisons must be greater
-than the constant MIN\_SHORE\_PIECE\_GROUP.
-
-The process also checks that all individual pieces inside a newly
-created object are different (because obviously is impossible to reuse the same piece twice to solve a puzzle)
-\subsection{The Algorithm}
-
-As mentioned earlier, the algorithm is implemented with a recursive function.
-The function is generic, and can take as input objects of any level.
-
-A Function of level N takes as input a list of objects of level N,
-and creates all possible objects with level N+1.
-Then it uses the newly created objects to generate a recursive call on a version
-of itself with level N+1.
-This process is repeated until the desired size is reached.
-
-\begin{minipage}{\textwidth}
-\begin{lstlisting}
-  # This function returns a list of object that match with `piece_to_match'
-  # along the direction `direction'.
-  # It also filters the data to return only pieces with an index greater than `index_filter'
-  # This function is executed in constant time, since it relies on some pre-processing of the data
-  def get_matches(piece_to_match, direction, index_filter):
-      ...
-
-  def solve<T>(pieces: List<T>):
-
-      number_of_pieces = pieces.length()
-
-      found_pieces = List::<PieceGroup<T>>::new()
-
-      # this function compare all pieces with the others, and build some data structures
-      # that are used from the function `get_matches'
-	   # the time complexity is o(N^2)
-      do_pre_processing(pieces)
-
-      # test all possible combinations for the top left piece
-      for top_left_index in 0..number_of_pieces:
-	       for top_left_orientation in 0..4:
-
-          # get the top left piece
-          top_left = get_piece(top_left_index, top_left_orientation)
-
-          # test all possible combinations of top_right, bottom_right and bottom_left
-          for top_right in get_matches(top_left, RIGHT, top_left_index):
-	           for bottom_right in get_matches(top_right, DOWN , top_left_index):
-                  for bottom_left in get_matches(bottom_right, LEFT, top_left_index):
-
-                      # try to create the new piece group
-                      new_element = PieceGroup::new(top_left, top_right, bottom_right,bottom_left)
-
-                      if new_element.is_valid():
-                          # if the 4 pieces can fit together the newly created piece
-                          # is added to the list of found pieces
-                          found_pieces.add_element(new_element)
-                      else:
-                          # otherwise the program check what the case of the 
-                          # invalid creation is, and generate a continue
-                          # on the respective loop, to speed up the operations
-                          continue_failure_cause_loop()
-
-      # at the end a recursive call is generated 
-      return solve::<PieceGroup<T>>(found_pieces)
-
-\end{lstlisting}
-\end{minipage}
-The procedure begins by testing all possible pieces and orientations as the top\_right piece.
-Then continues by finding all the other 3 pieces in an efficient way thanks to get\_matches.
-When the program has an hypothesis on the 4 pieces that can build a new piece it tries to create it.\newline
-The creation process does some checks, and if everything is successful it adds the piece to the list of found pieces.
-If the creation is not successful it figures out which piece has caused the failure, and moves to the next iteration of the respective loop.\newline
-When all combinations have been found, the function makes a recursive call and the process is repeated.\newline
-The process ensures that the piece in the top\_left is always the one with the lower index.
-This is done to avoid building the same piece 4 times with 4 different orientations.\newline
-One advantage of this algorithm is that the outer edge for loop can be easily parallelized to achieve better performances.
-
 \section{Testing Results}
@@
 \subsection{Setup}
-We have tested many different sizes of real, and digital puzzles.
-The real world puzzles have been obtained with a printer’s scanner, more data are available in REF SETUP.
-The digital puzzles have been obtained from \url{https://puzzle.telegnom.org/}.
-This web app can generate a puzzle from a dimension and a jitter value. The jitter is a parameter that controls
-how unique and distorted the puzzle images are, see \cref{fig:jiiter}.
-The default jitter used in the tests is 5\%.
+See~\cref{document:dataset} for a detailed
+description of the setup.
 

### 2023-11-25 LaTeX_paper/paper.tex
improve  "out implementation" section

@@
 is to split a piece into
-his 4 sides, this could be done with the following steps:
+his 4 sides, this can be done with the following steps:
 
@@
     \includegraphics[width=\linewidth]{pictures/remove_knobs_knob_pixels.png}
-    \caption{Difference:~\cref{fig:s_s_no_holes} \textminus~\cref{fig:s_s_erosion}.}
+    \caption{Difference:~\cref{fig:s_s_no_holes} \textminus~\cref{fig:s_s_dilatation}.}
     \label{fig:s_s_no_holes_minus_expansion}
@@
 \subsection{Our Comparator}\label{document:my_comparator}
-The last step in the setup, is to compare the sides that have been
-generated before.
-In order to generate a compatibility shore,
-the program compute the following steps:
+The next step is to compare the sides that have been
+generated before, in order to generate
+a compatibility shore.
+To achieve this, the program employs
+the following steps:
 

### 2023-11-25 LaTeX_paper/paper.tex
refactor related work section

@@
 One advantage of this algorithm is that the outer edge for loop can be easily parallelized to achieve better performances.
+
+\section{Related work}\label{document:related_work}
+Now that we have developed our own solution, it would be
+interesting to see how it compares against the current
+state-of-the-art algorithms for both digital and real-world
+jigsaw puzzles. This section gives a brief introduction to 3
+state-of-the-art algorithms, so that they can be compared with
+our solution in the conclusions.
+
+\subsection{Solving Jigsaw Puzzles By The Graph Connection Laplacian~\cite{GCL}}
+This algorithm falls within the ``binary comparison'' category (\cref{document:comparator}).
+And can be used to understand the strength and weaknesses
+of this approach.\newline
+The primary advantage of this approach lies in its speed;
+the utilization of binary comparison permits specific optimizations,
+particularly leveraging graph theory techniques.\newline
+The algorithm exhibits a time complexity of approximately \(O(N^2)\),
+a value consistent with the theoretical minimum for
+jigsaw puzzle solving, as outlined in the study
+``No easy puzzles: Hardness results for jigsaw puzzles~\cite{ON2Claim}''.\newline
+However, a potential drawback may arise in terms of accuracy.
+This stems from the fact that, with only two states
+(matching or not matching),
+certain details may be lost when compared to a non-binary comparison. 
+To quantify accuracy the paper used the ``neighbors compariso'' metric,
+which ``calculates the percentage of pairs of image patches that are matched correctly''.
+This will be useful later.\label{document:GCL}
+
+\subsection{A Genetic Algorithm-Based Solver for Very Large Jigsaw Puzzles~\cite{GA}}
+This paper employs genetic algorithms to address the
+jigsaw puzzle problem, yielding promising results.\newline
+The algorithm seems to have a \(O(N^2)\) time complexity,
+with execution time slightly lower than the previous example
+(However, it remains uncertain which one is faster, as the papers did not specify
+the particular hardware configuration used).\newline
+The paper adopts the same evaluation method for accuracy as the previous example,
+namely neighbor comparison, facilitating direct comparison between the two approaches.
+This algorithm falls under the category of “Non binary comparison”~\cref{document:comparator}
+a distinction that theoretically grants it an advantage due to the increased granularity
+of input data.
+Unfortunately this advantage does not compensate for the worst precision
+of the algorithm itself, and the accuracy results are equivalent,
+if not slightly worse than the previous algorithm.\newline
+It is important to keep in mind that for the very nature of genetic algorithms,
+it might be possible that the accuracy would have been better if they had allowed
+the algorithm to run for more generations.\label{document:GA}
+
+\subsection{Computer Vision Powers Automatic Jigsaw Puzzle Solver~\cite{Abto}}
+Solutions~\cref{document:GCL} and~\cref{document:GA} can be considered ``state-of-the-art''
+for digital jigsaw puzzles.
+However, as already introduced in section ~\cref{document:DigitalVSReal},
+translating these solutions to the real world can be challenging.\newline
+This article represents one of the most comprehensive and well-documented
+implementations for real-world puzzles. However,
+it's important to note that referring to this approach as a ``solution''
+may be misleading, as it primarily identifies the top eight matching
+pieces for a specific point and subsequently relies on user input to make
+the final placement decision.
+This aspect renders the algorithm non-autonomous..\newline
+Even disregarding this significant detail,
+conducting an analysis of this solution has proven to be challenging,
+as the article leans more towards a publicity stunt than an academic paper.
+In fact, the code is not open source, and informations regarding the time needed
+to solve the puzzle are absent. The article only showcases a single puzzle solved,
+with dimensions of 9\(\times\)6.\newline
+Despite these limitations, this article still stands as one of the best examples of a solution
+for real-world puzzles.
 
@@
 
-\section{Related work}\label{document:related_work}
-This section will analyze three different algorithms that have been
-proposed as solutions for type 2 puzzles.
-The objective is to understand the strengths and weaknesses of each one,
-in order to build up knowledge that will be useful for the next sections.
-
-\subsection{Solving Jigsaw Puzzles By The Graph Connection Laplacian~\cite{GCL}}
-This algorithm falls within the ``binary comparison'' category~\cref{document:comparator}.
-And can be used to understand the strength and weaknesses
-of this approach.\newline
-The primary advantage of this approach lies in its speed;
-the utilization of binary comparison permits specific optimizations,
-particularly leveraging graph theory techniques.\newline
-The algorithm exhibits a time complexity of approximately \(O(N^2)\),
-a value consistent with the theoretical minimum for
-jigsaw puzzle solving, as outlined in the study
-``No easy puzzles: Hardness results for jigsaw puzzles~\cite{ON2Claim}''.\newline
-However, a potential drawback may arise in terms of accuracy.
-This stems from the fact that, with only two states
-(matching or not matching),
-certain details may be lost when compared to a non-binary comparison. 
-To quantify accuracy the paper used the ``neighbors compariso'' metric,
-which ``calculates the percentage of pairs of image patches that are matched correctly''.
-This will be useful later.\label{document:GCL}
-
-\subsection{A Genetic Algorithm-Based Solver for Very Large Jigsaw Puzzles~\cite{GA}}
-This paper employs genetic algorithms to address the
-jigsaw puzzle problem, yielding promising results.\newline
-The algorithm seems to have a \(O(N^2)\) time complexity,
-with execution time slightly lower than the previous example
-(However, it remains uncertain which one is faster, as the papers did not specify
-the particular hardware configuration used).\newline
-The paper adopts the same evaluation method for accuracy as the previous example,
-namely neighbor comparison, facilitating direct comparison between the two approaches.
-This algorithm falls under the category of “Non binary comparison”~\cref{document:comparator}
-a distinction that theoretically grants it an advantage due to the increased granularity
-of input data.
-Unfortunately this advantage does not compensate for the worst precision
-of the algorithm itself, and the accuracy results are equivalent,
-if not slightly worse than the previous algorithm.\newline
-It is important to keep in mind that for the very nature of genetic algorithms,
-it might be possible that the accuracy would have been better if they had allowed
-the algorithm to run for more generations.\label{document:GA}
-
-\subsection{Computer Vision Powers Automatic Jigsaw Puzzle Solver~\cite{Abto}}
-Solutions~\cref{document:GCL} and~\cref{document:GA} can be considered ``state-of-the-art''
-for digital jigsaw puzzles.
-However, as already introduced in section ~\cref{document:DigitalVSReal},
-translating these solutions to the real world can be challenging.\newline
-This article represents one of the most comprehensive and well-documented
-implementations for real-world puzzles. However,
-it's important to note that referring to this approach as a ``solution''
-may be misleading, as it primarily identifies the top eight matching
-pieces for a specific point and subsequently relies on user input to make
-the final placement decision.
-This aspect renders the algorithm non-autonomous..\newline
-Even disregarding this significant detail,
-conducting an analysis of this solution has proven to be challenging,
-as the article leans more towards a publicity stunt than an academic paper.
-In fact, the code is not open source, and informations regarding the time needed
-to solve the puzzle are absent. The article only showcases a single puzzle solved,
-with dimensions of 9\(\times\)6.\newline
-Despite these limitations, this article still stands as one of the best examples of a solution
-for real-world puzzles.
-
 \section{Conclusions}

### 2023-11-25 LaTeX_paper/paper.tex
lay out structure of conclusions

@@
 for real-world puzzles.
+
+\section{Conclusions}
+This section will conclude the paper,
+by answering the two questions posed in \cref{document:objective}:
+
+\begin{itemize}
+  \item What is the difference in execution time between
+                digital and real-world puzzles?
+  \item What are the challenges to use the current state of the art algorithms developed for digital
+                puzzles in the real-world, and how can we overcome them?
+\end{itemize}
+And by making some consideration about possible future works related to this problem.
+
+\subsection{Difference In Execution Time}
+
+\subsection{Applying Already Existing Algorithms To The Real World}
+
+\subsection{Future Works}
+
+\subsubsection{Machine Learning Based Comparator}
+
+\subsubsection{Labeling tool}
+
+\subsection{Conclusion}
 
@@
 
-\section{Conclusions}
+\section{ConclusionsOld}
 In conclusion, this paper has successfully achieved its objectives.

### 2023-11-25 LaTeX_paper/paper.tex
fromat testing results

@@
 
-\paragraph{The Levels}
+\subsubsection{The Levels}
 
@@
 
-\paragraph{The Behaviors}
+\subsubsection{The Behaviors}
 
@@
 
-\paragraph{Combining four objects}\label{document:combining_four_objects}
-
-When combining four objects into one, some comparisons are executed to ensure that the resulting piece is a valid  combination.
+\subsubsection{Combining four objects}\label{document:combining_four_objects}
+When combining four objects into one, some comparisons are executed to
+ensure that the resulting piece is a valid  combination.
+
 \begin{itemize}
@@
 \subsection{Difference In Execution Time}
+
+This section measures the execution time of many puzzles,
+and plots the results. The puzzles that has been used for
+this test has been described in ~\cref{document:dataset}.
+
+The constants MIN\_SHORE\_SINGLE\_SIDE and MIN\_SHORE\_PIECE\_GROUP mentioned in
+section~\cref{document:combining_four_objects} were set at different values
+depending on the nature of the puzzle (real or digital).
+
+The test has been performed on a ryzen 5 5600 CPU with 16 GB of RAM.
+The time measured in the test does not include the execution time of the Comparator
+\cref{document:my_comparator}, but only the one of the Solver~\cref{document:my_solver}.
+
+\subsection{Digital vs Real World Puzzles}
+
+In the table below we can see how the same algorithm
+can have vastly different performance depending on the kind of puzzle 
+it is working with.
+\begin{table}[H]
+  \centering
+  \begin{tabular}{
+  >{\columncolor[HTML]{D9EAD3}}c 
+  >{\columncolor[HTML]{D0E0E3}}c 
+  >{\columncolor[HTML]{F4CCCC}}c 
+  >{\columncolor[HTML]{FCE5CD}}c }
+  \cellcolor[HTML]{B6D7A8} &
+    \cellcolor[HTML]{A2C4C9} &
+    \multicolumn{2}{c}{\cellcolor[HTML]{EA9999}Execution time {[}s{]}} \\
+  \multirow{-2}{*}{\cellcolor[HTML]{B6D7A8}Size} &
+    \multirow{-2}{*}{\cellcolor[HTML]{A2C4C9}Pieces} &
+    \cellcolor[HTML]{DD7E6B}Digital puzzle &
+    \cellcolor[HTML]{F9CB9C}Real Puzzle \\
+  2x3   & 6   & 1   & 4    \\
+  3x4   & 12  & 3   & 14   \\
+  4x4   & 16  & 4   & 59   \\
+  4x5   & 20  & 4   & 48   \\
+  5x8   & 40  & 20  & 627  \\
+  8x8   & 64  & 30  & 2851 \\
+  8x12  & 96  & 660 & N/A  \\
+  16x16 & 256 & 377 & N/A 
+  \end{tabular}
+\end{table}
+
+Looking at the data we can spot to anomalies:
+\begin{itemize}
+  \item The 4x5 real puzzle has a lower execution time than the 4x4 real puzzle. This is not a big
+  difference and can be attribute to run to run variation.
+  \item The 8x12 digital puzzle has a much higher execution time than the 16x16 digital puzzle.
+  This is also easily explainable, as puzzles whose side is not a power of two are in general
+  harder compared to those who fulfill this condition. As they require an extra step compared to
+  the simple algorithm shown in section REF.
+\end{itemize}
+
+\subsubsection{Effect of Jitter on Execution Time}
+
+As mention in \cref{document:dataset} the digital puzzle have an attribute called jitter.
+Intuitively increasing the jitter would make the pieces harder to
+match with each other, and consequently making the puzzle easier to solve.
+And we can observe that this intuition is correct in the table below.
+
+\begin{figure}[h]
+  \caption{Effect of jitter on jigsaw pieces}\label{fig:jiiter}
+  \centering
+  \includegraphics[height=0.3\textwidth]{pictures/jitter.png}
+\end{figure}
+
+\begin{table}[H]
+  \centering
+  \begin{tabular}{
+  >{\columncolor[HTML]{D0E0E3}}c 
+  >{\columncolor[HTML]{C9DAF8}}c }
+  \multicolumn{2}{c}{\cellcolor[HTML]{B6D7A8}Jitter effect on an 8x8 digital puzzle} \\
+  \cellcolor[HTML]{A2C4C9}Jitter   & \cellcolor[HTML]{A4C2F4}Execution time {[}s{]}  \\
+  4\%                              & 104                                             \\
+  5\%                              & 30                                              \\
+  6\%                              & 17                                              \\
+  8\%                              & 17                                              \\
+  10\%                             & 16                                             
+  \end{tabular}
+  \end{table}
+
+This shows how the execution time can be six times faster just by making
+each piece more unique.
+\subsection{Run to Run Variation}
+
+Another feature of the algorithm that is worth testing is his consistency.
+The table below shows how the algorithm performs using a set of different
+same-sized puzzles as input.
+\begin{table}[H]
+  \centering
+  \begin{tabular}{
+  >{\columncolor[HTML]{FCE5CD}}c 
+  >{\columncolor[HTML]{FFF2CC}}c 
+  >{\columncolor[HTML]{EAD1DC}}c }
+  \multicolumn{3}{c}{\cellcolor[HTML]{EA9999}Run to run vairance on a 4x4 real puzzle}                                                             \\
+  \cellcolor[HTML]{F9CB9C}Execution time {[}s{]} & \cellcolor[HTML]{FFE599}Avrege                 & \cellcolor[HTML]{D5A6BD}Standard deviation     \\
+  64 & \cellcolor[HTML]{FFF2CC} & \cellcolor[HTML]{EAD1DC} \\
+  68 & \cellcolor[HTML]{FFF2CC} & \cellcolor[HTML]{EAD1DC} \\
+  43 & \cellcolor[HTML]{FFF2CC} & \cellcolor[HTML]{EAD1DC} \\
+  24 & \cellcolor[HTML]{FFF2CC} & \cellcolor[HTML]{EAD1DC} \\
+  29 & \cellcolor[HTML]{FFF2CC} & \cellcolor[HTML]{EAD1DC} \\
+  59 & \multirow{-6}{*}{\cellcolor[HTML]{FFF2CC}47.8} & \multirow{-6}{*}{\cellcolor[HTML]{EAD1DC}18.6}
+\end{tabular}
+\end{table}
+
+\subsection{Accuracy}
+It is crucial to mention that the project currently lacks an automated
+method for evaluating the accuracy of results. However, the accuracy
+of two real-world puzzles (4x4 and 8x8) and one digital puzzle (16x16) has been manually confirmed,
+with them achieving a 100\% correctness.
+
+\subsection{Answering The Question}
+
+This paper has asserted from the beginning that real-world puzzles
+pose greater challenges compared to their digital counterparts.
+While some intuitive explanations were provided to support this assertion,
+a proof hasn't been been presented until now. This test ultimately substantiates 
+the claim, demonstrating that the performance of the same
+algorithm can vary significantly depending on the accuracy of the input data.
 
@@
 
-\section{Testing Results}
-
-In this section, the solver proposed by this paper will be put to the test.
-This evaluation serves two key purposes:
-
-\begin{itemize}
-  \item Gaining insight into the performance and limitations of the proposed algorithm.
-  \item Conducting tests using both digital and real-world jigsaw puzzles to discern the distinctions between the two contexts.
-\end{itemize}
-
-\subsection{Setup}
-See~\cref{document:dataset} for a detailed
-description of the setup.
-
-\begin{figure}[H]
-  \caption{Effect of jitter on jigsaw pieces}\label{fig:jiiter}
-  \centering
-  \includegraphics[height=0.3\textwidth]{pictures/jitter.png}
-\end{figure}
-
-The constants MIN\_SHORE\_SINGLE\_SIDE and MIN\_SHORE\_PIECE\_GROUP mentioned in section
-\cref{document:combining_four_objects} were set at different values
-depending on the nature of the puzzle (real or digital).
-
-The test has been performed on a ryzen 5 5600 CPU with 16 GB of RAM.
-The time measured in the test does not include the execution time of the Comparator
-\cref{document:my_comparator}, but only the one of the Solver~\cref{document:my_solver}.
-
-\subsection{Digital vs Real World Puzzles}
-
-In the table below we can see how the same algorithm
-can have vastly different performance depending on the kind of puzzle 
-it is working with.
-\begin{table}[H]
-  \centering
-  \begin{tabular}{
-  >{\columncolor[HTML]{D9EAD3}}c 
-  >{\columncolor[HTML]{D0E0E3}}c 
-  >{\columncolor[HTML]{F4CCCC}}c 
-  >{\columncolor[HTML]{FCE5CD}}c }
-  \cellcolor[HTML]{B6D7A8} &
-    \cellcolor[HTML]{A2C4C9} &
-    \multicolumn{2}{c}{\cellcolor[HTML]{EA9999}Execution time {[}s{]}} \\
-  \multirow{-2}{*}{\cellcolor[HTML]{B6D7A8}Size} &
-    \multirow{-2}{*}{\cellcolor[HTML]{A2C4C9}Pieces} &
-    \cellcolor[HTML]{DD7E6B}Digital puzzle &
-    \cellcolor[HTML]{F9CB9C}Real Puzzle \\
-  2x3   & 6   & 1   & 4    \\
-  3x4   & 12  & 3   & 14   \\
-  4x4   & 16  & 4   & 59   \\
-  4x5   & 20  & 4   & 48   \\
-  5x8   & 40  & 20  & 627  \\
-  8x8   & 64  & 30  & 2851 \\
-  8x12  & 96  & 660 & N/A  \\
-  16x16 & 256 & 377 & N/A 
-  \end{tabular}
-\end{table}
-
-Looking at the data we can spot to anomalies:
-\begin{itemize}
-  \item The 4x5 real puzzle has a lower execution time than the 4x4 real puzzle. This is not a big
-  difference and can be attribute to run to run variation.
-  \item The 8x12 digital puzzle has a much higher execution time than the 16x16 digital puzzle.
-  This is also easily explainable, as puzzles whose side is not a power of two are in general
-  harder compared to those who fulfill this condition. As they require an extra step compared to
-  the simple algorithm shown in section REF.
-\end{itemize}
-
-\subsubitem{Effect of Jitter on Execution Time}
-
-Intuitively increasing the jitter would make the pieces harder to
-match with each other, and consequently making the puzzle easier to solve.
-And we can observe that this intuition is correct in the table below.
-
-\begin{table}[H]
-  \centering
-  \begin{tabular}{
-  >{\columncolor[HTML]{D0E0E3}}c 
-  >{\columncolor[HTML]{C9DAF8}}c }
-  \multicolumn{2}{c}{\cellcolor[HTML]{B6D7A8}Jitter effect on an 8x8 digital puzzle} \\
-  \cellcolor[HTML]{A2C4C9}Jitter   & \cellcolor[HTML]{A4C2F4}Execution time {[}s{]}  \\
-  4\%                              & 104                                             \\
-  5\%                              & 30                                              \\
-  6\%                              & 17                                              \\
-  8\%                              & 17                                              \\
-  10\%                             & 16                                             
-  \end{tabular}
-  \end{table}
-
-This shows how the execution time can be six times faster just by making
-each piece more unique. This notion can be applied to the real world puzzle,
-in fact the current version of the comparator REF is not using the color
-of the piece, only the shape. Adding the color to the available
-data could significantly increase the uniqueness of each piece,
-bringing down the execution time.
-
-\subsection{Run to Run Variation}
-
-Another feature of the algorithm that is worth testing is his consistency.
-The table below shows how the algorithm performs using a set of different
-same-sized puzzles as input.
-\begin{table}[H]
-  \centering
-  \begin{tabular}{
-  >{\columncolor[HTML]{FCE5CD}}c 
-  >{\columncolor[HTML]{FFF2CC}}c 
-  >{\columncolor[HTML]{EAD1DC}}c }
-  \multicolumn{3}{c}{\cellcolor[HTML]{EA9999}Run to run vairance on a 4x4 real puzzle}                                                             \\
-  \cellcolor[HTML]{F9CB9C}Execution time {[}s{]} & \cellcolor[HTML]{FFE599}Avrege                 & \cellcolor[HTML]{D5A6BD}Standard deviation     \\
-  64 & \cellcolor[HTML]{FFF2CC} & \cellcolor[HTML]{EAD1DC} \\
-  68 & \cellcolor[HTML]{FFF2CC} & \cellcolor[HTML]{EAD1DC} \\
-  43 & \cellcolor[HTML]{FFF2CC} & \cellcolor[HTML]{EAD1DC} \\
-  24 & \cellcolor[HTML]{FFF2CC} & \cellcolor[HTML]{EAD1DC} \\
-  29 & \cellcolor[HTML]{FFF2CC} & \cellcolor[HTML]{EAD1DC} \\
-  59 & \multirow{-6}{*}{\cellcolor[HTML]{FFF2CC}47.8} & \multirow{-6}{*}{\cellcolor[HTML]{EAD1DC}18.6}
-\end{tabular}
-\end{table}
-
-\subsection{Accuracy}
-It is crucial to mention that the project currently lacks an automated
-method for evaluating the accuracy of results. However, the accuracy
-of two real-world puzzles (4x4 and 8x8) has been manually confirmed,
-with both achieving a 100\% correctness.
-
-\subsection{Analysis}
-
-This paper has asserted from the beginning that real-world puzzles
-pose greater challenges compared to their digital counterparts.
-While some intuitive explanations were provided to support this assertion,
-a proof hasn't been been presented until now. This test ultimately substantiates 
-the claim, demonstrating that the performance of the same
-algorithm can vary significantly depending on the accuracy of the input data.
-
-It is fair to point out that the performances of the algorithm are not amazing,
-but they are good enough to achieve the objectives of this paper \cref{document:objective}.
-It is also worth remembering that the problem itself is extremely complex.
-Using the formula introduced in section \cref{document:proof_definitions} we can calculate that a 64 piece puzzle,
-like the one that has been solved before, has approximately \(4 \cdot 10^{127}\) possible combinations.
-\[C = N! \cdot 4^N =  64! \cdot 4^{64} \approx 4.32 \cdot 10^{127}\]
-
 \section{The Labeling tool}

### 2023-11-25 LaTeX_paper/paper.tex
refactor applying sotha soltion to real world

@@
 
-\subsection{Digital vs Real World Puzzles}
+\subsubsection{Digital vs Real World Puzzles}
 
@@
 each piece more unique.
-\subsection{Run to Run Variation}
+\subsubsection{Run to Run Variation}
 
@@
 
-\subsection{Accuracy}
+\subsubsection{Accuracy}
 It is crucial to mention that the project currently lacks an automated
@@
 
-\subsection{Answering The Question}
+\subsubsection{Answering The Question}
 
@@
 
-\subsection{Future Works}
-
-\subsubsection{Machine Learning Based Comparator}
-
-\subsubsection{Labeling tool}
-
-\subsection{Conclusion}
-
-\section{Applying Already Existing Algorithms To The Real World}
-With the initial setup completed, it is now possible to
-test the existing algorithms with real-world puzzle. For this test,
-the fist algorithm~\cref{document:GCL} is selected due to the comprehensive
-details provided in the paper. Notably, it contains information
+Comparing the results achieved by our algorithm with some of the algorithms seen in the related
+work section (\cref{document:related_work}), clearly shows how our algorithm is far away
+from the current state of the art digital puzzle solvers. In this section we want to
+see if it is possible to use our comparator with current state of the art algorithms.
+In particular we selected the ``Graph Connection Laplacian'' solution, due to the
+comprehensive details provided in the paper. Notably, it contains information
 regarding the algorithm's accuracy in relation to the corruption rate,
@@
 
-The conducted tests reveal that the Comparator developed in this paper~\cref{document:my_comparator}
-and the ``Graph Connection Laplacian'' solution ~\cref{document:my_comparator} are not compatible with each other.
+Unfortunately the conducted tests reveal that the Comparator developed
+in this paper~\cref{document:my_comparator}
+and the ``Graph Connection Laplacian'' solution~\cref{document:GCL}
+are not compatible with each other.
 A formal proof supporting this assertion is presented subsequently.
 
-\subsection{Proof}
+\subsubsection{Selecting The Threshold Based On Input Data}
 
@@
 data to convert them from float to bool.
-\subsubsection{Input Data}
+
 To find the optimal threshold a small 16 piece puzzle has been solved.
@@
 
+\subsection{Future Works}
+
+\subsubsection{Machine Learning Based Comparator}
+
+\subsubsection{Labeling tool}
+
+\subsection{Conclusion}
+
 \subsection{Solutions For The Problem}

### 2023-11-25 LaTeX_paper/paper.tex
refactor future work

@@
 
+Until now this paper has not painted a positive picture about real-world
+puzzle solving. The current digital puzzle solver achieves a good time
+complexity, but requires really precise input data that we didn't manage
+to achieve with our real-world comparator (\cref{document:my_comparator}).
+On the other hand we managed to create a Solver (\cref{document:my_solver})
+that could operate with the noisy data generated by our comparator;
+But the greater reliability came at the expense of time complexity,
+and this meant that the maximum size of puzzle that could be solved was limited.
+
+Despite this inconvenience we think there is still a chance to solve
+the problem by significantly improving the comparator.
+
 \subsubsection{Machine Learning Based Comparator}
-
-\subsubsection{Labeling tool}
-
-\subsection{Conclusion}
-
-\subsection{Solutions For The Problem}
-
-There are two viable approaches to overcome this challenge.
-It is either necessary to enhance the Comparator while continuing
-to utilize the state-of-the-art solver,
-or it is possible to re-design the solver algorithm and create one
-specifically designed to operate with noisier data.
-
-\subsubsection{Improve The Comparator}
 
@@
 
-\subsubsection{Improving The Solver Algorithm}
-
-The puzzle dilemma is a ``multiobjective optimization problem'',
-where one objective is optimizing the time complexity,
-and the other is optimizing the accuracy of the algorithm
-in the presence of corrupted data.
-All the major algorithms proposed up to this point have prioritize speed.
-However, it is conceivable, and even probable,
-that an algorithm prioritizing accuracy over speed could prove
-effective with our comparator
-
-\subsubsection{The Path Forward}
-
-Improving the comparator is likely the most effective long-term solution,
-but it presents a significant challenge: manually testing if certain
-pieces fit together, followed by scanning and labeling,
+But this presents a significant challenge: manually testing if certain
+pieces fit together, followed by scanning them and labeling,
 is a time-intensive process that could require hundreds,
@@
 
-On the other hand, improving the solver may not be the optimal long-term
-solution, as it is likely to result in a worse time complexity.
-However, it could yield significant short-term benefits.
-
-Notably, this approach does not necessitate the creation of an extensive dataset
-and has the potential to facilitate its development.
-In fact, it could have the capability to solve numerous small
-puzzles and subsequently auto-label the connections
-based on the solutions it generates.
-
-Given the two options, it has been decided to focus on improving
-the solver algorithm. This choice was driven by the belief
-that creating a new algorithm, and subsequently using it to
-generate a dataset, would still be a more time-efficient
-approach compared to manually constructing a dataset.
-
-\section{The Labeling tool}
-When the program runs, it also exports files that could be utilized
-in the future for training a machine-learning-based comparator.
-This section will list the available data and explain the format employed.
-
-\subsection{Basic notions}
+However we just created a puzzle solver, even with a suboptimal
+time complexity, can easily solve small size real world puzzles.
+We could use it to solve a couple hundred small size puzzles,
+and automatically label the results for us,
+paving the way to a superior machine learning based comparator.
+
+\subsubsection{Labeling tool}
+
+To facilitate ours or someone else's future attempt to create a 
+machine-learning-based comparator;
+We added to our program the capability to export the data useful
+to train a machine learning model.
+This section will explain the format of the data.
+
+\paragraph {Basic notions}
 
@@
 
-\subsection{Image of each piece}
+\paragraph {Image of each piece}
 
@@
 
-\subsection{Image of each side}
+\paragraph {Image of each side}
 
@@
 
-\subsection{Corners of each piece}
+\paragraph{Corners of each piece}
 The file corners.json will be generated inside the folder results.
@@
 
-\subsection{Match for each side}
+\paragraph{Match for each side}
 The file connections\_result.json will be generated
@@
 
-\section{ConclusionsOld}
+\subsection{Conclusion}
+
 In conclusion, this paper has successfully achieved its objectives.

### 2023-11-25 LaTeX_paper/paper.tex
finish typo fixes

@@
   \item Type 2 puzzles have both the orientation and the position of the pieces unknown.
-  \item Type 3 puzzles have the orientation of the pieces unknown, but the position is known.
+  \item Type 3 puzzles have the orientation of the pieces unknown, but the position known.
 \end{itemize}
@@
 but also to all the algorithms analyzed in the related
-work section of this paper~\cref{document:related_work}.
+work section of this paper (\cref{document:related_work}).
 
@@
 	To answer this question we will measure the accuracy of the comparator we developed
-  to answer the previous question and observe what would happen if that accuracy is
+  and observe what would happen if that accuracy is
   applied to a digital puzzle solver. We will then propose a solution to improve
@@
 \section{Our Implementation Of A Puzzle Solver}
+
+This section will describe the implementation of the puzzle solver we developed.
+This solver will then be put to the test in the next section.
 
@@
 
-\subsection{Difference In Execution Time}
+\subsection{Execution Time Analysis}
 
 This section measures the execution time of many puzzles,
-and plots the results. The puzzles that has been used for
+and shows the results. The puzzles that has been used for
 this test has been described in ~\cref{document:dataset}.
@@
   harder compared to those who fulfill this condition. As they require an extra step compared to
-  the simple algorithm shown in section REF.
+  the simple algorithm shown in~\cref{document:my_solver}.
 \end{itemize}
@@
 work section (\cref{document:related_work}), clearly shows how our algorithm is far away
-from the current state of the art digital puzzle solvers. In this section we want to
-see if it is possible to use our comparator with current state of the art algorithms.
-In particular we selected the ``Graph Connection Laplacian'' solution, due to the
+from the current state-of-the-art digital puzzle solvers. In this section we want to
+see if it is possible to use our comparator with current state-of-the-art algorithms.
+In particular we selected the ``Graph Connection Laplacian''~\cite{GCL} solution, due to the
 comprehensive details provided in the paper. Notably, it contains information
@@
 
-Improving the comparator can shortly be done.
-Some minor improvements can be made by spending some time
+Some minor improvements to the comparator can be made by spending some time
 tweaking the current algorithm.
@@
 the most viable solution would likely involve
-leveraging machine learning techniques.
+leveraging machine-learning techniques.
 
 But this presents a significant challenge: manually testing if certain
-pieces fit together, followed by scanning them and labeling,
+pieces fit together, followed by scanning and labeling them,
 is a time-intensive process that could require hundreds,
@@
 
-However we just created a puzzle solver, even with a suboptimal
+However we just created a puzzle solver that, even with a suboptimal
 time complexity, can easily solve small size real world puzzles.
@@
 which holds great promise for future applications in creating a
-machine learning-based comparator. Such a comparator has the potential
+machine-learning-based comparator. Such a comparator has the potential
 to greatly facilitate puzzle-solving algorithms by providing more

### 2024-04-10 LaTeX_paper/paper.tex
minor fixes

@@
 Several algorithms with efficient time complexity have been developed
-specifically for ``digital''~\cref{fig:figure_digital_puzzle} jigsaw puzzles. However, the counterpart:
-the ``real world'' jigsaw puzzle~\cref{fig:figure_real_puzzle}, has received relatively little attention
+specifically for ``digital'' jigsaw puzzles. However, the counterpart:
+the ``real world'' jigsaw puzzle, has received relatively little attention
 in the literature. While some small-scale projects have addressed this issue,
@@
 
-The puzzle problem can be divided into two separate components: the ``Comparator''~\cref{document:comparator}
+The puzzle problem can be divided into two separate components: the ``Comparator''
 whose objective is to determine whether two sides of two pieces fit together,
-and the ``Solver''~\cref{document:solver} whose objective is to use the information provided
+and the ``Solver'' whose objective is to use the information provided
 by the comparator to find the best way to fit some pieces together.
@@
 The Solver poses its own set of challenges, as it is an example of a
-multiobjective optimization problem. Specifically, one objective is to have
+multi-objective optimization problem. Specifically, one objective is to have
 the fastest algorithm possible,
@@
 
-In the first half of this paper, a Comparator is developed, and its accuracy
-is evaluated.
-The data are then used to demonstrate its incompatibility with the current
+In the first half of this paper, we developed a Comparator, and evaluate it's accuracy.
+We then use the data to demonstrate its incompatibility with the current
 state-of-the-art algorithm. At this juncture,
@@
 it could be applied to the reconstruction of archaeological finds,
-such as a terracotta pot~\cref{fig:pot}.
+such as a terracotta pot of~\cref{fig:pot}.
 
@@
 \begin{itemize}
-  \item SinglePiece: which contains information about a single puzzle piece.
-  \item PieceGroup\(<\)T\(>\) where T can be either a PieceGroup or a SinglePiece\newline
-  This element encompasses four elements of type T, each with its own position (top right, top left, bottom left, bottom right).
-\end{itemize}
-Both SinglePiece and PieceGroup have an ``orientation'' attribute that goes from 0 to 3~\cref{fig:orientation}.
+  \item \texttt{SinglePiece}: which contains information about a single puzzle piece.
+  \item P\texttt{ieceGroup\(<\)T\(>\)} where \texttt{T} can be either a \texttt{PieceGroup} or a \texttt{SinglePiece}\newline
+  This element encompasses four elements of type \texttt{T}, each with its own position (top right, top left, bottom left, bottom right).
+\end{itemize}
+Both \texttt{SinglePiece} and \texttt{PieceGroup} have an ``orientation'' attribute that goes from 0 to 3~\cref{fig:orientation}.
 \begin{figure}[H]
@@
 \begin{itemize}
-\item SinglePiece is at level 0, representing a 1x1 ``solution'' to a puzzle.
-\item PieceGroup\(<\)SinglePiece\(>\) is at level 1, representing a 2x2 solution to a puzzle.
-\item PieceGroup\(<\)PieceGroup\(<\)SinglePiece\(>>\) is at level 2, representing a 4x4 solution to a puzzle, and so forth.
+\item \texttt{SinglePiece} is at level 0, representing a 1x1 ``solution'' to a puzzle.
+\item \texttt{PieceGroup\(<\)SinglePiece\(>\)} is at level 1, representing a 2x2 solution to a puzzle.
+\item \texttt{PieceGroup\(<\)PieceGroup\(<\)SinglePiece\(>>\)} is at level 2, representing a 4x4 solution to a puzzle, and so forth.
 \end{itemize}
@@
   \begin{itemize}
-    \item The comparing shore for level 0 objects is just the shore given by the Comparator~\cref{document:comparator}.
+    \item The comparing shore for level 0 objects is just the shore given by the Comparator of~\cref{document:comparator}.
     \item The comparing shore for level N+1 objects is the average between two comparisons made with objects of level N
@@
 In order for the created object to be considered valid all of the comparisons must have a shore greater
-than the constant MIN\_SHORE\_SINGLE\_SIDE. And the average of the four comparisons must be greater
-than the constant MIN\_SHORE\_PIECE\_GROUP.
+than the constant \texttt{MIN\_SHORE\_SINGLE\_SIDE}. And the average of the four comparisons must be greater
+than the constant \texttt{MIN\_SHORE\_PIECE\_GROUP}.
 
@@
 One advantage of this algorithm is that the outer edge for loop can be easily parallelized to achieve better performances.
+
+It should be noted that this pseudo code omits many details, two of witch are:
+\begin{itemize}
+  \item A condition that checks if the desired size has been reached and eventually stops the recursion.
+  \item A condition that specifically handles cases where the final size of the puzzle can't be reached simply by combining 4 pieces together recursively.
+  Without this condition the algorithm could only solve squared puzzles. Who's size is a power of 2. 
+\end{itemize}
 
@@
 Another feature of the algorithm that is worth testing is his consistency.
-The table below shows how the algorithm performs using a set of different
-same-sized puzzles as input.
+To measure tested the performance on 5 distinct puzzles, with the only thing in common
+been a size of 4$\times$4.
+
 \begin{table}[H]
@@
   \multicolumn{3}{c}{\cellcolor[HTML]{EA9999}Run to run vairance on a 4x4 real puzzle}                                                             \\
-  \cellcolor[HTML]{F9CB9C}Execution time {[}s{]} & \cellcolor[HTML]{FFE599}Avrege                 & \cellcolor[HTML]{D5A6BD}Standard deviation     \\
+  \cellcolor[HTML]{F9CB9C}Execution time {[}s{]} & \cellcolor[HTML]{FFE599}Average                 & \cellcolor[HTML]{D5A6BD}Standard deviation     \\
   64 & \cellcolor[HTML]{FFF2CC} & \cellcolor[HTML]{EAD1DC} \\
@@
 with them achieving a 100\% correctness.
+
+\begin{table}[H]
+\centering
+\begin{tabular}{
+>{\columncolor[HTML]{FCE5CD}}c 
+>{\columncolor[HTML]{FFF2CC}}c 
+>{\columncolor[HTML]{EAD1DC}}c }
+\multicolumn{3}{c}{\cellcolor[HTML]{EA9999}Manualy evaluated accuracy of the solution}                       \\
+\cellcolor[HTML]{F9CB9C}Puzzle size & \cellcolor[HTML]{FFE599}Puzzle kind & \cellcolor[HTML]{D5A6BD}Accuracy \\
+4x4                                 & real world                          & 100\%                            \\
+8x8                                 & real world                          & 100\%                            \\
+16x16                               & digital                             & 100\%                           
+\end{tabular}
+\end{table}
 

### 2024-04-10 LaTeX_paper/paper.tex
fix spelling

@@
   and Solver~\cref{document:solver}. Due to the intrinsic difference of digital and real-world jigsaw puzzles
-  reusing the Comparator is impossible, but there is the possibility to reuse the Sover,
+  reusing the Comparator is impossible, but there is the possibility to reuse the Solver,
   assuming we could build a Comparator for real-world puzzles that is in the same realm
@@
   \item \texttt{SinglePiece}: which contains information about a single puzzle piece.
-  \item P\texttt{ieceGroup\(<\)T\(>\)} where \texttt{T} can be either a \texttt{PieceGroup} or a \texttt{SinglePiece}\newline
+  \item P\texttt{PieceGroup\(<\)T\(>\)} where \texttt{T} can be either a \texttt{PieceGroup} or a \texttt{SinglePiece}\newline
   This element encompasses four elements of type \texttt{T}, each with its own position (top right, top left, bottom left, bottom right).
@@
 certain details may be lost when compared to a non-binary comparison. 
-To quantify accuracy the paper used the ``neighbors compariso'' metric,
+To quantify accuracy the paper used the ``neighbors comparison'' metric,
 which ``calculates the percentage of pairs of image patches that are matched correctly''.
@@
   >{\columncolor[HTML]{EAD1DC}}c }
-  \multicolumn{3}{c}{\cellcolor[HTML]{EA9999}Run to run vairance on a 4x4 real puzzle}                                                             \\
+  \multicolumn{3}{c}{\cellcolor[HTML]{EA9999}Run to run variance on a 4x4 real puzzle}                                                             \\
   \cellcolor[HTML]{F9CB9C}Execution time {[}s{]} & \cellcolor[HTML]{FFE599}Average                 & \cellcolor[HTML]{D5A6BD}Standard deviation     \\
@@
 >{\columncolor[HTML]{EAD1DC}}c }
-\multicolumn{3}{c}{\cellcolor[HTML]{EA9999}Manualy evaluated accuracy of the solution}                       \\
+\multicolumn{3}{c}{\cellcolor[HTML]{EA9999}Manually evaluated accuracy of the solution}                       \\
 \cellcolor[HTML]{F9CB9C}Puzzle size & \cellcolor[HTML]{FFE599}Puzzle kind & \cellcolor[HTML]{D5A6BD}Accuracy \\
@@
 
-% Please add the following required packages to your document preamble:
-% \usepackage[table,xcdraw]{xcolor}
-% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
 \begin{table}[H]
@@
   The total number of possible combinations is \(N! \times 4^N\) where
-  \(N!\) represent all possible way to combinate the pieces in a particular position, and
+  \(N!\) represent all possible way to combine the pieces in a particular position, and
   \(4^N\) represents all possible orientations that each piece can have.
@@
 
-In Figure \cref{fig:GCL_Corruption_Rate}, it can be observed that at a corruption rate of 0.057,
+In \cref{fig:GCL_Corruption_Rate}, it can be observed that at a corruption rate of 0.057,
 a neighbors comparison metric of roughly 80\% can be anticipated.

### 2024-04-10 LaTeX_paper/paper.tex
Split last section, todo: final check

@@
 
-\section{Conclusions}
-This section will conclude the paper,
-by answering the two questions posed in \cref{document:objective}:
-
+\section{Evaluation}
+This section will evaluate the proposed solution by measuring
+two key metrics: execution time and accuracy. 
+The objective of this section is to answer the first question posed in~\cref{document:objective}:
 \begin{itemize}
@@
                 digital and real-world puzzles?
-  \item What are the challenges to use the current state of the art algorithms developed for digital
-                puzzles in the real-world, and how can we overcome them?
-\end{itemize}
-And by making some consideration about possible future works related to this problem.
+\end{itemize}
 
@@
 algorithm can vary significantly depending on the accuracy of the input data.
+
+\section{Conclusion}
+
+This sections aim to conclude the paper by answering the second question
+posed in ~\cref{document:objective}:
+
+\begin{itemize}
+  \item What are the challenges to use the current state of the art algorithms developed for digital
+                puzzles in the real-world, and how can we overcome them?
+\end{itemize}
+
+Ath the end of the section we will also make some consideration about
+possible future works related to this problem.
 

### 2024-04-13 LaTeX_paper/paper.tex
minor fixes

@@
 
-The most promising approach to improving the Comparator
+The most promising approach to improve the Comparator
 involves utilizing machine learning, but this requires a substantial amount of data.
@@
 \subsubsection{Classification}
-Puzzles are categorized in different types, for example 
+Puzzles are categorized in different types, for example:
 \begin{itemize}
@@
 There is  another important distinction between different types of puzzles.
-They can be divided into “digital”~\cref{fig:figure_digital_puzzle} and
-“real world”~\cref{fig:figure_real_puzzle} jigsaw puzzles.
+They can be divided into “digital” e.g.~\cref{fig:figure_digital_puzzle} and
+“real world” e.g.~\cref{fig:figure_real_puzzle} jigsaw puzzles.
 The difference between the two is quite self explanatory,
@@
 despite the generic concept of the puzzle not changing,
-obtaining accurate matches of a piece's characteristics
+obtaining accurate measures of a piece's characteristics
 is far easier with a digital puzzle,
@@
 For example, a piece's shape may be distorted by
-a low-quality cut, as seen in picture~\cref{fig:figure_measurement_error}
+a low-quality cut, as seen in~\cref{fig:figure_measurement_error}
 
@@
     \subsubsection{The Solver:} This component utilizes the information provided by the
-    Comparator~\cref{document:comparator}, and attempts to find a solution
+    Comparator, and attempts to find a solution
     (i.e.\ a position and an orientation for each piece)
@@
   and observe what would happen if that accuracy is
-  applied to a digital puzzle solver. We will then propose a solution to improve
+  applied to a digital puzzle Solver. We will then propose a solution to improve
   the accuracy of real-world Comparators.
@@
 This section will describe the implementation of the puzzle solver we developed.
-This solver will then be put to the test in the next section.
+This solver will then be put to the test in the next sections.
 
@@
 
-The next step following the general structure~\cref{document:splitter}
+The next step following the general structure described in~\cref{document:splitter}
 is to split a piece into
@@
 \subsection{Our Solver}\label{document:my_solver}
-The Solver that has been developed is not the primary focus of this
-paper and cannot be considered state-of-the-art when compared
+The Solver we developed cannot be considered state-of-the-art when compared
 to the current best digital puzzle solvers. However, it may be
 considered as such when compared to existing ``real-world'' puzzle solvers.
+
+Regardless, the achieved performances are still good enough to test and understand
+the differences between digital and real-world puzzles,
+which is the main objective of this paper.
 
@@
 \end{itemize}
-Both \texttt{SinglePiece} and \texttt{PieceGroup} have an ``orientation'' attribute that goes from 0 to 3~\cref{fig:orientation}.
+Both \texttt{SinglePiece} and \texttt{PieceGroup} have an ``orientation'' attribute that goes from 0 to 3, this attribute
+represent the orientation of the piece, as shown in~\cref{fig:orientation}.
 \begin{figure}[H]
@@
 
-The constants MIN\_SHORE\_SINGLE\_SIDE and MIN\_SHORE\_PIECE\_GROUP mentioned in
+The constants \texttt{MIN\_SHORE\_SINGLE\_SIDE} and \texttt{MIN\_SHORE\_PIECE\_GROUP} mentioned in
 section~\cref{document:combining_four_objects} were set at different values
@@
 It is crucial to mention that the project currently lacks an automated
-method for evaluating the accuracy of results. However, the accuracy
+method for evaluating the accuracy of the results. However, the accuracy
 of two real-world puzzles (4x4 and 8x8) and one digital puzzle (16x16) has been manually confirmed,
@@
 >{\columncolor[HTML]{EAD1DC}}c }
-\multicolumn{3}{c}{\cellcolor[HTML]{EA9999}Manually evaluated accuracy of the solution}                       \\
+\multicolumn{3}{c}{\cellcolor[HTML]{EA9999}Manually evaluated accuracy of the solutions}                       \\
 \cellcolor[HTML]{F9CB9C}Puzzle size & \cellcolor[HTML]{FFE599}Puzzle kind & \cellcolor[HTML]{D5A6BD}Accuracy \\
@@
 While some intuitive explanations were provided to support this assertion,
-a proof hasn't been been presented until now. This test ultimately substantiates 
+a proof hasn't been presented until now. This test ultimately substantiates 
 the claim, demonstrating that the performance of the same
@@
 
-Unfortunately the conducted tests reveal that the Comparator developed
-in this paper~\cref{document:my_comparator}
-and the ``Graph Connection Laplacian'' solution~\cref{document:GCL}
+Unfortunately the conducted tests reveal that the Comparator we developed in~\cref{document:my_comparator}
+and the ``Graph Connection Laplacian'' solution of~\cref{document:GCL}
 are not compatible with each other.
-A formal proof supporting this assertion is presented subsequently.
+A proof supporting this assertion is presented subsequently.
 
@@
 
-The comparison algorithm deceived in section~\cref{document:my_comparator} outputs a compatibility
+The comparison algorithm described in~\cref{document:my_comparator} outputs a compatibility
 shore that goes from 0 to 1.\newline
-But the algorithm~\cref{document:GCL} takes as input a binary value.
+But the graph connection Laplacian algorithm of~\cref{document:GCL} takes as input a binary value.
 Which means that it is necessary to apply a threshold to the input
@@
 
-To find the optimal threshold a small 16 piece puzzle has been solved.
-And the following 4 values have been measured, in function of the threshold:
+To find the optimal threshold we solved a small 16 piece puzzle.
+And we measured the following 4 values in function of the threshold:
 
@@
   The probability that 2 randomly selected sides matches given that in the correct puzzle
-  solution they are actually close to each other. Ideally this should be 1.
+  solution they are actually close to each other. Ideally this should be 1, as we would prefer
+  that the comparison never returns false if two pieces are actually connected in the correct solution.
 
@@
   multiplied by the probability that the comparison returns true
-  (which is c.c match\%). \newline
-  Ideally limit match\% should be almost zero.
+  (which is c.c match\%).\newline
+  Ideally limit match\% should be almost zero, as we would prefer that the comparison is true only when
+  the pieces are actually connected in the correct solution.
   \[limit \: math\% = math\% - \frac{c.c. \: mathc\%}{16 \times 4}\]
@@
 
-Now, let's consider Algorithm \cref{document:GCL} tasked with solving a 500-piece puzzle
-using our Comparator \cref{document:my_comparator}.
+Now, let's consider the graph connection Laplacian algorithm of \cref{document:GCL} tasked with solving a 500-piece puzzle
+using our Comparator of \cref{document:my_comparator}.
 A threshold of 0.425 is chosen;
@@
 \subsubsection{Corruption Rate Analysis}
-\begin{figure}[h]
-  \caption{Neighbors comparison vs Corruption rate of algorithm \cref{document:GCL}. Image taken from pater \cite{GCL} page 34.}\label{fig:GCL_Corruption_Rate}
+\begin{figure}[H]
+  \caption{Neighbors comparison vs Corruption rate of graph connection laplacian algorithm of \cref{document:GCL}. Image taken from paper~\cite{GCL} page 34.}\label{fig:GCL_Corruption_Rate}
   \centering
@@
 tweaking the current algorithm.
-However, it is evident that for a task of this nature,
+However, it is clear that for a task of this nature,
 the most viable solution would likely involve
@@
 
-\paragraph {Basic notions}
-
-One piece is uniquely identified by his id piece\_id.
+\paragraph{Basic notions}
+
+One piece is uniquely identified by his id \texttt{piece\_id}.
 The id is an integer that goes from 0 to \mbox{Number of pieces - 1}.
-Each piece has 4 sides that can be identified by the side side\_id,
+Each piece has 4 sides that can be identified by the side \texttt{side\_id},
 an integer that goes from 0 to 3.
 
-\paragraph {Image of each piece}
-
-Inside the folder results/pieces the program will generate one image
-for each one of the pieces of the puzzle. The file will be named \{piece\_id\}.jpeg.
+\paragraph{Image of each piece}
+
+Inside the folder \texttt{results/pieces} the program will generate one image
+for each one of the pieces of the puzzle. The file will be named \texttt{\{piece\_id\}.jpeg}.
 An example can be seen in \cref{fig:result_pieces}
@@
 
-\paragraph {Image of each side}
-
-Inside the folder results/sides the program will generate one image 
-for each side of each piece. The images will be named \{piece\_id\}\_\{side\_id\}.jpeg.
+\paragraph{Image of each side}
+
+Inside the folder \texttt{results/sides} the program will generate one image 
+for each side of each piece. The images will be named \texttt{\{piece\_id\}\_\{side\_id\}.jpeg}.
 An example can be seen in \cref{fig:result_sides}
@@
 \paragraph{Corners of each piece}
-The file corners.json will be generated inside the folder results.
+The file \texttt{corners.json} will be generated inside the folder \texttt{results}.
 This file will contain a list of pieces.
@@
 \paragraph{Match for each side}
-The file connections\_result.json will be generated
-inside the folder results. This file will contain a list of pieces,
+The file \texttt{connections\_result.json} will be generated
+inside the folder \texttt{results}. This file will contain a list of pieces,
 each piece has 4 sides, and each side has a link to the side of the piece
@@
 
+All the code used in this project is available on the GitHub repository: \url{https://github.com/lucaSartore/PuzzleSolver}.
+
 \begin{figure}[h]

### 2024-04-13 LaTeX_paper/paper.tex
add unitn logo in paper start
use unitn margins

@@
-\documentclass{article}
-
+\documentclass[epsfig,a4paper,11pt,titlepage,twoside,openany]{article}
+\usepackage{epsfig}
+\usepackage{plain}
+\usepackage{setspace}
+\usepackage[paperheight=29.7cm,paperwidth=21cm,outer=1.5cm,inner=2.5cm,top=2cm,bottom=2cm]{geometry} % per definizione layout
+\usepackage{titlesec} % per formato custom dei titoli dei capitoli
+
+%\documentclass[epsfig,a4paper,11pt,titlepage,twoside,openany]{book}
 % Required for inserting images
@@
 \usepackage{etoolbox}
-
-% to set the margin of the page
-\usepackage[a4paper, left=25mm,top=20mm,bottom=20mm,right=15mm]{geomet ry}
 
@@
 
-\maketitle
-
+% \maketitle
+
+\begin{center}
+
+  \includegraphics[scale=1]{pictures/unitn_logo.pdf}
+
+  \vspace{3 cm}
+
+  \LARGE{Department of Information Engineering and Computer Science\\}
+
+  \vspace{1 cm} 
+  \Large{Bachelor’s Degree in\\
+    Computer, Communications and Electronic Engineering
+  }
+
+  \vspace{2 cm} 
+  \Large\textsc{Final Dissertation\\} 
+  \vspace{1 cm} 
+  \Huge\textsc{Title\\}
+  \Large{\it{Use Of Jigsaw Puzzle Solving Algorithms In The Real World}}
+
+  \vspace{2 cm} 
+  \begin{tabular*}{\textwidth}{ c @{\extracolsep{\fill}} c }
+  \Large{Supervisor} & \Large{Student}\\
+  \Large{Patrignani Marco}& \Large{Sartore Luca}\\
+  \end{tabular*}
+
+  \vspace{2 cm}
+
+  \Large{Academic year 2023/2024}
+
+\end{center}
 \newpage

### 2024-04-14 LaTeX_paper/paper.tex
Fix title
fix typo

@@
   \vspace{1 cm} 
-  \Huge\textsc{Title\\}
-  \Large{\it{Use Of Jigsaw Puzzle Solving Algorithms In The Real World}}
+  \Huge\textsc{Use Of Jigsaw Puzzle Solving Algorithms In The Real World}
 
@@
   \item \texttt{SinglePiece}: which contains information about a single puzzle piece.
-  \item P\texttt{PieceGroup\(<\)T\(>\)} where \texttt{T} can be either a \texttt{PieceGroup} or a \texttt{SinglePiece}\newline
+  \item \texttt{PieceGroup\(<\)T\(>\)} where \texttt{T} can be either a \texttt{PieceGroup} or a \texttt{SinglePiece}\newline
   This element encompasses four elements of type \texttt{T}, each with its own position (top right, top left, bottom left, bottom right).
